---
title: "Framed Listening: Descriptive Stats & Text Preprocessing"
author: "Hazel A. van der Walle (PhD student, Music, Durham University)"
date: "7 April 2026"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    theme: cosmo
---

All datasets generated and used for this study are openly available on GitHub: <https://github.com/HazelvdW/context-framed-listening>.

---

## Setup

```{r}
reticulate::py_install("pandas")
```

```{python}
import os
import csv
import pandas as pd
import numpy as np
```

Load in the data file **`dataMAINstudy`** that contains participants' thought descriptions:

```{python}
data = pd.read_csv(
    "/Users/hazelaileenvanderwalle/Library/CloudStorage/OneDrive-Personal/work/study/PhD/_PROJECT/_framedListening_NLP/context-framed-listening/dataMAINstudy.csv"
)
```

Sentiment analysis is being conducted on music-influence mental contents (MIMC).

Create a separate dataset that only contains trials where MIMC were described, dropping all rows where "descr_THOUGHT.text" is NA.

### Descriptive stats before splitting MIMC trials

```{python}
dataMIMC = data[data['descr_THOUGHT.text'].notna()].copy()

# drop no-MIMC columns
dataMIMC.drop(columns=['response_thought_or_not.keys', 'input_NOT.text'],
              inplace=True)

# Edit clip_name column
for rowIndex, row in dataMIMC.iterrows():
    clip_name = row['clip_name']
    if clip_name[0:3] == '80s':
        dataMIMC.loc[rowIndex, 'clip_name'] = '80s' + clip_name[3:10]
    elif clip_name[0:3] == 'Jaz':
        dataMIMC.loc[rowIndex, 'clip_name'] = 'Jaz' + clip_name[4:11]
    elif clip_name[0:3] == 'Met':
        dataMIMC.loc[rowIndex, 'clip_name'] = 'Met' + clip_name[5:12]
    elif clip_name[0:3] == 'Ele':
        dataMIMC.loc[rowIndex, 'clip_name'] = 'Ele' + clip_name[10:17]

print(dataMIMC)

# print all column headers for later reference
print(dataMIMC.columns)

# print number of trials with and without MIMC descriptions
non_na_count = len(dataMIMC)
na_count = data['descr_THOUGHT.text'].isna().sum()
total_trials = non_na_count + na_count
percentage_with_MIMC = (non_na_count / total_trials) * 100

print(f"\nNumber of trials with MIMC description: {non_na_count}")
print(f"Number of trials with no MIMC description: {na_count}")
print(f"Total number of trials: {total_trials}")
print(f"\n{non_na_count} out of {total_trials} trials ({percentage_with_MIMC:.1f}%) contained music-influenced mental content descriptions.")

# Calculate number of MIMC descriptions per unique clip and context pair
MIMC_per_clip_context = dataMIMC.groupby(['clip_name', 'context_word']).size().reset_index(name='MIMC_count')
print(f"\nNumber of MIMC descriptions per unique clip and context pair:\n{MIMC_per_clip_context}")

# Calculate min, max, and mean MIMC counts per clip-context pair
min_mimc_count = MIMC_per_clip_context['MIMC_count'].min()
max_mimc_count = MIMC_per_clip_context['MIMC_count'].max()
mean_mimc_count = MIMC_per_clip_context['MIMC_count'].mean()

print(f"\nAt an excerpt level, participants reported {min_mimc_count} to {max_mimc_count} thoughts (M = {mean_mimc_count:.2f}).")
```

Combine the clip and context values into an additional column (`clip_context_PAIR`). Create a clip genre column (`clip_genre`) to use later.

```{python}
def create_clip_context_pair(row):
    clip_name = row['clip_name']
    if 'bar' in row['context_word']:
        return 'BAR-' + clip_name
    elif 'videogame' in row['context_word']:
        return 'VIDEOGAME-' + clip_name
    elif 'concert' in row['context_word']:
        return 'CONCERT-' + clip_name
    elif 'movie' in row['context_word']:
        return 'MOVIE-' + clip_name
    else:
        return 'NO_MATCH'

dataMIMC['clip_context_PAIR'] = dataMIMC.apply(create_clip_context_pair, axis=1)

# Create 'clip_genre' column
def extract_genre(clip_name):
    if '80s' in clip_name:
        return '80s'
    elif 'Jaz' in clip_name:
        return 'Jazz'
    elif 'Met' in clip_name:
        return 'Metal'
    elif 'Ele' in clip_name:
        return 'Electronic'
    else:
        return 'UNKNOWN'

dataMIMC['clip_genre'] = dataMIMC['clip_name'].apply(extract_genre)

# Reorder columns
cols = dataMIMC.columns.tolist()
# Move 'clip_genre' to be after 'clip_name'
cols.insert(cols.index('clip_name') + 1, cols.pop(cols.index('clip_genre')))
# Move 'clip_context_PAIR' to be after 'context_word'
cols.insert(cols.index('context_word') + 1, cols.pop(cols.index('clip_context_PAIR')))
dataMIMC = dataMIMC[cols]

# Check the dataframe by a quick re-view
print(dataMIMC)
print(dataMIMC.columns)

# Saving a .csv for the option to open and look at the full dataframe
base_path = "/Users/hazelaileenvanderwalle/Library/CloudStorage/OneDrive-Personal/work/study/PhD/_PROJECT/_framedListening_NLP/context-framed-listening"
dataMIMC.to_csv(f'{base_path}/NLP_outputs/dataMIMC.csv', encoding='utf-8')
```

---

## Descriptive Statistics

Basic descriptive statistics on the clip-context pairings.

Create a dataframe including summary info about each clip-context stimuli pairing:

- Number of participants that reported MIMC while listening
- Mean MIMC and clip ratings

```{python}
columns = dataMIMC.columns.tolist()[1:-1]

# Drop these following columns so they don't aggregate by clip-context grouping:
drop = ['clip_name', 'clip_genre', 'context_word', 'clip_context_PAIR',
        'expName', 'File_ID', 'date', 'descr_THOUGHT.text',
        'demographics.headphones', 'demographics.age',
        'demographics.gender', 'demographics.livingCountry',
        'demographics.birthCountry', 'demographics.nativeLanguage',
        'demographics.otherLanguage', 'demographics.otherLanguageText',
        'demographics.hearingImpariments', 'demographics.hearingImpairmentsText',
        'demographics.education', 'demographics.musicianIdentification',
        'demographics.feedback']

# Setting up an aggregate function collector
agg_fun = {}

# As we dropped trials without MIMC, we can just sum participants for MIMC occurrence
agg_fun['PROLIFIC_PID'] = 'count'

# Taking the mean of all columns except participant IDs and dropped columns
for col in columns:
    if col not in drop and col != 'PROLIFIC_PID':
        agg_fun[col] = 'mean'

# Group the dataframe by clip-context pairing, then run the aggregate functions created above
clipContextDescrStats = dataMIMC.groupby('clip_context_PAIR').agg(agg_fun)
print(clipContextDescrStats)

# Saving a .csv for the option to open and look at the full dataframe
clipContextDescrStats.to_csv(f'{base_path}/NLP_outputs/clipContextDescrStats.csv', encoding='utf-8')
```

Check the minimum and maximum reported MIMC occurences of all clip-context stimuli pairings:

```{python}
mostMIMC_ccpair = clipContextDescrStats['PROLIFIC_PID'].idxmax()
leastMIMC_ccpair = clipContextDescrStats['PROLIFIC_PID'].idxmin()
mostMIMC_value = clipContextDescrStats['PROLIFIC_PID'].max()
leastMIMC_value = clipContextDescrStats['PROLIFIC_PID'].min()

print(f"Clip-context pair with the most reported MIMC: {mostMIMC_ccpair} ({mostMIMC_value})")
print(f"Clip-context pair with the least reported MIMC: {leastMIMC_ccpair} ({leastMIMC_value})")
```

---

## Text Preprocessing

Different NLP models require different levels of text filtering to perform optimally.

**BERT** — Benefits from minimal preprocessing because:

- Understands context and handles common words well
- Has its own tokenisation and handles word variations
- Only needs custom domain-specific stop words removed

**TF-IDF** — Needs more aggressive preprocessing because:

- Dosen't understand context as well
- Common stop words add noise
- Needs lemmatisation to group related terms

> We will produce two levels of text preprocessing to save out for later analyses. All text will be manually spell checked.

### Spell checking

Collect all misspellings flagged by spell checking packages to manually go through and make corrections where necessary.

```{r}
reticulate::py_install("nltk")
reticulate::py_install("pyspellchecker")
```

```{python}
import re
from collections import defaultdict

import nltk
nltk.download('stopwords')

from nltk import pos_tag, word_tokenize
nltk.download('punkt_tab')
nltk.download('wordnet')
nltk.download('averaged_perceptron_tagger_eng')

from spellchecker import SpellChecker
spell = SpellChecker()
```

```{python}
def find_potential_misspellings_with_context(row):
    misspellings_with_context = []
    text = row['descr_THOUGHT.text']
    if isinstance(text, str):
        # Tokenise the raw text
        tokens = word_tokenize(text)
        for word in tokens:
            # Clean the word for spell checking (lowercase and remove punctuation)
            cleaned_word = re.sub(r'[^a-zA-Z0-9]', '', word.lower())
            if cleaned_word and cleaned_word not in spell:
                misspellings_with_context.append((cleaned_word, text))  # Store word and original text
    return misspellings_with_context

# Apply the function to each row and collect all misspellings with their context
all_misspellings_with_context = []
for index, row in dataMIMC.iterrows():
    misspellings_list = find_potential_misspellings_with_context(row)
    all_misspellings_with_context.extend(misspellings_list)

# Create a DataFrame from the collected misspellings and their context
misspellings_df = pd.DataFrame(all_misspellings_with_context, columns=['Potential Misspelling', 'Original Text'])

# Display the dataFrame showing unique misspellings
# (to show all occurrences, remove .drop_duplicates() <- otherwise, this shows their first occurrence context only.)
print(misspellings_df.drop_duplicates(subset=['Potential Misspelling']))

# Saving the full dataFrame to a CSV file
misspellings_df.to_csv(f'{base_path}/NLP_outputs/misspellings_df.csv', encoding='utf-8', index=False)

# This dataFrame can be used to create your spelling dictionary.
```

> I saved the above file out to manually check over and edit the spellings as needed. See `misspelling_correction_MAINstudy.csv`.

Below, apply these spelling corrections from the **manually edited csv file** to `dataMIMC`:

```{python}
# Load the correction mapping from the CSV file
try:
    correction_df = pd.read_csv(f"{base_path}/NLP_outputs/misspelling_correction_MAINstudy.csv")

    # Ensure the 'correction' column is treated as strings and handle potential NaNs
    correction_df['correction'] = correction_df['correction'].astype(str).replace('nan', '')

    # Create a dictionary from the df, filtering out any remaining NaNs if necessary
    correction_mapping = pd.Series(correction_df.correction.values, index=correction_df.misspelling).dropna().to_dict()

    print("Correction mapping loaded successfully.")

except FileNotFoundError:
    print("Error: misspelling_correction_MAINstudy.csv not found.")
    correction_mapping = {}
except KeyError:
    print("Error: CSV must contain 'misspelling' and 'correction' columns.")
    correction_mapping = {}


def apply_manual_corrections(text, mapping):
    if isinstance(text, str):
        # Clean the text (lowercase and remove punctuation) before applying corrections
        cleaned_text = re.sub(r'[^a-zA-Z0-9\s]', '', text.lower())
        words = cleaned_text.split()
        # Apply corrections
        corrected_words = [str(mapping.get(word, word)) for word in words]
        return " ".join(corrected_words)
    return str(text)

# Apply the manual corrections to the descr_THOUGHT.text column
dataMIMC['descr_THOUGHT.text_spellchecked'] = dataMIMC['descr_THOUGHT.text'].apply(
    lambda x: apply_manual_corrections(x, correction_mapping)
)

# Display the original and corrected text to check the changes
print(dataMIMC[['descr_THOUGHT.text', 'descr_THOUGHT.text_spellchecked']])
```

Importing some more packages necessary for text cleaning before feeding these MIMC into our NLP models.

### Stop Words

These are words we will remove from the text that won't be accounted for in analyses.

We will define custom domain-specific stop words (e.g. music style, context cues, thought types), and get NLTK common English-language stop words.

Both preprocessing levels will have custom stop words removed, but only level 2 preprocessing for TF-IDF will has the NLTK stop words removed (as BERT understands "the", "is", "and", etc.).

```{python}
# Define custom stop words (domain-specific terms to remove)
customStopWords = ['music', 'song', 'songs', 'excerpt', 'excerpts', 'piece', 'pieces', 'clip', 'clips',
                    'electronic', 'jazz', 'metal', 'rock',
                    'bar', 'bars', 'concert', 'concerts', 'film', 'films',
                    'movie', 'movies', 'videogame', 'videogames',
                    'video', 'videos', 'game', 'games',
                    'instrument', 'instruments', 'instrumental', 'drum', 'drums',
                    'guitar', 'guitars', 'guitarist', 'piano', 'pianos', 'pianist',
                    'keyboard', 'keyboards', 'band', 'play', 'playing', 'plays',
                    'saxophone', 'saxophones', 'xylophone', 'xylophones',
                    'vibraphone', 'vibraphones', 'singer', 'singers', 'sing', 'sings',
                    'could', 'would']

thoughtStopWords = ['think', 'thinks', 'thought', 'thinking',
                    'imagine', 'imagines', 'imagined', 'imagining',
                    'image', 'images', 'imaged', 'imaging',
                    'visualise', 'visualises', 'visualised', 'visualising',
                    'visualize', 'visualizes', 'visualized', 'visualizing',
                    'picture', 'pictures', 'pictured', 'picturing',
                    'scene', 'scenes', 'story', 'stories',
                    'memory', 'memories', 'reminder', 'reminders', 'remind', 'reminds',
                    'remember', 'remembers', 'remembered', 'remembering',
                    'reminiscent', 'reminisce', 'reminisces', 'reminisced', 'reminiscing',
                    'sound', 'sounds', 'sounded', 'sounding', 'like',
                    'make', 'makes', 'made', 'making']

# set NLTK stop words
nltk_stop_words = set(nltk.corpus.stopwords.words('english'))
print(nltk_stop_words)
print("\nNLTK Stop Words:", len(nltk_stop_words))
```

### Lemmatise

Lemmatising groups inflected word forms together by identifying the dictionary form (the lemma) to analyse them as a single item.

[*e.g., improve/improving/improvements/improved/improver = improve*]

Only level 2 preprocessing for TF-IDF will have lemmatisation (BERT is able to handle word variations).

```{python}
# Initialise lemmatiser and tag mapping
lemmatiser = nltk.stem.WordNetLemmatizer()
wn = nltk.corpus.wordnet

tag_map = defaultdict(lambda: wn.NOUN)
tag_map['J'] = wn.ADJ
tag_map['V'] = wn.VERB
tag_map['R'] = wn.ADV
```

### Apply text preprocessing

**LEVEL 1:** Minimal preprocessing for BERT, only removing custom stop words from spell-checked MIMC descriptions.

**LEVEL 2:** Aggressive preprocessing for TF-IDF, removing custom stop words, NLTK stop words, lemmatising, converting to lowercase, and removing punctuation from the spell-checked MIMC descriptions.

```{python}
def to_list(arg):
    return list(arg) if isinstance(arg, set) else arg

def preprocessing_lvl1a(text, stimuli_stop_words, thought_stop_words):
    """
    Level 1a: Minimal preprocessing for BERT
    - Only removes custom domain-specific stop words
    - Preserves original word forms (no lemmatisation)
    - Keeps punctuation and capitalization for BERT's tokeniser
    """
    if isinstance(text, str):
        custom_stop_words = set(to_list(stimuli_stop_words) + to_list(thought_stop_words))
        tokens = word_tokenize(text)
        filtered_tokens = []
        for word in tokens:
            if word.lower() not in custom_stop_words:
                filtered_tokens.append(word)
        return " ".join(filtered_tokens)
    return text

def preprocessing_lvl1b(text, stimuli_stop_words):
    """
    Same as Level 1a but doesn't remove thought-related stop words
    """
    if isinstance(text, str):
        custom_stop_words = set(to_list(stimuli_stop_words))
        tokens = word_tokenize(text)
        filtered_tokens = []
        for word in tokens:
            if word.lower() not in custom_stop_words:
                filtered_tokens.append(word)
        return " ".join(filtered_tokens)
    return text


def preprocessing_lvl2a(text, stimuli_stop_words, thought_stop_words, nltk_stop_words, lemmatiser, tag_map):
    """
    Level 2a: Aggressive preprocessing for TF-IDF
    - Removes all stop words (custom + NLTK)
    - Applies lemmatisation
    - Converts to lowercase
    - Removes punctuation
    """
    if isinstance(text, str):
        combined_stop_words = set(to_list(stimuli_stop_words) + to_list(thought_stop_words) + to_list(nltk_stop_words))
        lemmatized_stop_words = set()
        for sw in combined_stop_words:
            lemmatized_stop_words.add(lemmatiser.lemmatize(sw.lower(), wn.NOUN))
            lemmatized_stop_words.add(lemmatiser.lemmatize(sw.lower(), wn.VERB))

        tokens = word_tokenize(text)
        lemmatised_tokens = []
        for word, tag in pos_tag(tokens):
            cleaned_word = re.sub(r'[^a-zA-Z]', '', word.lower())
            if cleaned_word:
                lemmatised_word = lemmatiser.lemmatize(cleaned_word, tag_map[tag[0]])
                if lemmatised_word not in lemmatized_stop_words:
                    lemmatised_tokens.append(lemmatised_word)
        return " ".join(lemmatised_tokens)
    return text

def preprocessing_lvl2b(text, stimuli_stop_words, nltk_stop_words, lemmatiser, tag_map):
    """
    Same as Level 2a but doesn't remove thought-related stop words
    """
    if isinstance(text, str):
        combined_stop_words = set(to_list(stimuli_stop_words) + to_list(nltk_stop_words))
        lemmatized_stop_words = set()
        for sw in combined_stop_words:
            lemmatized_stop_words.add(lemmatiser.lemmatize(sw.lower(), wn.NOUN))
            lemmatized_stop_words.add(lemmatiser.lemmatize(sw.lower(), wn.VERB))

        tokens = word_tokenize(text)
        lemmatised_tokens = []
        for word, tag in pos_tag(tokens):
            cleaned_word = re.sub(r'[^a-zA-Z]', '', word.lower())
            if cleaned_word:
                lemmatised_word = lemmatiser.lemmatize(cleaned_word, tag_map[tag[0]])
                if lemmatised_word not in lemmatized_stop_words:
                    lemmatised_tokens.append(lemmatised_word)
        return " ".join(lemmatised_tokens)
    return text


# Apply Level 1a preprocessing (for BERT)
dataMIMC['textMIMC_lvl1a'] = dataMIMC['descr_THOUGHT.text_spellchecked'].apply(
    lambda x: preprocessing_lvl1a(x, customStopWords, thoughtStopWords)
)

# Apply Level 1b preprocessing
dataMIMC['textMIMC_lvl1b'] = dataMIMC['descr_THOUGHT.text_spellchecked'].apply(
    lambda x: preprocessing_lvl1b(x, customStopWords)
)

# Apply Level 2a preprocessing (for TF-IDF)
dataMIMC['textMIMC_lvl2a'] = dataMIMC['descr_THOUGHT.text_spellchecked'].apply(
    lambda x: preprocessing_lvl2a(x, customStopWords, thoughtStopWords, nltk_stop_words, lemmatiser, tag_map)
)

# Apply Level 2b preprocessing
dataMIMC['textMIMC_lvl2b'] = dataMIMC['descr_THOUGHT.text_spellchecked'].apply(
    lambda x: preprocessing_lvl2b(x, customStopWords, nltk_stop_words, lemmatiser, tag_map)
)

# Display all text processing stages
print(dataMIMC[['descr_THOUGHT.text',
                  'descr_THOUGHT.text_spellchecked',
                  'textMIMC_lvl1a',
                  'textMIMC_lvl1b',
                  'textMIMC_lvl2a',
                  'textMIMC_lvl2b']])

# Save out for analyses and inspection
dataMIMC.to_csv(f'{base_path}/NLP_outputs/dataMIMC_preprocessed.csv', encoding='utf-8')

print("\nPreprocessing complete")
print("- 'textMIMC_lvl1a': Minimal filtering for BERT (custom stop words only)")
print("- 'textMIMC_lvl1b': Minimal filtering for BERT (stimuli stop words only)")
print("- 'textMIMC_lvl2a': Full preprocessing for TF-IDF (all stop words + lemmatisation)")
print("- 'textMIMC_lvl2b': Full preprocessing for TF-IDF (stimuli+NLTK stop words + lemmatisation)")
```

`dataMIMC` (saved out as `"dataMIMC_preprocessed.csv"`) now contains the preprocessed data from individual participants (one row = one MIMC) with the two levels of filtering: `MIMCdata_prepLVL1` and `MIMCdata_prepLVL2`. We will refer to this file for the NLP analyses.

---

## Creating Combined combMIMC

Here, we are combining the preprocessed MIMC descriptions into singular aggregated documents grouped by stimuli condition i.e. specific clip and context pairing. This produces 64 document combinations (16 clips × 4 contexts).

Where the individual preprocessed MIMC descriptions can be analysed to measure semantic similarity between *individual* thought descriptions, combMIMC can be analysed to measure semantic similarity between *aggregated representations* of conditions.

```{python}
# Initialise DataFrame for Level 1apreprocessed MIMC description
combMIMC_lvl1a = pd.DataFrame(index=range(0, 1), columns=dataMIMC.columns)
rowIndex = 0

for idStimPair in np.unique(dataMIMC['clip_context_PAIR']):
    stimPairMask = dataMIMC['clip_context_PAIR'] == idStimPair
    filt_ClipContextData = dataMIMC[stimPairMask]

    if len(filt_ClipContextData) > 0:
        first_row = filt_ClipContextData.iloc[0]
        idClip = first_row['clip_name']
        idContext = first_row['context_word']

        descrSeries = filt_ClipContextData['textMIMC_lvl1a']

        joinedstring = ""
        for ival in range(0, len(descrSeries.values)):
            joinedstring = joinedstring + str(descrSeries.values[ival]) + " endofinput "

        combMIMC_lvl1a.loc[rowIndex, 'textMIMC_lvl1a'] = joinedstring
        combMIMC_lvl1a.loc[rowIndex, 'clip_name'] = idClip
        combMIMC_lvl1a.loc[rowIndex, 'context_word'] = idContext
        combMIMC_lvl1a.loc[rowIndex, 'ClipContext_pair'] = idStimPair
        combMIMC_lvl1a.loc[rowIndex, 'GenreContext_pair'] = idStimPair[0:3] + "_" + idClip[0:3]
        if idClip[0:3] == '80s':
            combMIMC_lvl1a.loc[rowIndex, 'genre_code'] = '80s'
        elif idClip[0:3] == 'Jaz':
            combMIMC_lvl1a.loc[rowIndex, 'genre_code'] = 'Jaz'
        elif idClip[0:3] == 'Met':
            combMIMC_lvl1a.loc[rowIndex, 'genre_code'] = 'Met'
        elif idClip[0:3] == 'Ele':
            combMIMC_lvl1a.loc[rowIndex, 'genre_code'] = 'Ele'

        rowIndex = rowIndex + 1

# Initialise DataFrame for Level 1b preprocessed MIMC description
combMIMC_lvl1b = pd.DataFrame(index=range(0, 1), columns=dataMIMC.columns)
rowIndex = 0

for idStimPair in np.unique(dataMIMC['clip_context_PAIR']):
    stimPairMask = dataMIMC['clip_context_PAIR'] == idStimPair
    filt_ClipContextData = dataMIMC[stimPairMask]

    if len(filt_ClipContextData) > 0:
        first_row = filt_ClipContextData.iloc[0]
        idClip = first_row['clip_name']
        idContext = first_row['context_word']

        descrSeries = filt_ClipContextData['textMIMC_lvl1b']

        joinedstring = ""
        for ival in range(0, len(descrSeries.values)):
            joinedstring = joinedstring + str(descrSeries.values[ival]) + " endofinput "

        combMIMC_lvl1b.loc[rowIndex, 'textMIMC_lvl1b'] = joinedstring
        combMIMC_lvl1b.loc[rowIndex, 'clip_name'] = idClip
        combMIMC_lvl1b.loc[rowIndex, 'context_word'] = idContext
        combMIMC_lvl1b.loc[rowIndex, 'ClipContext_pair'] = idStimPair
        combMIMC_lvl1b.loc[rowIndex, 'GenreContext_pair'] = idStimPair[0:3] + "_" + idClip[0:3]
        if idClip[0:3] == '80s':
            combMIMC_lvl1b.loc[rowIndex, 'genre_code'] = '80s'
        elif idClip[0:3] == 'Jaz':
            combMIMC_lvl1b.loc[rowIndex, 'genre_code'] = 'Jaz'
        elif idClip[0:3] == 'Met':
            combMIMC_lvl1b.loc[rowIndex, 'genre_code'] = 'Met'
        elif idClip[0:3] == 'Ele':
            combMIMC_lvl1b.loc[rowIndex, 'genre_code'] = 'Ele'

        rowIndex = rowIndex + 1


# Initialise DataFrame for Level 2a preprocessed MIMC description
combMIMC_lvl2a = pd.DataFrame(index=range(0, 1), columns=dataMIMC.columns)
rowIndex = 0

for idStimPair in np.unique(dataMIMC['clip_context_PAIR']):
    stimPairMask = dataMIMC['clip_context_PAIR'] == idStimPair
    filt_ClipContextData = dataMIMC[stimPairMask]

    if len(filt_ClipContextData) > 0:
        first_row = filt_ClipContextData.iloc[0]
        idClip = first_row['clip_name']
        idContext = first_row['context_word']

        descrSeries = filt_ClipContextData['textMIMC_lvl2a']

        joinedstring = ""
        for ival in range(0, len(descrSeries.values)):
            joinedstring = joinedstring + str(descrSeries.values[ival]) + " endofinput "

        combMIMC_lvl2a.loc[rowIndex, 'textMIMC_lvl2a'] = joinedstring
        combMIMC_lvl2a.loc[rowIndex, 'clip_name'] = idClip
        combMIMC_lvl2a.loc[rowIndex, 'context_word'] = idContext
        combMIMC_lvl2a.loc[rowIndex, 'ClipContext_pair'] = idStimPair
        combMIMC_lvl2a.loc[rowIndex, 'GenreContext_pair'] = idStimPair[0:3] + "_" + idClip[0:3]
        if idClip[0:3] == '80s':
            combMIMC_lvl2a.loc[rowIndex, 'genre_code'] = '80s'
        elif idClip[0:3] == 'Jaz':
            combMIMC_lvl2a.loc[rowIndex, 'genre_code'] = 'Jaz'
        elif idClip[0:3] == 'Met':
            combMIMC_lvl2a.loc[rowIndex, 'genre_code'] = 'Met'
        elif idClip[0:3] == 'Ele':
            combMIMC_lvl2a.loc[rowIndex, 'genre_code'] = 'Ele'

        rowIndex = rowIndex + 1

# Initialise DataFrame for Level 2b preprocessed MIMC description
combMIMC_lvl2b = pd.DataFrame(index=range(0, 1), columns=dataMIMC.columns)
rowIndex = 0

for idStimPair in np.unique(dataMIMC['clip_context_PAIR']):
    stimPairMask = dataMIMC['clip_context_PAIR'] == idStimPair
    filt_ClipContextData = dataMIMC[stimPairMask]

    if len(filt_ClipContextData) > 0:
        first_row = filt_ClipContextData.iloc[0]
        idClip = first_row['clip_name']
        idContext = first_row['context_word']

        descrSeries = filt_ClipContextData['textMIMC_lvl2b']

        joinedstring = ""
        for ival in range(0, len(descrSeries.values)):
            joinedstring = joinedstring + str(descrSeries.values[ival]) + " endofinput "

        combMIMC_lvl2b.loc[rowIndex, 'textMIMC_lvl2b'] = joinedstring
        combMIMC_lvl2b.loc[rowIndex, 'clip_name'] = idClip
        combMIMC_lvl2b.loc[rowIndex, 'context_word'] = idContext
        combMIMC_lvl2b.loc[rowIndex, 'ClipContext_pair'] = idStimPair
        combMIMC_lvl2b.loc[rowIndex, 'GenreContext_pair'] = idStimPair[0:3] + "_" + idClip[0:3]
        if idClip[0:3] == '80s':
            combMIMC_lvl2b.loc[rowIndex, 'genre_code'] = '80s'
        elif idClip[0:3] == 'Jaz':
            combMIMC_lvl2b.loc[rowIndex, 'genre_code'] = 'Jaz'
        elif idClip[0:3] == 'Met':
            combMIMC_lvl2b.loc[rowIndex, 'genre_code'] = 'Met'
        elif idClip[0:3] == 'Ele':
            combMIMC_lvl2b.loc[rowIndex, 'genre_code'] = 'Ele'

        rowIndex = rowIndex + 1

# Filter and save
combMIMC_lvl1a = combMIMC_lvl1a.filter(['context_word', 'genre_code', 'clip_name', 'ClipContext_pair', 'GenreContext_pair', 'textMIMC_lvl1a'], axis=1)
combMIMC_lvl1a.to_csv(f'{base_path}/NLP_outputs/combMIMC_lvl1a.csv', encoding='utf-8')

combMIMC_lvl1b = combMIMC_lvl1b.filter(['context_word', 'genre_code', 'clip_name', 'ClipContext_pair', 'GenreContext_pair', 'textMIMC_lvl1b'], axis=1)
combMIMC_lvl1b.to_csv(f'{base_path}/NLP_outputs/combMIMC_lvl1b.csv', encoding='utf-8')

combMIMC_lvl2a = combMIMC_lvl2a.filter(['context_word', 'genre_code', 'clip_name', 'ClipContext_pair', 'GenreContext_pair', 'textMIMC_lvl2a'], axis=1)
combMIMC_lvl2a.to_csv(f'{base_path}/NLP_outputs/combMIMC_lvl2a.csv', encoding='utf-8')

combMIMC_lvl2b = combMIMC_lvl2b.filter(['context_word', 'genre_code', 'clip_name', 'ClipContext_pair', 'GenreContext_pair', 'textMIMC_lvl2b'], axis=1)
combMIMC_lvl2b.to_csv(f'{base_path}/NLP_outputs/combMIMC_lvl2b.csv', encoding='utf-8')


print(f"Created {len(combMIMC_lvl1a)} documents (Clip-Context combinations), combining Level 1a preprocessed MIMC descriptions")
print(combMIMC_lvl1a.head(5))

print(f"Created {len(combMIMC_lvl1b)} documents (Clip-Context combinations), combining Level 1b preprocessed MIMC descriptions")
print(combMIMC_lvl1b.head(5))

print(f"Created {len(combMIMC_lvl2a)} documents (Clip-Context combinations), combining Level 2a preprocessed MIMC descriptions")
print(combMIMC_lvl2a.head(5))

print(f"Created {len(combMIMC_lvl2b)} documents (Clip-Context combinations), combining Level 2b preprocessed MIMC descriptions")
print(combMIMC_lvl2b.head(5))
```

Text preprocessing is complete!

The saved out files `combMIMC_lvl1a.csv`, `combMIMC_lvl1b.csv`, `combMIMC_lvl2a.csv`, and `combMIMC_lvl2b.csv` will also be used alongside the `dataMIMC_preprocessed.csv` for the different levels of analysis in subsequent NLP analyses.

*(Reminder: LVL1 & LVL2 have thought words removed, LVL1A & LVL2A have thought words* kept in*.)*
