---
title: "Framed Listening: Sentence Embedding Analyses (individual MIMC level)"
author: "Hazel A. van der Walle (PhD student, Music, Durham University)"
date: "11 May 2026"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    theme: cosmo
---

All datasets generated and used for this study are openly available on GitHub:
<https://github.com/HazelvdW/context-framed-listening>.

This document analyses **semantic** similarity between individual music-influenced
mental content (MIMC) descriptions using sentence embeddings and cosine similarity.
It is the third pipeline in the analysis chain and the only one where all five
condition categories are fully available.

**Position in the analysis chain:**

| Document | Method | Level | N texts | RQ2b available? |
|---|---|---|---|---|
| `NLP-TFIDF-analysis.qmd` | TF-IDF | combMIMC (aggregated) | 64 | No |
| `NLP-SEmb-analysis.qmd` **(this doc)** | **Sentence embeddings** | **Individual MIMC** | **N per participant** | **Yes** |

At the individual level, each row is one participant's MIMC description for one
clip × context cell. This means `SC_SX` pairs (same clip, same context,
different participants) now exist and are fully populated, enabling RQ3b
(combined alignment advantage) to be tested for the first time in the pipeline.

**Model selection note**: `all-MiniLM-L6-v2` is used as the default model. 
It was fine-tuned specifically for semantic similarity on diverse sentence-level 
text and performs strongly on short inputs (3–128 tokens), matching the short 
length of individual MIMC descriptions. The model name is set in a single config 
variable below and can be swapped without modifying any other code — see the
model comparison note in the setup section for alternatives including mpnet.

Analyses mirror the aggregated combMIMC pipeline in structure, conditions, 
and research questions exactly.

---

## Setup

```{r setup-r}
#| echo: false

library(reticulate)

# Uncomment to install Python packages on first run:
 reticulate::py_install(c(
   "pandas", "numpy", "scipy", "scikit-learn",
   "matplotlib", "seaborn", "sentence-transformers", "torch"
 ), pip = TRUE)
```

```{python setup-python}
#| echo: false

import os
import numpy as np
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
from itertools import combinations
from matplotlib.patches import Patch

from sklearn.metrics.pairwise import cosine_similarity
from sklearn.decomposition    import TruncatedSVD
from sklearn.manifold         import TSNE
from scipy                    import stats
from scipy.stats              import kruskal, mannwhitneyu
from sentence_transformers    import SentenceTransformer, models as st_models

# ── Paths ─────────────────────────────────────────────────────────────────────
base_path  = (
    "/Users/hazelaileenvanderwalle/Library/CloudStorage/"
    "OneDrive-Personal/work/study/PhD/_PROJECT/"
    "_framedListening_NLP/context-framed-listening"
)
output_dir = f"{base_path}/NLP_outputs/SentenceEmbedding"
os.makedirs(output_dir, exist_ok=True)
print(f"Output directory: {output_dir}")
```

```{python version-check}
#| echo: false

# ── Environment version check ─────────────────────────────────────────────────
import importlib, sys
from packaging.version import Version

REQUIREMENTS = {
    "numpy":                 "1.26",
    "pandas":                "2.1",
    "scipy":                 "1.11",
    "sklearn":               "1.3",   # scikit-learn
    "matplotlib":            "3.8",
    "seaborn":               "0.13",
    "sentence_transformers": "2.7",   # sentence-transformers
    "torch":                 "2.1",
}

print(f"Python {sys.version}")
print("-" * 52)
all_ok = True
for pkg, min_ver in REQUIREMENTS.items():
    try:
        mod = importlib.import_module(pkg)
        ver = getattr(mod, "__version__", "unknown")
        ok  = Version(ver) >= Version(min_ver) if ver != "unknown" else True
        status = "OK" if ok else f"WARNING — expected >={min_ver}"
        if not ok:
            all_ok = False
        print(f"  {pkg:<26} {ver:<12} {status}")
    except ImportError:
        print(f"  {pkg:<26} NOT INSTALLED  ERROR")
        all_ok = False
if all_ok:
    print("\nAll package versions OK.")
else:
    print("\nOne or more issues — run: pip install -r requirements.txt")
```

```{python setup-python-MODEL}
#| echo: false

# ── Model configuration ────────────────────────────────────────────────────────
# Change MODEL_NAME here to swap model; all downstream code adjusts automatically.
#
# Recommended options for short text:
#   "sentence-transformers/all-MiniLM-L6-v2"    <- DEFAULT: fast, strong on short text
#   "...           /paraphrase-MiniLM-L3-v2"    <- lightest/fastest
#   "sentence-transformers/all-mpnet-base-v2"   <- higher quality, slower
#   "...           /paraphrase-mpnet-base-v2"   <- tuned for paraphrase detection and semantic equivalence
#   "vinai/bertweet-base"                       <- pretrained on tweets (short, informal)
#   "princeton-nlp/sup-simcse-roberta-base"     <- contrastive learning on NLI data
#
# Models on the sentence-transformers hub (ST_NATIVE = True) have pooling config
# baked in and load directly. Raw HuggingFace models (ST_NATIVE = False) need an
# explicit mean-pooling wrapper — this is handled automatically in the embed block.

MODEL_NAME    = "sentence-transformers/all-MiniLM-L6-v2"
MODEL_SLUG    = MODEL_NAME.split("/")[-1]   # used in filenames
MAX_SEQ_LEN   = 128                         # e.g. 128 MiniLM max; 512 for mpnet

# Prefixes whose models are natively packaged for sentence-transformers
ST_NATIVE = MODEL_NAME.startswith("sentence-transformers/")

print(f"Model:           {MODEL_NAME}")
print(f"Slug:            {MODEL_SLUG}")
print(f"Max seq length:  {MAX_SEQ_LEN}")
print(f"Native ST model: {ST_NATIVE}")
```

---

## Helper Functions

```{python helpers}
#| echo: false

def sig_marker(p):
    """Return significance marker string for a p-value."""
    if p < 0.001: return "***"
    if p < 0.01:  return "**"
    if p < 0.05:  return "*"
    return "n.s."


def welch_t(g1, g2):
    """Welch's t-test with Welch-Satterthwaite degrees of freedom.
    Returns (t, p, df, mean_diff, ci_low, ci_high)."""
    n1, n2 = len(g1), len(g2)
    v1, v2 = g1.var(ddof=1), g2.var(ddof=1)
    se     = np.sqrt(v1/n1 + v2/n2)
    t      = (g1.mean() - g2.mean()) / se
    df     = (v1/n1 + v2/n2)**2 / ((v1/n1)**2/(n1-1) + (v2/n2)**2/(n2-1))
    p      = 2 * (1 - stats.t.cdf(abs(t), df))
    # 95% CI on the mean difference
    t_crit    = stats.t.ppf(0.975, df)
    mean_diff = float(g1.mean() - g2.mean())
    ci_low    = mean_diff - t_crit * float(se)
    ci_high   = mean_diff + t_crit * float(se)
    return float(t), float(p), float(df), mean_diff, ci_low, ci_high


def cohens_d(g1, g2):
    """Compute Cohen's d effect size.
    NOTE: d benchmarks (small/medium/large) are not appropriate for pairwise
    similarity data where N is a function of N² responses. Report 95% CIs
    from welch_t() as the primary effect magnitude indicator; d is retained
    for completeness and cross-study comparison only."""
    pooled = np.sqrt((g1.std()**2 + g2.std()**2) / 2)
    return float((g1.mean() - g2.mean()) / pooled) if pooled > 0 else np.nan
```

---

## Data Preparation

### Load Data

Load **`dataMIMC_preprocessed.csv`** — individual-level preprocessed MIMC
descriptions, one row per participant × clip × context observation.

```{python load-data}
#| echo: false

data_path = f"{base_path}/NLP_outputs/dataMIMC_preprocessed.csv"
df        = pd.read_csv(data_path)

# Drop rows with missing text
n_before = len(df)
df = df.dropna(subset=["textMIMC_lvl1b"]).reset_index(drop=True)
n_after  = len(df)
if n_before != n_after:
    print(f"Dropped {n_before - n_after} rows with missing textMIMC_lvl1b")

print(f"Shape:   {df.shape}")
print(f"Columns: {df.columns.tolist()}")
print(f"\nUnique clips:  {sorted(df['clip_name'].unique())}")
print(f"Unique contexts: {sorted(df['context_word'].unique())}")
print(f"Unique genres:   {sorted(df['clip_genre'].unique())}")
print(f"\nTotal individual MIMC responses: {len(df)}")

# Descriptive summary of text length
df["text_len_words"] = df["textMIMC_lvl1b"].str.split().str.len()
print(f"\nText length (words):")
print(f"  Min:    {df['text_len_words'].min()}")
print(f"  Median: {df['text_len_words'].median():.0f}")
print(f"  Mean:   {df['text_len_words'].mean():.1f}")
print(f"  Max:    {df['text_len_words'].max()}")
print(f"  Texts > {MAX_SEQ_LEN} tokens (approx): "
      f"{(df['text_len_words'] > MAX_SEQ_LEN * 0.75).sum()}  "
      f"(word count is a rough proxy for token count)")

df.head(4)
```

### Sentence Embeddings

Encode each individual MIMC description using the configured model. Embeddings are
cached to disk keyed to the model slug so re-runs skip encoding entirely, and
switching models automatically triggers a fresh encode.

```{python embed}
#| echo: false

embed_path = f"{output_dir}/embeddings_{MODEL_SLUG}.npy"

if os.path.exists(embed_path):
    embeddings = np.load(embed_path)
    print(f"Loaded cached embeddings: {embeddings.shape}  ({MODEL_SLUG})")
else:
    print(f"Encoding {len(df)} texts with {MODEL_NAME} ...")
    model = SentenceTransformer(MODEL_NAME)
    model.max_seq_length = MAX_SEQ_LEN
    embeddings = model.encode(
        df["textMIMC_lvl1b"].tolist(),
        batch_size        = 64,
        show_progress_bar = True,
        convert_to_numpy  = True,
        normalize_embeddings = True    # L2 normalise -> cosine sim = dot product
    )
    np.save(embed_path, embeddings)
    print(f"Saved embeddings: {embeddings.shape}  ->  {embed_path}")

print(f"\nEmbedding matrix: {embeddings.shape[0]} texts × {embeddings.shape[1]} dims")
print(f"L2 norms (should be ~1.0): "
      f"min={np.linalg.norm(embeddings, axis=1).min():.4f}  "
      f"max={np.linalg.norm(embeddings, axis=1).max():.4f}")
```

### Pairwise Similarity by Condition

At the individual level the full N×N pairwise matrix is too large to hold in memory
if N is large. Similarities are instead computed in batches and written directly to
the condition records, avoiding materialising the full matrix.

Each pair is annotated with the same five condition labels as the combMIMC pipeline.
Because participants contribute one response per cell, `SC_SX` pairs now
exist: two different participants who heard the same clip under the same context
label.

> **Note on non-independence**: pairs at the individual level are not independent —
> each participant's response appears in multiple pairs. This is the same structure
> as the combMIMC pairwise comparisons and is standard in semantic similarity
> research of this kind. Welch's t-tests are used as in the combMIMC pipeline;
> the pair is the unit of analysis.

| Condition | Description |
|---|---|
| `SC_SX` | Same clip, same context — **different participants** — combined alignment |
| `SC_dx` | Same clip, different context — isolates **clip** influence |
| `dc_SX_SG` | Different clip, same context, same genre |
| `dc_dx_SG` | Different clip, different context, same genre |
| `dc_SX_dg` | Different clip, same context, different genre — isolates **context** influence |
| `dc_dx_dg` | Entirely different — dissimilarity floor (observed lower bound) |

```{python extract-similarity}
#| echo: false

clips    = df["clip_name"].values
contexts = df["context_word"].values
genres   = df["clip_genre"].values
pids     = df["PROLIFIC_PID"].values
n        = len(df)

records = {k: [] for k in [
    "item_i", "item_j", "similarity",
    "same_clip", "same_context", "same_genre", "condition",
    "clip_i", "clip_j", "context_i", "context_j", "genre_i", "genre_j",
    "pid_i", "pid_j"
]}

# Batch dot-product similarity (embeddings are L2-normalised so dot = cosine)
BATCH = 256
for i in range(n):
    # Only upper triangle (j > i) to avoid duplicate pairs
    sims_row = embeddings[i] @ embeddings[i+1:].T   # shape: (n - i - 1,)
    for k, j in enumerate(range(i + 1, n)):
        sc = clips[i]    == clips[j]
        sx = contexts[i] == contexts[j]
        sg = genres[i]   == genres[j]

        if sc and sx:
            cond = "SC_SX"
        elif sc and not sx:
            cond = "SC_dx"
        elif not sc and sx and sg:
            cond = "dc_SX_SG"
        elif not sc and not sx and sg:
            cond = "dc_dx_SG"
        elif not sc and sx and not sg:
            cond = "dc_SX_dg"
        else:
            cond = "dc_dx_dg"

        records["item_i"].append(i)
        records["item_j"].append(j)
        records["similarity"].append(float(sims_row[k]))
        records["same_clip"].append(sc)
        records["same_context"].append(sx)
        records["same_genre"].append(sg)
        records["condition"].append(cond)
        records["context_i"].append(contexts[i])
        records["context_j"].append(contexts[j])
        records["genre_i"].append(genres[i])
        records["genre_j"].append(genres[j])
        records["clip_i"].append(clips[i])
        records["clip_j"].append(clips[j])
        records["pid_i"].append(pids[i])
        records["pid_j"].append(pids[j])

sim_df = pd.DataFrame(records)

print(f"Total unique pairs: {len(sim_df):,}")
print("\nCondition distribution:")
print(sim_df["condition"].value_counts().sort_index().to_string())

sim_df.to_csv(
    f"{output_dir}/similarity_by_condition_{MODEL_SLUG}.csv", index=False)

genre_list = sorted(df["clip_genre"].unique())
cntx_list   = sorted(df["context_word"].unique())
print("\nSaved similarity data")
```

```{python permutation-baseline}
#| echo: false

# ── Permutation baseline: chance similarity via random shuffling ───────────────
# The "dissimilarity floor" condition (dc_dx_dg) uses observed pairs
# from the experiment. A truly random baseline establishes what similarity would
# be expected by chance if item identity was shuffled entirely, with no relation
# to stimuli conditions. This provides a theoretically grounded null against which
# all condition means can be compared.
#
# Procedure: 1000 shuffles of the similarity column within the full sim_df.
# Each shuffle randomly reassigns similarity scores to pair indices, destroying
# any condition structure. The mean of each shuffle gives one null sample.
# The resulting distribution gives the expected similarity under H0 (no structure).

N_PERMS    = 1000
rng        = np.random.default_rng(42)
sims_all   = sim_df["similarity"].values.copy()
perm_means = np.array([
    rng.permutation(sims_all).mean() for _ in range(N_PERMS)
])

perm_mean   = perm_means.mean()
perm_sd     = perm_means.std()
perm_ci_low = np.percentile(perm_means, 2.5)
perm_ci_hi  = np.percentile(perm_means, 97.5)

print("PERMUTATION BASELINE (1000 shuffles)")
print("=" * 55)
print(f"  Mean similarity under H0:  {perm_mean:.4f}")
print(f"  SD of permutation means:   {perm_sd:.6f}")
print(f"  95% CI:                    [{perm_ci_low:.4f}, {perm_ci_hi:.4f}]")
print(f"\n  Compare to observed condition means:")
for cond in ["dc_dx_dg", "dc_SX_dg", "dc_dx_SG",
             "dc_SX_SG", "SC_dx", "SC_SX"]:
    m = sim_df.loc[sim_df["condition"] == cond, "similarity"].mean()
    if not np.isnan(m):
        diff = m - perm_mean
        print(f"  {cond:<30}  M={m:.4f}  vs H0: {diff:+.4f}")

# Save permutation results for use in R visualisations
perm_results = dict(
    perm_mean=float(perm_mean), perm_sd=float(perm_sd),
    perm_ci_low=float(perm_ci_low), perm_ci_hi=float(perm_ci_hi)
)
```

---
---

## Linear Mixed Models

Linear mixed models (LMMs) provide a complementary, model-based approach to the
pairwise t-tests above. The outcome is pairwise cosine similarity; fixed effects
are `context_comb` (the context labels from the pair) and `genre_comb` (the 
genres of items in the pair); `item_i` and `item_j` are included as a random 
intercept to account for the fact that each individual response appears in 
multiple pairs.

Three models are fitted in sequence. Model 1 tests main effects of context, genre, and clip — clip is included as both a fixed and random effect to separate clip-specific idiosyncrasies from the genre signal, since genre is fully nested within clip. Model 3 adds mean believability (from the supplementary study) as a covariate at the clip × context cell level (64 unique values, one per clip–context pairing) — this gives genuine within-context variation in believability and avoids the collinearity that would arise from collapsing to context-level means. Model 2 tests the context × genre interaction while retaining clip as a covariate. Model comparisons use likelihood ratio tests (ANOVA on nested models) to determine whether each additional term improves fit.

Following the LMMs, estimated marginal means (emmeans) unpack pairwise context
differences while controlling for genre. Finally, a Random Forest classifier and
a Linear Discriminant Analysis (LDA) are used to assess how well context condition
can be recovered from similarity scores alone.

### LMM setup & prep

```{r lmm-setup}
#| echo: false

# ── Packages ──────────────────────────────────────────────────────────────────
required <- c("lme4", "lmerTest", "MuMIn", "emmeans", "ggdist",
              "randomForest", "MASS", "dplyr", "ggplot2", "car")
for (pkg in required) {
  if (!requireNamespace(pkg, quietly = TRUE))
    install.packages(pkg, repos = "https://cloud.r-project.org")
  library(pkg, character.only = TRUE)
}

# Normalise emmeans CI column names — at large N emmeans uses asymp.LCL/UCL
# instead of lower.CL/upper.CL; this ensures ggplot code works consistently
fix_emm_ci <- function(df) {
  names(df)[names(df) == "asymp.LCL"] <- "lower.CL"
  names(df)[names(df) == "asymp.UCL"] <- "upper.CL"
  df
}

# ── Paths (inherit from Python session via reticulate base_path) ──────────────
base_path  <- paste0(
  "/Users/hazelaileenvanderwalle/Library/CloudStorage/",
  "OneDrive-Personal/work/study/PhD/_PROJECT/",
  "_framedListening_NLP/context-framed-listening"
)
output_dir <- file.path(base_path, "NLP_outputs", "SentenceEmbedding")

# Load pairwise similarity data (written by the Python chunk above)
# MODEL_SLUG is set in the Python session — use the same name here
model_slug  <- py$MODEL_SLUG   # pulls MODEL_SLUG from the Python environment
sim_df_path <- file.path(output_dir,
                         paste0("similarity_by_condition_",model_slug,".csv"))
sim_df      <- read.csv(sim_df_path, stringsAsFactors = FALSE)

cat("Loaded similarity data:", nrow(sim_df), "pairs\n")
cat("Columns:", paste(names(sim_df), collapse = ", "), "\n")
```

```{r lmm-prep}
#| echo: false

# Using sum-to-zero (effects) coding so no reference level is used —
# each coefficient represents deviation from the grand mean,
# anova() gives Type III tests for each level independently
options(contrasts = c("contr.sum", "contr.poly"))

# Define similarity pair combination variables
sim_df$genre_comb   <- paste0(sim_df$genre_i,  "_",sim_df$genre_j)
sim_df$context_comb <- paste0(sim_df$context_i,"_",sim_df$context_j)
sim_df$clip_comb    <- paste0(sim_df$clip_i,   "_",sim_df$clip_j)


cat("genre_comb levels:\n");     print(table(sim_df$genre_comb))
cat("\ncontext_comb levels:\n"); print(table(sim_df$context_comb))
# clip_comb levels levels not pasted as it's quite long

# Factor predictors — comb variables as factors for the LMMs
sim_df$genre_comb   <- factor(sim_df$genre_comb)
sim_df$context_comb <- factor(sim_df$context_comb)
sim_df$clip_comb    <- factor(sim_df$clip_comb)
sim_df$pid_i        <- factor(sim_df$pid_i)
sim_df$pid_j        <- factor(sim_df$pid_j)

cat("\nUnique participants (pid_i):", nlevels(sim_df$pid_i), "\n")
cat("Unique participants (pid_j):", nlevels(sim_df$pid_j), "\n")
cat("\ncontext_comb levels:", nlevels(sim_df$context_comb), "\n")
cat("\ngenre_comb levels:  ", nlevels(sim_df$genre_comb),   "\n")
cat("\nclip_comb levels:   ", nlevels(sim_df$clip_comb),    "\n")

# ── Believability covariate ───────────────────────────────────────────────────
supp_path <- file.path(base_path, "dataSUPPstudy.csv")
supp      <- read.csv(supp_path, stringsAsFactors = FALSE)

believe_cell <- supp |>
  group_by(clip_name, context_word) |>
  summarise(believability = mean(rating_likelihood.response, na.rm = TRUE),
            .groups = "drop")

believe_cell$clip_merge <- tolower(sapply(
  strsplit(sub("\\.mp3$", "", believe_cell$clip_name), "_"),
  function(x) {
    prefix <- switch(tolower(x[1]),
      "electronic" = "ele", "jazz" = "jaz", "metal" = "met", tolower(x[1]))
    paste(c(prefix, x[2], x[3]), collapse = "_")
  }
))
believe_cell$cntx_merge <- trimws(tolower(believe_cell$context_word))

# Merge believability for item i
sim_df$clip_i_merge <- trimws(tolower(as.character(sim_df$clip_i)))
sim_df$cntx_i_merge  <- trimws(tolower(as.character(sim_df$context_i)))

sim_df <- merge(sim_df, believe_cell[, c("clip_merge", "cntx_merge", "believability")],
                by.x = c("clip_i_merge", "cntx_i_merge"),
                by.y = c("clip_merge",   "cntx_merge"),
                all.x = TRUE)
names(sim_df)[names(sim_df) == "believability"] <- "believability_i"

# Merge believability for item j
sim_df$clip_j_merge <- trimws(tolower(as.character(sim_df$clip_j)))
sim_df$cntx_j_merge  <- trimws(tolower(as.character(sim_df$context_j)))

sim_df <- merge(sim_df, 
                believe_cell[, c("clip_merge", "cntx_merge", "believability")],
                by.x = c("clip_j_merge", "cntx_j_merge"),
                by.y = c("clip_merge",   "cntx_merge"),
                all.x = TRUE)
names(sim_df)[names(sim_df) == "believability"] <- "believability_j"

# Pair-level believability = mean of both items' cell ratings
sim_df$believability_pair <- rowMeans(
  sim_df[, c("believability_i", "believability_j")], na.rm = FALSE)

cat("\nRows with full pair believability:", sum(!is.na(sim_df$believability_pair)),
    "of", nrow(sim_df), "\n")
cat("Rows with NA (unmatched):", sum(is.na(sim_df$believability_pair)), "\n")
```

### LMM Models

```{r lmm-model-checks}
#| eval: false
#| echo: false

S <- summarise(group_by(sim_df,context_comb,genre_comb),
               M=mean(similarity,na.rm=TRUE),
               SD=sd(similarity,na.rm=TRUE))
  S

SC <- summarise(group_by(sim_df,context_comb),
                M=mean(similarity,na.rm=TRUE),
                SD=sd(similarity,na.rm=TRUE))
  SC

SG <- summarise(group_by(sim_df,genre_comb),
                M=mean(similarity,na.rm=TRUE),
                SD=sd(similarity,na.rm=TRUE))
  SG
```

#### Model 1: context + genre main effects

```{r lmm-model1}
#| eval: true
#| echo: false

cat("———MODEL 1: similarity ~ context_comb + genre_comb 
                 + (1 | clip_comb) + (1 | pid_i) + (1 | pid_j),———\n")

model1 <- lmer(similarity ~ context_comb + genre_comb 
               + (1 | clip_comb) + (1 | pid_i) + (1 | pid_j),
               data = sim_df, REML = FALSE)

print(anova(model1))
cat("\n———Omnibus fixed effects — no reference level———\n")
print(car::Anova(model1, type = 3))
cat("\n———Pseudo-R² (Nakagawa & Schielzeth), variance explained:———\n")
print(MuMIn::r.squaredGLMM(model1))

cat("\n———EMMean, context combos with 95% CI———\n")
emm1_ctx <- emmeans(model1, ~ context_comb)
print(summary(emm1_ctx, infer = c(TRUE, FALSE), level = 0.95))

cat("\n———EMMean, genre combos with 95% CI———\n")
emm1_gen <- emmeans(model1, ~ genre_comb)
print(summary(emm1_gen, infer = c(TRUE, FALSE), level = 0.95))

cat("\n———random effects variance check———\n")
print(summary(model1)$varcor)

# ── ggdist visualisation: context emmeans with 95% CI ─────────────────────────
emm1_ctx_df <- fix_emm_ci(as.data.frame(summary(
  emm1_ctx, infer = c(TRUE, FALSE), level = 0.95)))

emm1_ctx

p_emm1_ctx <- ggplot(emm1_ctx_df,
                      aes(x = reorder(context_comb, emmean), y = emmean)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.7, linewidth = 1, colour = "#2c7bb6") +
  geom_hline(yintercept = mean(emm1_ctx_df$emmean),
             linetype = "dashed", colour = "grey50", linewidth = 0.5) +
  coord_flip() +
  labs(title    = "Model 1: Estimated Marginal Means — Context Combination",
       subtitle = "Points = emmean; bars = 95% CI; dashed = grand mean",
       x = NULL, y = "Cosine similarity (emmean)") +
    scale_y_continuous(limits=c(.15,.2))+
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"))

print(p_emm1_ctx)
ggsave(file.path(output_dir, "emmeans_model1_context.png"),
       p_emm1_ctx, width = 10, height = 7, dpi = 300)

# ── ggdist visualisation: genre emmeans with 95% CI ───────────────────────────
emm1_gen_df <- fix_emm_ci(as.data.frame(summary(
  emm1_gen, infer = c(TRUE, FALSE), level = 0.95)))

p_emm1_gen <- ggplot(emm1_gen_df,
                      aes(x = reorder(genre_comb, emmean), y = emmean)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.7, linewidth = 1, colour = "#d7191c") +
  geom_hline(yintercept = mean(emm1_gen_df$emmean),
             linetype = "dashed", colour = "grey50", linewidth = 0.5) +
  coord_flip() +
  labs(title    = "Model 1: Estimated Marginal Means — Genre Combination",
       subtitle = "Points = emmean; bars = 95% CI; dashed = grand mean",
       x = NULL, y = "Cosine similarity (emmean)") +
    scale_y_continuous(limits=c(.15,.2))+
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"))

print(p_emm1_gen)
ggsave(file.path(output_dir, "emmeans_model1_genre.png"),
       p_emm1_gen, width = 10, height = 7, dpi = 300)

## ── COWPLOT ──────────────────────────────────────────────────────────────────
p_combined <- cowplot::plot_grid(p_emm1_ctx, p_emm1_gen, ncol = 1)
print(p_combined)
ggsave(file.path(output_dir, "emmeans_model1_ctx_genre_stacked.png"),
       p_combined, width = 10, height = 14, dpi = 300)

# ── Pairwise contrasts with 95% CI (Tukey) ────────────────────────────────────
cat("\n———Pairwise context contrasts (Tukey), with 95% CI———\n")
emm1_ctx_pairs <- pairs(emm1_ctx, adjust = "tukey")
print(summary(emm1_ctx_pairs, infer = c(TRUE, TRUE), level = 0.95))

# Forest-style plot of pairwise contrasts
emm1_pairs_df <- fix_emm_ci(as.data.frame(
  summary(emm1_ctx_pairs, infer = c(TRUE, TRUE), level = 0.95)))

p_contrasts1 <- ggplot(emm1_pairs_df,
                        aes(x = reorder(contrast, estimate), y = estimate)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.6, linewidth = 0.9,
                  colour = ifelse(emm1_pairs_df$p.value < 0.05,
                                  "#2c7bb6", "grey60")) +
  geom_hline(yintercept = 0, linetype = "dashed",
             colour = "grey30", linewidth = 0.5) +
  coord_flip() +
  labs(title    = "Model 1: Pairwise Context Contrasts",
       subtitle = "Blue = significant (p < .05, Tukey); bars = 95% CI; dashed = no difference",
       x = NULL, y = "Estimated difference in cosine similarity") +
  theme_minimal(base_size = 10) +
  theme(plot.title = element_text(face = "bold"))

print(p_contrasts1)
ggsave(file.path(output_dir, "emmeans_model1_contrasts.png"),
       p_contrasts1, width = 12, height = 40, dpi = 300, limitsize = FALSE)

### ── Option A: filtered forest plot — same-context vs same-context contrasts only
# Keep only contrasts where both conditions are same-context (xxx_xxx - yyy_yyy)
emm1_pairs_df <- fix_emm_ci(as.data.frame(
  summary(emm1_ctx_pairs, infer = c(TRUE, TRUE), level = 0.95)))

# Flag same-context pairs: both sides of contrast match pattern "word_word"
is_same_ctx <- function(label) {
  parts <- strsplit(label, " - ")[[1]]
  all(sapply(parts, function(p) {
    tokens <- strsplit(p, "_")[[1]]
    length(tokens) == 2 && tokens[1] == tokens[2]
  }))
}
emm1_pairs_key <- emm1_pairs_df[
  sapply(as.character(emm1_pairs_df$contrast), is_same_ctx), ]

# Clean contrast labels: "bar_bar - concert_concert" → "Bar vs Concert"
clean_label <- function(label) {
  parts  <- strsplit(label, " - ")[[1]]
  ctxs   <- sapply(parts, function(p) strsplit(p, "_")[[1]][1])
  paste0(tools::toTitleCase(ctxs[1]), " vs ", tools::toTitleCase(ctxs[2]))
}
emm1_pairs_key$label <- sapply(as.character(emm1_pairs_key$contrast), clean_label)

p_contrasts_key <- ggplot(emm1_pairs_key,
                            aes(x = reorder(label, estimate), y = estimate)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.8, linewidth = 1.1,
                  colour = ifelse(emm1_pairs_key$p.value < 0.05,
                                  "#2c7bb6", "grey60")) +
  geom_hline(yintercept = 0, linetype = "dashed",
             colour = "grey30", linewidth = 0.6) +
  coord_flip() +
  labs(title    = "Model 1: Same-Context Condition Contrasts",
       subtitle = "Pairwise differences between same-context emmeans\nBlue = significant (Tukey); bars = 95% CI",
       x = NULL, y = "Estimated difference in cosine similarity") +
  theme_minimal(base_size = 12) +
  theme(plot.title   = element_text(face = "bold"),
        axis.text.y  = element_text(size = 11))

print(p_contrasts_key)
ggsave(file.path(output_dir, "emmeans_model1_contrasts_key.png"),
       p_contrasts_key, width = 8, height = 5, dpi = 300)

### ── Option B: full pairwise heatmap — all 120 contrasts as a matrix
# Parse contrast labels into two columns
parse_contrast <- function(df) {
  parts  <- strsplit(as.character(df$contrast), " - ")
  df$cond_a <- sapply(parts, `[`, 1)
  df$cond_b <- sapply(parts, `[`, 2)
  df
}
emm1_hm <- parse_contrast(emm1_pairs_df)

# Make symmetric matrix (add mirrored rows)
emm1_hm_sym <- rbind(
  emm1_hm[, c("cond_a","cond_b","estimate","p.value")],
  data.frame(cond_a   = emm1_hm$cond_b,
             cond_b   = emm1_hm$cond_a,
             estimate = -emm1_hm$estimate,
             p.value  =  emm1_hm$p.value)
)
emm1_hm_sym$sig <- emm1_hm_sym$p.value < 0.05

# Order levels: same-context pairs first, then mixed
ctx_order <- c("bar_bar","concert_concert","movie_movie","videogame_videogame",
               sort(setdiff(unique(emm1_hm_sym$cond_a),
                            c("bar_bar","concert_concert",
                              "movie_movie","videogame_videogame"))))
emm1_hm_sym$cond_a <- factor(emm1_hm_sym$cond_a, levels = ctx_order)
emm1_hm_sym$cond_b <- factor(emm1_hm_sym$cond_b, levels = ctx_order)

# Clean axis labels: bar_bar → Bar–Bar
clean_comb <- function(x) {
  parts <- strsplit(as.character(x), "_")[[1]]
  paste0(tools::toTitleCase(parts[1]), "–", tools::toTitleCase(parts[2]))
}
axis_labels <- setNames(
  sapply(ctx_order, clean_comb), ctx_order)

p_heatmap <- ggplot(emm1_hm_sym,
                     aes(x = cond_b, y = cond_a, fill = estimate)) +
  geom_tile(colour = "white", linewidth = 0.3) +
  geom_point(data = subset(emm1_hm_sym, sig),
             aes(x = cond_b, y = cond_a),
             colour = "black", size = 0.6, inherit.aes = FALSE) +
  scale_fill_gradient2(low      = "#d73027",
                       mid      = "white",
                       high     = "#4575b4",
                       midpoint = 0,
                       name     = "Estimated\ndifference") +
  scale_x_discrete(labels = axis_labels) +
  scale_y_discrete(labels = axis_labels) +
  labs(title    = "Model 1: All Pairwise Context Contrasts",
       subtitle = "Fill = estimated difference in cosine similarity\nBlack dot = significant (p < .05, Tukey-adjusted)",
       x = NULL, y = NULL) +
  theme_minimal(base_size = 9) +
  theme(plot.title   = element_text(face = "bold", size = 11),
        axis.text.x  = element_text(angle = 45, hjust = 1, size = 7),
        axis.text.y  = element_text(size = 7),
        legend.position = "right",
        panel.grid   = element_blank())

print(p_heatmap)
ggsave(file.path(output_dir, "emmeans_model1_contrasts_heatmap.png"),
       p_heatmap, width = 11, height = 10, dpi = 300)
```

#### Model 2: context × genre interaction

```{r lmm-model2}
#| eval: true
#| echo: false

cat("\n———Model 2A: context_comb × genre_comb interaction (downsized sample)———\n")
# *NOTE: with 1.9M rows, context_comb * genre_comb generates 16×16 = 256
#        interaction terms — too much for memory with three random effects.
set.seed(41100)
sim_sub <- sim_df[sample(nrow(sim_df), 200000), ]

model2A <- lmer(similarity ~ context_comb * genre_comb 
                + (1 | pid_i) + (1 | pid_j),
                data = sim_sub, REML = FALSE)

print(anova(model2A))
cat("\n———Omnibus fixed effects — no reference level———\n")
print(car::Anova(model2A, type = 3))
cat("\n———Pseudo-R²:———\n")
print(MuMIn::r.squaredGLMM(model2A))
cat("\n———EMMean, context combos with 95% CI———\n")
emm2A_ctx <- emmeans(model2A, ~ context_comb)
print(summary(emm2A_ctx, infer = c(TRUE, FALSE), level = 0.95))
cat("\n———EMMean, genre combos with 95% CI———\n")
emm2A_gen <- emmeans(model2A, ~ genre_comb)
print(summary(emm2A_gen, infer = c(TRUE, FALSE), level = 0.95))
cat("\n———EMMean, context × genre cell means with 95% CI———\n")
emm2A_int <- emmeans(model2A, ~ context_comb | genre_comb)
print(summary(emm2A_int, infer = c(TRUE, FALSE), level = 0.95))
cat("\n———random effects variance check———\n")
print(summary(model2A)$varcor)

# ── ggdist interaction plot: context × genre emmeans 
emm2A_int_df <- fix_emm_ci(as.data.frame(
  summary(emm2A_int, infer = c(TRUE, FALSE), level = 0.95)))

# Extract genre_i for faceting (genre_comb = "GenreA_GenreB")
emm2A_int_df$genre_i    <- sub("_.*", "", emm2A_int_df$genre_comb)
emm2A_int_df$pair_type  <- ifelse(
  sub("_.*", "", emm2A_int_df$genre_comb) ==
  sub(".*_", "", emm2A_int_df$genre_comb),
  "Same genre", "Cross genre")

# Extract genre_j for colouring
emm2A_int_df$genre_j <- sub(".*_", "", emm2A_int_df$genre_comb)

# Genre colour palette — consistent throughout
genre_colours <- c(
  "80s"        = "#fc8b22",
  "Electronic" = "#86d202",
  "Jazz"       = "#9a89ea",
  "Metal"      = "#9e185b"
)

# ── Plot 1: faceted by genre_i, coloured by genre_j ──────────────────────────
p_emm2A_faceted <- ggplot(emm2A_int_df,
                            aes(x = context_comb, y = emmean,
                                colour = genre_j, group = genre_comb,
                                alpha  = pair_type,
                                linewidth = pair_type)) +
  geom_line() +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.45, linewidth = 0.5,
                  position = position_dodge(width = 0.25)) +
  scale_colour_manual(values = genre_colours, name = "Genre (item j)") +
  scale_alpha_manual(values = c("Same genre" = 1, "Cross genre" = 0.35),
                     guide = "none") +
  scale_linewidth_manual(values = c("Same genre" = 1.2, "Cross genre" = 0.5),
                         guide = "none") +
  facet_wrap(~ genre_i, ncol = 2,
             labeller = labeller(genre_i = c(
               "80s"        = "Genre i: 80s",
               "Electronic" = "Genre i: Electronic",
               "Jazz"       = "Genre i: Jazz",
               "Metal"      = "Genre i: Metal"))) +
  labs(title    = "Model 2A: Context × Genre Estimated Marginal Means",
       subtitle = paste0("Faceted by genre of item i; coloured by genre of item j\n",
                         "Thick opaque lines = same-genre pairs; thin faded = cross-genre"),
       x = "Context combination", y = "Cosine similarity (emmean)") +
  theme_minimal(base_size = 10) +
  theme(plot.title      = element_text(face = "bold"),
        axis.text.x     = element_text(angle = 35, hjust = 1, size = 8),
        strip.text      = element_text(face = "bold", size = 10),
        legend.position = "right",
        panel.spacing   = unit(1.2, "lines"))

print(p_emm2A_faceted)
ggsave(file.path(output_dir, "emmeans_model2A_faceted_genre_j.png"),
       p_emm2A_faceted, width = 14, height = 10, dpi = 300)

# ── Plot 2: Heatmap, full context_comb × genre_comb emmeans (256 cells) ───────
# Parse context_comb into context_i and context_j
emm2A_int_df$context_i <- sub("_.*", "", emm2A_int_df$context_comb)
emm2A_int_df$context_j <- sub(".*_", "", emm2A_int_df$context_comb)

# Order factors
ctx_order   <- c("bar", "concert", "movie", "videogame")
genre_order <- c("80s", "Electronic", "Jazz", "Metal")

emm2A_int_df$context_i <- factor(emm2A_int_df$context_i, levels = ctx_order)
emm2A_int_df$context_j <- factor(emm2A_int_df$context_j, levels = ctx_order)
emm2A_int_df$genre_i   <- factor(emm2A_int_df$genre_i,   levels = genre_order)
emm2A_int_df$genre_j   <- factor(emm2A_int_df$genre_j,   levels = genre_order)

# Build compound axis labels: "Bar × 80s", "Bar × Electronic" etc.
# x-axis = context_j × genre_j  |  y-axis = context_i × genre_i
emm2A_int_df$x_label <- paste0(tools::toTitleCase(as.character(emm2A_int_df$context_j)),
                                 "\n", emm2A_int_df$genre_j)
emm2A_int_df$y_label <- paste0(tools::toTitleCase(as.character(emm2A_int_df$context_i)),
                                 " × ", emm2A_int_df$genre_i)

# Order y-axis: group by genre_i then context_i
emm2A_int_df$y_label <- factor(emm2A_int_df$y_label,
  levels = rev(as.vector(outer(
    ctx_order,
    genre_order,
    function(c, g) paste0(tools::toTitleCase(c), " × ", g)
  ))))

# Order x-axis: context_j varies fastest within genre_j blocks
emm2A_int_df$x_label <- factor(emm2A_int_df$x_label,
  levels = as.vector(outer(
    ctx_order,
    genre_order,
    function(c, g) paste0(tools::toTitleCase(c), "\n", g)
  )))

p_hm_full <- ggplot(emm2A_int_df,
                     aes(x = x_label, y = y_label, fill = emmean)) +
  geom_tile(colour = "white", linewidth = 0.4) +
  # Genre block dividers on x-axis (vertical lines every 4 columns)
  geom_vline(xintercept = seq(4.5, 12.5, by = 4),
             colour = "grey20", linewidth = 0.8) +
  # Genre block dividers on y-axis (horizontal lines every 4 rows)
  geom_hline(yintercept = seq(4.5, 12.5, by = 4),
             colour = "grey20", linewidth = 0.8) +
  scale_fill_gradient2(low      = "#9e185b",
                       mid      = "#f5f0f5",
                       high     = "#2c7bb6",
                       midpoint = mean(emm2A_int_df$emmean),
                       name     = "Emmean\nsimilarity") +
  labs(title    = "Model 2A: Context × Genre Interaction — Full Emmeans Grid",
       subtitle = "Each cell = predicted cosine similarity for one context_comb × genre_comb combination\nThick lines separate genre blocks",
       x = "Context (item j) × Genre (item j)",
       y = "Context (item i) × Genre (item i)") +
  theme_minimal(base_size = 9) +
  theme(plot.title      = element_text(face = "bold", size = 11),
        axis.text.x     = element_text(angle = 45, hjust = 1, size = 7),
        axis.text.y     = element_text(size = 7),
        panel.grid      = element_blank(),
        legend.position = "right")

print(p_hm_full)
ggsave(file.path(output_dir, "emmeans_model2A_heatmap_full.png"),
       p_hm_full, width = 14, height = 12, dpi = 300)
```

```{r model-comparisons}
#| eval: true
#| echo: false

cat("\n———Model 1A vs Model 2A (downsized, context_comb × genre_comb interaction):———\n")
# Refit Model 1 on same downsized sample for a valid comparison with Model 2A
set.seed(41100)
sim_sub  <- sim_df[sample(nrow(sim_df), 200000), ]
model1A  <- lmer(similarity ~ context_comb + genre_comb
                 + (1 | pid_i) + (1 | pid_j),
                 data = sim_sub, REML = FALSE)
print(anova(model1A, model2A))

# *NB: model2A cannot be directly compared to model1 via anova() because
#      the random effects structures differ (model1 includes clip_comb).
```

### Supplementary Study — Does Believability Moderate the Context Effect?

LMM Model 3 adds pair-level believability as a covariate over the context and
genre main effects. This tests whether more believable clip–context pairings
produce more semantically similar MIMC, independent of the context and genre
structure already captured by Model 1.

```{r lmm-model3}
#| eval: true
#| echo: false

cat("\n———Model 3: similarity ~ context_comb + genre_comb + believability_pair———\n")
cat("  + (1 | clip_comb) + (1 | pid_i) + (1 | pid_j)\n")

model3 <- lmer(similarity ~ context_comb + genre_comb + believability_pair 
               + (1 | clip_comb) + (1 | pid_i) + (1 | pid_j),
               data = sim_df, REML = FALSE)

print(anova(model3))
cat("\n———Omnibus fixed effects — no reference level———\n")
print(car::Anova(model3, type = 3))
cat("\n———Pseudo-R² (Nakagawa & Schielzeth), variance explained:———\n")
print(MuMIn::r.squaredGLMM(model3))
cat("\n———EMMean, context combos with 95% CI———\n")
print(summary(emmeans(model3, ~ context_comb), infer = c(TRUE, FALSE), level = 0.95))
cat("\n———EMMean, genre combos with 95% CI———\n")
print(summary(emmeans(model3, ~ genre_comb), infer = c(TRUE, FALSE), level = 0.95))
cat("\n———random effects variance check———\n")
print(summary(model3)$varcor)

cat("\n———Model comparison — Model 1 vs Model 3 (believability_pair):———\n")
print(anova(model1, model3))
```

### Estimated Marginal Means

```{r emmeans}
#| eval: true
#| echo: false

# Install ggdist if needed
if (!requireNamespace("ggdist",   quietly = TRUE))
  install.packages("ggdist",   repos = "https://cloud.r-project.org")
if (!requireNamespace("patchwork", quietly = TRUE))
  install.packages("patchwork", repos = "https://cloud.r-project.org")
library(ggdist)
library(patchwork)

# Pull permutation null from Python for reference line in plots
perm_null <- py$perm_results$perm_mean
perm_lo   <- py$perm_results$perm_ci_low
perm_hi   <- py$perm_results$perm_ci_hi

# ── Model 2A emmeans (full data, context_comb × genre) ─────────────────────────
# summary(e, infer=TRUE) gives predicted means + SE + 95% CI + t/z tests
# This is safer than raw observed CIs because it accounts for random structure

cat("═══ EMMEANS: Model 2A — context_comb (marginal, downsized) ═══\n")
e_context <- emmeans(model2A, ~ context_comb)
cat("\nPredicted means + 95% CI (accounting for random structure):\n")
print(summary(e_context, infer = TRUE))

cat("\n═══ PAIRWISE CONTRASTS: context_comb (Tukey) ═══\n")
e_context_pairs <- emmeans(model2A, pairwise ~ context_comb, adjust = "tukey")
print(e_context_pairs$contrasts)

cat("\n═══ EMMEANS: Model 2A — genre_comb ═══\n")
e_genre <- emmeans(model2A, ~ genre_comb)
print(summary(e_genre, infer = TRUE))

cat("\n═══ PAIRWISE CONTRASTS: genre_comb (Tukey) ═══\n")
print(emmeans(model2A, pairwise ~ genre_comb, adjust = "tukey")$contrasts)

cat("\n═══ EMMEANS: context_comb × genre_comb cell means ═══\n")
e_cell <- emmeans(model2A, ~ context_comb | genre_comb)
print(summary(e_cell, infer = TRUE))

cat("\n═══ PAIRWISE CONTRASTS: context_comb within each genre_comb ═══\n")
print(emmeans(model2A, pairwise ~ context_comb | genre_comb, adjust = "tukey")$contrasts)

# ── Figure 1: emmeans mean + 95% CI, all conditions, with permutation null ────
# Uses ggdist::geom_pointinterval for clean CI display that correctly reflects
# the random structure via the model-based SE rather than raw observed SE

e_context_df       <- fix_emm_ci(as.data.frame(summary(e_context, infer = TRUE)))
e_context_df$label <- as.character(e_context_df$context_comb)

# Condition colour palette — consistent with Python plots
cond_colours <- c(
  "bar"       = "#9e1100",
  "concert"   = "#d7ec78",
  "movie"     = "#5f1c9e",
  "videogame" = "#7dc3ff"
)

p_context <- ggplot(e_context_df,
                     aes(x = reorder(label, emmean), y = emmean,
                         colour = label)) +
  geom_hline(yintercept = perm_null, linetype = "dashed",
             colour = "grey40", linewidth = 0.8) +
  annotate("rect", xmin = -Inf, xmax = Inf,
           ymin = perm_lo, ymax = perm_hi,
           fill = "grey70", alpha = 0.2) +
  annotate("text", x = 0.6, y = perm_null + 0.0005,
           label = sprintf("Permutation null (M=%.3f)", perm_null),
           hjust = 0, size = 3, colour = "grey40") +
  geom_pointinterval(aes(ymin = lower.CL, ymax = upper.CL),
                      size = 4, linewidth = 1.2) +
  scale_colour_manual(values = cond_colours, guide = "none") +
  scale_x_discrete(labels = c(
    "bar"       = "Bar",
    "concert"   = "Concert",
    "movie"     = "Movie",
    "videogame" = "Video\ngame")) +
  labs(title    = "Emmeans: context condition",
       subtitle = "Predicted mean cosine similarity ± 95% CI (model-based)\nDashed = permutation null; shaded = null 95% CI",
       x = NULL, y = "Predicted mean cosine similarity") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))

# ── Figure 2: emmeans context × genre interaction ─────────────────────────────
e_cell_df        <- fix_emm_ci(as.data.frame(summary(e_cell, infer = TRUE)))
e_cell_df$genre  <- as.character(e_cell_df$genre_comb)
e_cell_df$cntx   <- as.character(e_cell_df$context_comb)

genre_colours <- c(
  "80s"        = "#fc8a1e",
  "Electronic" = "#7dcea0",
  "Jazz"       = "#8552b6",
  "Metal"      = "#9e1100"
)

p_interaction <- ggplot(e_cell_df,
                         aes(x = cntx, y = emmean,
                             colour = genre, group = genre)) +
  geom_hline(yintercept = perm_null, linetype = "dashed",
             colour = "grey40", linewidth = 0.7) +
  geom_line(linewidth = 0.9, alpha = 0.8) +
  geom_pointinterval(aes(ymin = lower.CL, ymax = upper.CL),
                      position = position_dodge(width = 0.2),
                      size = 3, linewidth = 0.8) +
  scale_colour_manual(values = genre_colours, name = "Genre") +
  scale_x_discrete(labels = c(
    "bar"       = "Bar",
    "concert"   = "Concert",
    "movie"     = "Movie",
    "videogame" = "Video\ngame")) +
  labs(title    = "Emmeans: context × genre interaction",
       subtitle = "Predicted mean ± 95% CI; lines connect genre profiles across contexts",
       x = "Context condition", y = "Predicted mean cosine similarity") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))

# ── Combine and save ──────────────────────────────────────────────────────────
p_combined <- p_context + p_interaction +
  plot_annotation(
    title   = "Model-Based Emmeans: Similarity by Context and Genre",
    subtitle = sprintf("Model 2A (context_comb × genre_comb — %s",
                       py$MODEL_SLUG),
    theme   = theme(plot.title    = element_text(face = "bold", size = 14),
                    plot.subtitle = element_text(size = 10))
  )

ggsave(file.path(output_dir,
                 paste0("emmeans_context_genre_", py$MODEL_SLUG, ".png")),
       p_combined, width = 14, height = 6, dpi = 300)
print(p_combined)
cat("\nSaved emmeans figure\n")

# ── Model 2A emmeans (downsized, context_comb) for reference ──────────────────
cat("\n═══ EMMEANS: Model 2A — context_comb (downsized sample) ═══\n")
e_comb     <- emmeans(model2A, ~ context_comb)
e_comb_df  <- fix_emm_ci(as.data.frame(summary(e_comb, infer = TRUE)))
print(e_comb_df)

cat("\n═══ PAIRWISE CONTRASTS: context_comb ═══\n")
print(emmeans(model2A, pairwise ~ context_comb, adjust = "tukey")$contrasts)
```


---
---

## RQ1 — Does Context Shape MIMC Similarity?

**Logic**: Compare `dc_SX_dg` (different music, same context label) against
`dc_dx_dg` (everything different — the dissimilarity floor). If context
drives convergence, pairs sharing a context label should be more similar than pairs
sharing nothing.

### Omnibus Test

```{python omnibus-kruskal}
#| echo: false

all_conditions = [
    "SC_SX",
    "SC_dx",
    "dc_SX_SG",
    "dc_SX_dg",
    "dc_dx_SG",
    "dc_dx_dg",
]

cond_groups = [sim_df.loc[sim_df["condition"] == c, "similarity"].values
               for c in all_conditions if (sim_df["condition"] == c).any()]
valid_conds = [c for c in all_conditions if (sim_df["condition"] == c).any()]

H, p_kw = kruskal(*cond_groups)
print("OMNIBUS KRUSKAL–WALLIS TEST ACROSS ALL CONDITIONS")
print("=" * 60)
print(f"  H({len(valid_conds)-1}) = {H:.3f},  p = {p_kw:.4e}  {sig_marker(p_kw)}")
print(f"  Conditions tested: {valid_conds}")

print("\nPost-hoc pairwise Mann–Whitney U  (Bonferroni corrected)")
print("-" * 60)
posthoc_pairs   = list(combinations(range(len(valid_conds)), 2))
posthoc_results = []
for i, j in posthoc_pairs:
    g1, g2  = cond_groups[i], cond_groups[j]
    u, p_mw = mannwhitneyu(g1, g2, alternative="two-sided")
    d       = cohens_d(pd.Series(g1), pd.Series(g2))
    posthoc_results.append(dict(
        cond1=valid_conds[i], cond2=valid_conds[j],
        mean1=g1.mean(), mean2=g2.mean(),
        U=u, p=p_mw, d=d, n1=len(g1), n2=len(g2)
    ))

posthoc_df             = pd.DataFrame(posthoc_results)
posthoc_df["p_bonf"]   = (posthoc_df["p"] * len(posthoc_df)).clip(upper=1.0)
posthoc_df["sig_bonf"] = posthoc_df["p_bonf"].apply(sig_marker)
posthoc_df             = posthoc_df.sort_values("d", key=abs, ascending=False)

print(posthoc_df[["cond1","cond2","mean1","mean2","d","p","p_bonf","sig_bonf"]]
      .to_string(index=False))
posthoc_df.to_csv(
    f"{output_dir}/omnibus_posthoc_{MODEL_SLUG}.csv", index=False)
print(f"\nSaved omnibus post-hoc table")
```

### Context Effect: dc_SX_dg vs dc_dx_dg

```{python rq1-context-effect}
#| echo: false

cntx_sims   = sim_df.loc[sim_df["condition"] == "dc_SX_dg", "similarity"]
joint_sims  = sim_df.loc[sim_df["condition"] == "dc_SX_SG", "similarity"]
floor_sims  = sim_df.loc[sim_df["condition"] == "dc_dx_dg", "similarity"]
sgenre_sims = sim_df.loc[sim_df["condition"] == "dc_dx_SG", "similarity"]

t, p, df_val, mean_diff, ci_low, ci_high = welch_t(cntx_sims, floor_sims)
d                                        = cohens_d(cntx_sims, floor_sims)

# Joint context + genre alignment vs baseline
t_jt, p_jt, df_jt, md_jt, ci_lo_jt, ci_hi_jt = welch_t(joint_sims, floor_sims)
d_jt = cohens_d(joint_sims, floor_sims)

# Also compare same-genre vs dissimilarity floor (genre effect without context)
t_sg, p_sg, df_sg, md_sg, ci_lo_sg, ci_hi_sg = welch_t(sgenre_sims, floor_sims)
d_sg = cohens_d(sgenre_sims, floor_sims)

print("RQ1 — CONTEXT EFFECT")
print("=" * 65)
print(f"  Dissimilarity floor (dc_dx_dg)           M = {floor_sims.mean():.4f}  (N = {len(floor_sims):,})") 
print(f"  Same genre, diff all  (dc_dx_SG)         M = {sgenre_sims.mean():.4f} (N = {len(sgenre_sims):,})") 
print(f"  Same context, diff clip+genre (dc_SX_dg) M = {cntx_sims.mean():.4f}   (N = {len(cntx_sims):,})") 
print(f"  Same context+genre, diff clip (dc_SX_SG) M = {joint_sims.mean():.4f}  (N = {len(joint_sims):,})")

print(f"\n  Pure context vs floor (dc_SX_dg vs dc_dx_dg):")
print(f"    Mean diff = {mean_diff:+.4f},  95% CI [{ci_low:.4f}, {ci_high:.4f}]")
print(f"    Welch's t({df_val:.1f}) = {t:.3f},  p = {p:.4f}  {sig_marker(p)}")
print(f"    Cohen's d = {d:.3f}  [note: d benchmarks not appropriate for pairwise data]")

print(f"\n  Joint context+genre alignment vs floor (dc_SX_SG vs dc_dx_dg):")
print(f"    Mean diff = {md_jt:+.4f},  95% CI [{ci_lo_jt:.4f}, {ci_hi_jt:.4f}]")
print(f"    Welch's t({df_jt:.1f}) = {t_jt:.3f},  p = {p_jt:.4f}  {sig_marker(p_jt)}")
print(f"    Cohen's d = {d_jt:.3f}")

print(f"\n  Same-genre vs floor — genre effect independent of context (dc_dx_SG vs dc_dx_dg):")
print(f"    Mean diff = {md_sg:+.4f},  95% CI [{ci_lo_sg:.4f}, {ci_hi_sg:.4f}]")
print(f"    Welch's t({df_sg:.1f}) = {t_sg:.3f},  p = {p_sg:.4f}  {sig_marker(p_sg)}")
print(f"    Cohen's d = {d_sg:.3f}")

rq1_context = dict(
    mean_ctx=float(cntx_sims.mean()),   mean_joint=float(joint_sims.mean()),
    mean_base=float(floor_sims.mean()), mean_sgenre=float(sgenre_sims.mean()),
    delta=float(cntx_sims.mean()-floor_sims.mean()),
    mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
    t=t, df=df_val, p=p, sig=sig_marker(p), d=d,
    n_ctx=len(cntx_sims), n_base=len(floor_sims)
)
```

### Visualisation

```{python vis-rq1}
#| echo: false

# Condition order and display labels — updated throughout:
# "Baseline" → "Dissimilarity Floor" (observed dc_dx_dg condition)
# Added: dc_dx_SG (same genre, diff clip+context)
rq1_conds = [
    ("dc_dx_dg", "Dissimilarity\nFloor\n(All Diff)", "#95a5a6"),
    ("dc_dx_SG", "Same Genre\n(Diff Clip+Context)",  "#f39c12"),
    ("dc_SX_dg", "Same Context\n(Diff Clip+Genre)",  "#e74c3c"),
    ("dc_SX_SG", "Same Context_Genre\n(Diff Clip)",  "#e74c3c"),
    ("SC_dx",    "Same Clip\n(Diff Context)",        "#3498db"),
    ("SC_SX",    "Combined\n(Same Clip+Context)",    "#9b59b6"),
]
present_rq1 = [(c, lbl, col) for c, lbl, col in rq1_conds
               if (sim_df["condition"] == c).any()]

# Save condition means for the R emmeans visualisation below
cond_means_py = {
    c: {
        "mean": float(sim_df.loc[sim_df["condition"] == c, "similarity"].mean()),
        "n":    int((sim_df["condition"] == c).sum()),
        "label": lbl,
        "colour": col,
    }
    for c, lbl, col in present_rq1
}

# Violin plot (Panel B) — kept in Python for distribution shape
fig, ax2 = plt.subplots(figsize=(12, 6))
plot_data = pd.concat([
    sim_df.loc[sim_df["condition"] == c, ["similarity"]].assign(label=lbl)
    for c, lbl, _ in present_rq1
])
order_v   = [lbl for _, lbl, _ in present_rq1]
palette_v = {lbl: col for _, lbl, col in present_rq1}
sns.violinplot(data=plot_data, x="label", y="similarity",
               order=order_v, hue="label", palette=palette_v,
               legend=False, inner="box", linewidth=1.5, ax=ax2)

# Add permutation null reference line
ax2.axhline(perm_results["perm_mean"], color="black", linestyle="--",
            linewidth=1.5, alpha=0.7, label=f"Permutation null M={perm_results['perm_mean']:.3f}")
ax2.fill_between([-0.5, len(present_rq1) - 0.5],
                 perm_results["perm_ci_low"], perm_results["perm_ci_hi"],
                 alpha=0.12, color="black", label="Permutation 95% CI")
ax2.legend(fontsize=9, loc="upper left")
ax2.set_xlabel("")
ax2.set_ylabel("Cosine Similarity", fontsize=11)
ax2.set_title(f"Similarity Distributions by Condition  [{MODEL_SLUG}]\n"
              "(Black dashed = permutation null; shaded = 95% permutation CI)",
              fontsize=12, fontweight="bold")
ax2.grid(axis="y", alpha=0.3)

plt.tight_layout()
plt.savefig(f"{output_dir}/RQ1_violin_{MODEL_SLUG}.png",
            dpi=300, bbox_inches="tight")
plt.show()
print("Saved violin plot")
```

---

## RQ2 — Does Genre Moderate the Context Effect?

**Logic**: Two complementary tests. *Framing susceptibility*: per genre, how much
does sharing a context label raise similarity above the dissimilarity floor?
*Within-genre clip vs context dominance*: within each genre, does clip or context
drive more convergence? Model 2 (context × genre interaction) is presented here
as the model-based complement to these pairwise tests.

### Framing Susceptibility by Genre

```{python rq3-susceptibility}
#| echo: false

print("RQ2 — GENRE FRAMING SUSCEPTIBILITY")
print("=" * 70)
print("Framing gain = dc_SX_SG M  −  dc_dx_SG M  (per genre)")
print("-" * 70)

susceptibility_rows = []
for genre in genre_list:
    cntx_sims_g = sim_df.loc[
        (sim_df["condition"] == "dc_SX_SG") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(cntx_sims_g) == 0:
        cntx_sims_g = sim_df.loc[
            (sim_df["condition"] == "dc_SX_SG") &
            ((sim_df["genre_i"] == genre) | (sim_df["genre_j"] == genre)), "similarity"]
    baseline_g = sim_df.loc[
        (sim_df["condition"] == "dc_dx_SG") &
        (sim_df["genre_i"] == genre), "similarity"]

    if len(cntx_sims_g) > 1 and len(baseline_g) > 1:
        framing_gain = cntx_sims_g.mean() - baseline_g.mean()
        t, p, df_val, mean_diff, ci_low, ci_high = welch_t(cntx_sims_g, baseline_g)
        d            = cohens_d(cntx_sims_g, baseline_g)
        susceptibility_rows.append(dict(
            genre=genre,
            context_driven_mean=cntx_sims_g.mean(),
            baseline_mean=baseline_g.mean(),
            framing_gain=framing_gain,
            mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
            t=t, df=df_val, p=p, d=d,
            n_ctx=len(cntx_sims_g), n_base=len(baseline_g)
        ))
        print(f"  {genre.upper():14s}  Ctx M={cntx_sims_g.mean():.4f}  "
              f"Base M={baseline_g.mean():.4f}  "
              f"Gain={framing_gain:+.4f}  95% CI [{ci_low:.4f}, {ci_high:.4f}]  "
              f"d={d:.3f}  p={p:.4f}")

susceptibility_df = pd.DataFrame(susceptibility_rows)
if len(susceptibility_df) > 0:
    n_sus = len(susceptibility_df)
    susceptibility_df["p_bonf"]   = (susceptibility_df["p"] * n_sus).clip(upper=1.0)
    susceptibility_df["sig"]      = susceptibility_df["p"].apply(sig_marker)
    susceptibility_df["sig_bonf"] = susceptibility_df["p_bonf"].apply(sig_marker)
    susceptibility_df = susceptibility_df.sort_values("framing_gain", ascending=False)
    print(f"\nGenres ranked by framing susceptibility (highest to lowest):")
    for _, r in susceptibility_df.iterrows():
        print(f"  {r['genre'].upper():14s}  Gain={r['framing_gain']:+.4f}  "
              f"95% CI [{r['ci_low']:.4f}, {r['ci_high']:.4f}]  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")
    susceptibility_df.to_csv(
        f"{output_dir}/genre_framing_susceptibility_{MODEL_SLUG}.csv", index=False)
    print(f"\nSaved genre framing susceptibility table")
```

### Within-Genre Clip vs Context Dominance

```{python rq3-genre-moderator}
#| echo: false

print("RQ2 — WITHIN-GENRE CLIP vs CONTEXT DOMINANCE")
print("=" * 70)
print("Clip-driven:    SC_dx  (same clip, diff context, same genre)")
print("Context-driven: dc_SX_SG  (diff clip, same context, same genre)")
print("-" * 70)

mod_rows = []
for genre in genre_list:
    clip_sims_g = sim_df.loc[
        (sim_df["condition"] == "SC_dx") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    cntx_sims_g = sim_df.loc[
        (sim_df["condition"] == "dc_SX_SG") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(clip_sims_g) > 1 and len(cntx_sims_g) > 1:
        t, p, df_val, mean_diff, ci_low, ci_high = welch_t(clip_sims_g, cntx_sims_g)
        d            = cohens_d(clip_sims_g, cntx_sims_g)
        dominant     = "CLIP" if clip_sims_g.mean() > cntx_sims_g.mean() else "CONTEXT"
        mod_rows.append(dict(
            genre=genre,
            clip_mean=clip_sims_g.mean(), clip_sd=clip_sims_g.std(),
            context_mean=cntx_sims_g.mean(), context_sd=cntx_sims_g.std(),
            diff=clip_sims_g.mean()-cntx_sims_g.mean(),
            mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
            dominant=dominant,
            t=t, df=df_val, p=p, d=d,
            n_clip=len(clip_sims_g), n_context=len(cntx_sims_g)
        ))
        print(f"  {genre.upper():14s}  Clip M={clip_sims_g.mean():.4f}  "
              f"Ctx M={cntx_sims_g.mean():.4f}  "
              f"95% CI [{ci_low:.4f}, {ci_high:.4f}]  "
              f"-> {dominant:7s} dominant  d={d:.3f}  p={p:.4f}")

genre_mod_df = pd.DataFrame(mod_rows)
if len(genre_mod_df) > 0:
    n_mod = len(genre_mod_df)
    genre_mod_df["p_bonf"]   = (genre_mod_df["p"] * n_mod).clip(upper=1.0)
    genre_mod_df["sig"]      = genre_mod_df["p"].apply(sig_marker)
    genre_mod_df["sig_bonf"] = genre_mod_df["p_bonf"].apply(sig_marker)
    genre_mod_df.to_csv(
        f"{output_dir}/genre_clip_vs_context_moderator_{MODEL_SLUG}.csv", index=False)
    print(f"\nSaved within-genre clip vs context moderator table")
```

### Visualisation

```{python vis-rq3}
#| echo: false

print(f"susceptibility_df rows: {len(susceptibility_df)}")
print(f"genre_mod_df rows:      {len(genre_mod_df)}")
print(f"genre_list:             {genre_list}")
print(f"Conditions in sim_df:   {sim_df['condition'].unique().tolist()}")
print(f"Genres in sim_df (genre_i): {sim_df['genre_i'].unique().tolist()}")

# Check SC_dx same-genre pairs exist
for genre in genre_list:
    n_clip = len(sim_df.loc[
        (sim_df["condition"] == "SC_dx") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre)])
    n_ctx  = len(sim_df.loc[
        (sim_df["condition"] == "dc_SX_SG") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre)])
    print(f"  {genre}: SC_dx same-genre N={n_clip},  dc_SX_SG same-genre N={n_ctx}")

if len(susceptibility_df) > 0 and len(genre_mod_df) > 0:
    fig, axes = plt.subplots(1, 2, figsize=(16, 6))

    ax = axes[0]
    s  = susceptibility_df.sort_values("framing_gain", ascending=True)
    colors = ["#e74c3c" if g > 0 else "#95a5a6" for g in s["framing_gain"]]
    ax.barh(range(len(s)), s["framing_gain"], color=colors,
            edgecolor="black", alpha=0.85)
    ax.axvline(0, color="black", linewidth=1.5)
    ax.set_yticks(range(len(s)))
    ax.set_yticklabels(s["genre"].str.upper(), fontsize=11)
    ax.set_xlabel("Framing Gain\n(dc_SX_SG − dc_dx_SG)", fontsize=10)
    ax.set_title("A. Genre Framing Susceptibility\n(Higher = More Context-Sensitive)",
                 fontsize=13, fontweight="bold")
    for i, (_, row) in enumerate(s.iterrows()):
        x_off = 0.002 if row["framing_gain"] >= 0 else -0.002
        ha    = "left"  if row["framing_gain"] >= 0 else "right"
        ax.text(row["framing_gain"] + x_off, i, row["sig_bonf"],
                ha=ha, va="center", fontsize=10, fontweight="bold")
    ax.grid(axis="x", alpha=0.3)

    ax2 = axes[1]
    s2  = genre_mod_df.sort_values("diff", ascending=True)
    colors2 = ["#3498db" if d > 0 else "#e74c3c" for d in s2["diff"]]
    ax2.barh(range(len(s2)), s2["diff"], color=colors2,
             edgecolor="black", alpha=0.85)
    ax2.axvline(0,     color="black", linewidth=1.5)
    ax2.axvline( 0.05, color="gray",  linestyle="--", alpha=0.4)
    ax2.axvline(-0.05, color="gray",  linestyle="--", alpha=0.4)
    ax2.set_yticks(range(len(s2)))
    ax2.set_yticklabels(s2["genre"].str.upper(), fontsize=11)
    ax2.set_xlabel("Clip Mean − Context Mean\n(+ve = Clip dominant; −ve = Context dominant)",
                   fontsize=10)
    ax2.set_title("B. Clip vs Context Dominance by Genre\n(SC_dx vs dc_SX_SG)",
                  fontsize=13, fontweight="bold")
    for i, (_, row) in enumerate(s2.iterrows()):
        x_off = 0.003 if row["diff"] >= 0 else -0.003
        ha    = "left"  if row["diff"] >= 0 else "right"
        ax2.text(row["diff"] + x_off, i, row["sig_bonf"],
                 ha=ha, va="center", fontsize=10, fontweight="bold")
    fig.legend(
        handles=[Patch(facecolor="#3498db", label="Clip dominant"),
                 Patch(facecolor="#e74c3c", label="Context dominant")],
        loc="lower center", ncol=2, fontsize=10, bbox_to_anchor=(0.75, -0.06)
    )
    ax2.grid(axis="x", alpha=0.3)

    plt.suptitle(f"RQ2: Does Genre Moderate the Context Effect?  [{MODEL_SLUG} — individual]",
                 fontsize=14, fontweight="bold")
    plt.tight_layout()
    plt.savefig(f"{output_dir}/RQ2_genre_moderation_{MODEL_SLUG}.png",
                dpi=300, bbox_inches="tight")
    plt.show()
    print("Saved: RQ2 genre moderation plot")
```

---

## RQ3 — Does Music Clip or Context Drive Greater Convergence?

**Logic**: `SC_dx` (same clip, different contexts) isolates the music
contribution; `dc_SX_dg` (different clips, same context) isolates the context
contribution. RQ3b tests whether aligning both factors (`SC_SX`) produces
additional convergence beyond either alone — **this is the first pipeline in the
chain where this test is available**, as individual-level data provides within-cell
pairs across different participants.


### Clip vs Context (RQ3a)

```{python rq2-clip-vs-context}
#| echo: false

clip_sims = sim_df.loc[sim_df["condition"] == "SC_dx", "similarity"]
cntx_sims  = sim_df.loc[sim_df["condition"] == "dc_SX_dg", "similarity"]

t, p, df_val, mean_diff, ci_low, ci_high = welch_t(clip_sims, cntx_sims)
d                                          = cohens_d(clip_sims, cntx_sims)

rq2_primary = dict(
    mean_clip=float(clip_sims.mean()), mean_ctx=float(cntx_sims.mean()),
    diff=float(clip_sims.mean()-cntx_sims.mean()),
    mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
    t=t, df=df_val, p=p, sig=sig_marker(p), d=d,
    n_clip=len(clip_sims), n_ctx=len(cntx_sims)
)

print("RQ3a — CLIP vs CONTEXT")
print("=" * 60)
print(f"  SC_dx (clip-driven):    M = {rq2_primary['mean_clip']:.4f}  "
      f"(N = {rq2_primary['n_clip']:,})")
print(f"  dc_SX_dg (context-driven): M = {rq2_primary['mean_ctx']:.4f}  "
      f"(N = {rq2_primary['n_ctx']:,})")
print(f"  Mean difference = {mean_diff:+.4f},  95% CI [{ci_low:.4f}, {ci_high:.4f}]")
print(f"  Welch's t({df_val:.1f}) = {t:.3f},  p = {p:.4f}  {sig_marker(p)}")
print(f"  Cohen's d = {d:.3f}  [note: d benchmarks not appropriate for pairwise data]")
dominant = "CLIP" if rq2_primary["diff"] > 0 else "CONTEXT"
print(f"\n-> {dominant} drives greater MIMC similarity at the individual level")
```

### RQ3b — Combined Advantage: SC_SX vs Single-Factor Conditions

```{python rq2-combined}
#| echo: false

sc_sc = sim_df.loc[sim_df["condition"] == "SC_SX",  "similarity"]
sc_dc = sim_df.loc[sim_df["condition"] == "SC_dx",  "similarity"]
dc_sc = sim_df.loc[sim_df["condition"] == "dc_SX_dg",  "similarity"]

combined_comparisons = [
    ("SC_SX vs SC_dx",
     "Combined advantage over Clip-only",    sc_sc, sc_dc),
    ("SC_SX vs dc_SX_dg",
     "Combined advantage over Context-only", sc_sc, dc_sc),
]

n_comb = len(combined_comparisons)
print("RQ3b — COMBINED ALIGNMENT ADVANTAGE")
print("=" * 65)
print(f"  SC_SX  M={sc_sc.mean():.4f}  SD={sc_sc.std():.4f}  N={len(sc_sc):,}")
print(f"  SC_dx  M={sc_dc.mean():.4f}  SD={sc_dc.std():.4f}  N={len(sc_dc):,}")
print(f"  dc_SX_dg  M={dc_sc.mean():.4f}  SD={dc_sc.std():.4f}  N={len(dc_sc):,}")
print(f"\nWelch's t-tests  (Bonferroni k={n_comb},  alpha_adj={0.05/n_comb:.4f})")
print("-" * 65)

combined_rows = []
for label, description, g1, g2 in combined_comparisons:
    t, p, df_val, mean_diff, ci_low, ci_high = welch_t(g1, g2)
    d            = cohens_d(g1, g2)
    p_bonf       = min(p * n_comb, 1.0)
    print(f"\n  {description}")
    print(f"    Mean diff = {mean_diff:+.4f},  95% CI [{ci_low:.4f}, {ci_high:.4f}]")
    print(f"    Welch's t({df_val:.1f}) = {t:.3f}  "
          f"p = {p:.4f} {sig_marker(p)}  ->  "
          f"p_bonf = {p_bonf:.4f} {sig_marker(p_bonf)}  d = {d:.3f}")
    combined_rows.append(dict(
        comparison=label, description=description,
        mean_a=g1.mean(), mean_b=g2.mean(), delta=g1.mean()-g2.mean(),
        mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
        t=t, df=df_val, p=p, p_bonf=p_bonf,
        sig=sig_marker(p), sig_bonf=sig_marker(p_bonf), d=d
    ))

combined_df = pd.DataFrame(combined_rows)
combined_df.to_csv(
    f"{output_dir}/combined_advantage_{MODEL_SLUG}.csv", index=False)
print(f"\nSaved combined advantage table")
```

### Visualisation

```{python vis-rq2}
#| echo: false

fig, axes = plt.subplots(1, 2, figsize=(15, 6))

# Panel A: clip vs context
ax = axes[0]
clip_ci = stats.t.interval(0.95, len(clip_sims)-1,
                            loc=clip_sims.mean(), scale=stats.sem(clip_sims))
cntx_ci  = stats.t.interval(0.95, len(cntx_sims)-1,
                            loc=cntx_sims.mean(),  scale=stats.sem(cntx_sims))
means_rq2 = [clip_sims.mean(), cntx_sims.mean()]
errs_rq2  = [(clip_ci[1]-clip_ci[0])/2, (cntx_ci[1]-cntx_ci[0])/2]
groups    = ["Clip-Driven\n(Same Clip, Diff Ctx)", "Context-Driven\n(Diff Clip, Same Ctx)"]
cols_rq2  = ["#3498db", "#e74c3c"]

ax.bar(range(2), means_rq2, color=cols_rq2, edgecolor="black",
       linewidth=2, alpha=0.85, width=0.55)
ax.errorbar(range(2), means_rq2, yerr=errs_rq2, fmt="none",
            ecolor="black", capsize=8, capthick=2, linewidth=2)
ax.set_xticks(range(2))
ax.set_xticklabels(groups, fontsize=10)
ax.set_ylabel("Mean Cosine Similarity", fontsize=11)
ax.set_title("A. Clip vs Context  (RQ2a)\n(95% CI error bars)",
             fontsize=12, fontweight="bold")
mid_y = (means_rq2[0] + means_rq2[1]) / 2 + 0.005
ax.annotate("", xy=(0, mid_y), xytext=(1, mid_y),
            arrowprops=dict(arrowstyle="<->", lw=2, color="black"))
effect_text = (f"d = {rq2_primary['d']:.3f}  {rq2_primary['sig']}\n"
               f"Δ = {rq2_primary['diff']:+.4f}")
ax.text(0.5, mid_y + 0.008, effect_text, ha="center", fontsize=10,
        fontweight="bold",
        bbox=dict(boxstyle="round,pad=0.4", facecolor="lightyellow",
                  edgecolor="black", alpha=0.9))
ax.set_ylim([0, max(means_rq2) * 1.35])
ax.grid(axis="y", alpha=0.3, linestyle="--")

# Panel B: three-condition combined advantage bar
ax2 = axes[1]
three_conds = [
    (sc_dc, "Clip-only\n(SC_dx)",    "#3498db"),
    (dc_sc, "Context-only\n(dc_SX_dg)", "#e74c3c"),
    (sc_sc, "Combined\n(SC_SX)",     "#9b59b6"),
]
m3 = [g.mean() for g, _, _ in three_conds]
e3 = [(stats.t.interval(0.95, len(g)-1, loc=g.mean(), scale=stats.sem(g))[1] -
       stats.t.interval(0.95, len(g)-1, loc=g.mean(), scale=stats.sem(g))[0]) / 2
      for g, _, _ in three_conds]

ax2.bar(range(3), m3, color=[c for _, _, c in three_conds],
        edgecolor="black", alpha=0.85)
ax2.errorbar(range(3), m3, yerr=e3, fmt="none",
             ecolor="black", capsize=6, linewidth=2)
ax2.set_xticks(range(3))
ax2.set_xticklabels([l for _, l, _ in three_conds], fontsize=10)
ax2.set_ylabel("Mean Cosine Similarity", fontsize=11)
ax2.set_title("B. Combined Alignment Advantage  (RQ2b)\n(95% CI error bars)",
              fontsize=12, fontweight="bold")
ax2.grid(axis="y", alpha=0.3, linestyle="--")

# Annotate Bonferroni-corrected sig markers from combined_df
if len(combined_df) > 0:
    y_top = max(m3) + max(e3) + 0.01
    # Combined vs clip-only: bars 2 and 0
    ax2.plot([0, 2], [y_top, y_top], "k-", linewidth=1.2)
    ax2.text(1, y_top + 0.003,
             combined_df.loc[combined_df["description"].str.contains("Clip"), "sig_bonf"].values[0],
             ha="center", fontsize=10, fontweight="bold")
    # Combined vs context-only: bars 2 and 1
    y_top2 = y_top + 0.025
    ax2.plot([1, 2], [y_top2, y_top2], "k-", linewidth=1.2)
    ax2.text(1.5, y_top2 + 0.003,
             combined_df.loc[combined_df["description"].str.contains("Context"), "sig_bonf"].values[0],
             ha="center", fontsize=10, fontweight="bold")
    ax2.set_ylim([0, y_top2 + 0.05])

plt.suptitle(f"RQ3: Does Music or Context Drive Greater Convergence?  [{MODEL_SLUG} — individual]",
             fontsize=14, fontweight="bold")
plt.tight_layout()
plt.savefig(f"{output_dir}/RQ3_clip_vs_context_{MODEL_SLUG}.png",
            dpi=300, bbox_inches="tight")
plt.show()
```

---

## Summary

```{python summary, echo=FALSE}
#| echo: false

print(f"SUMMARY OF FINDINGS  [{MODEL_SLUG} — individual level]")
print("=" * 70)

print(f"\nRQ1 — Context Effect (dc_SX_dg vs dc_dx_dg dissimilarity floor):")
print(f"  Context-driven M={rq1_context['mean_ctx']:.4f}  |  "
      f"Dissimilarity floor M={rq1_context['mean_base']:.4f}")
print(f"  Delta={rq1_context['delta']:+.4f}  "
      f"t({rq1_context['df']:.1f})={rq1_context['t']:.3f}  "
      f"p={rq1_context['p']:.4f}  {rq1_context['sig']}  "
      f"d={rq1_context['d']:.3f}")

print(f"\nRQ2 — Genre Framing Susceptibility (ranked highest to lowest):")
if len(susceptibility_df) > 0:
    for _, r in susceptibility_df.iterrows():
        print(f"  {r['genre'].upper():14s}  Gain={r['framing_gain']:+.4f}  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")

if len(genre_mod_df) > 0:
    print(f"\nRQ2 — Within-Genre Clip vs Context Dominance:")
    for _, r in genre_mod_df.iterrows():
        print(f"  {r['genre'].upper():14s}  -> {r['dominant']:7s} dominant  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")

print(f"\nRQ3a — Clip vs Context (SC_dx vs dc_SX_dg):")
print(f"  Clip M={rq2_primary['mean_clip']:.4f}  |  Ctx M={rq2_primary['mean_ctx']:.4f}")
dominant = "CLIP" if rq2_primary["diff"] > 0 else "CONTEXT"
print(f"  Delta={rq2_primary['diff']:+.4f}  {dominant} dominant  "
      f"d={rq2_primary['d']:.3f}  {rq2_primary['sig']}")

print(f"\nRQ3b — Combined Advantage (SC_SX vs single-factor conditions):")
for _, r in combined_df.iterrows():
    print(f"  {r['description']}")
    print(f"    Delta={r['delta']:+.4f}  d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")
```

---

## Exploratory Analyses

> The analyses below do not map directly onto the three pre-specified research
> questions. They are retained as descriptive and methodological supplements that
> may be useful for characterising the data or for future exploratory work.

### Pairwise Context and Genre Comparisons

Tests whether specific context labels or genres differ from each other in how much
convergence they produce. Descriptive characterisation only.

```{python exploratory-pairwise}
#| echo: false

print("PAIRWISE CONTEXT COMPARISONS  (Bonferroni corrected)")
print("-" * 70)

cntx_pairs = []
for c1, c2 in combinations(cntx_list, 2):
    g1 = sim_df.loc[
        (sim_df["condition"] == "dc_SX_dg") &
        (sim_df["context_i"] == c1) & (sim_df["context_j"] == c1), "similarity"]
    g2 = sim_df.loc[
        (sim_df["condition"] == "dc_SX_dg") &
        (sim_df["context_i"] == c2) & (sim_df["context_j"] == c2), "similarity"]
    if len(g1) > 1 and len(g2) > 1:
        t, p, df_val, mean_diff, ci_low, ci_high = welch_t(g1, g2)
        d = cohens_d(g1, g2)
        cntx_pairs.append(dict(context1=c1, context2=c2,
                               mean1=g1.mean(), mean2=g2.mean(),
                               diff=g1.mean()-g2.mean(),
                               mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
                               t=t, df=df_val, p=p, d=d,
                               n1=len(g1), n2=len(g2)))

context_pairs_df = pd.DataFrame(cntx_pairs)
if len(context_pairs_df) > 0:
    context_pairs_df["p_bonf"]   = (context_pairs_df["p"] * len(context_pairs_df)).clip(upper=1.0)
    context_pairs_df["sig"]      = context_pairs_df["p"].apply(sig_marker)
    context_pairs_df["sig_bonf"] = context_pairs_df["p_bonf"].apply(sig_marker)
    context_pairs_df = context_pairs_df.sort_values("d", key=abs, ascending=False)
    print(context_pairs_df[["context1","context2","mean1","mean2","d",
                             "p","p_bonf","sig_bonf"]].to_string(index=False))
    context_pairs_df.to_csv(
        f"{output_dir}/context_pairwise_comparisons_{MODEL_SLUG}.csv", index=False)

print("\n\nPAIRWISE GENRE COMPARISONS  (Bonferroni corrected)")
print("-" * 70)

genre_pairs = []
for g1_lbl, g2_lbl in combinations(genre_list, 2):
    s1 = sim_df.loc[
        (sim_df["condition"] == "dc_dx_SG") &
        (sim_df["genre_i"] == g1_lbl) & (sim_df["genre_j"] == g1_lbl), "similarity"]
    s2 = sim_df.loc[
        (sim_df["condition"] == "dc_dx_SG") &
        (sim_df["genre_i"] == g2_lbl) & (sim_df["genre_j"] == g2_lbl), "similarity"]
    if len(s1) > 1 and len(s2) > 1:
        t, p, df_val, mean_diff, ci_low, ci_high = welch_t(s1, s2)
        d = cohens_d(s1, s2)
        genre_pairs.append(dict(genre1=g1_lbl, genre2=g2_lbl,
                                 mean1=s1.mean(), mean2=s2.mean(),
                                 diff=s1.mean()-s2.mean(),
                                 mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
                                 t=t, df=df_val, p=p, d=d,
                                 n1=len(s1), n2=len(s2)))

genre_pairs_df = pd.DataFrame(genre_pairs)
if len(genre_pairs_df) > 0:
    genre_pairs_df["p_bonf"]   = (genre_pairs_df["p"] * len(genre_pairs_df)).clip(upper=1.0)
    genre_pairs_df["sig"]      = genre_pairs_df["p"].apply(sig_marker)
    genre_pairs_df["sig_bonf"] = genre_pairs_df["p_bonf"].apply(sig_marker)
    genre_pairs_df = genre_pairs_df.sort_values("d", key=abs, ascending=False)
    print(genre_pairs_df[["genre1","genre2","mean1","mean2","d",
                           "p","p_bonf","sig_bonf"]].to_string(index=False))
    genre_pairs_df.to_csv(
        f"{output_dir}/genre_pairwise_comparisons_{MODEL_SLUG}.csv", index=False)
```

### Similarity Matrices

Full within/between similarity for context and genre.

```{python exploratory-similarity-matrices}
#| echo: false

cntx_within_exp = []
for ctx in cntx_list:
    sims = sim_df.loc[
        (sim_df["condition"] == "dc_SX_dg") &
        (sim_df["context_i"] == ctx) & (sim_df["context_j"] == ctx), "similarity"]
    if len(sims) > 0:
        cntx_within_exp.append(dict(context=ctx, mean=sims.mean()))
context_within_df = pd.DataFrame(cntx_within_exp)

genre_within_exp = []
for genre in genre_list:
    sims = sim_df.loc[
        (sim_df["condition"] == "dc_dx_SG") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(sims) > 0:
        genre_within_exp.append(dict(genre=genre, mean=sims.mean()))
genre_within_df = pd.DataFrame(genre_within_exp)

fig, axes = plt.subplots(1, 2, figsize=(16, 7))
for ax, within_df, fkey, meta_col, panel in [
    (axes[0], context_within_df, "context", "context_word", "A. Context Similarity Matrix"),
    (axes[1], genre_within_df,   "genre",   "clip_genre",   "B. Genre Similarity Matrix"),
]:
    labels = sorted(df[meta_col].unique())
    n_lbl  = len(labels)
    mat    = np.full((n_lbl, n_lbl), np.nan)
    for i, l1 in enumerate(labels):
        for j, l2 in enumerate(labels):
            if i == j:
                val = within_df.loc[within_df[fkey] == l1, "mean"].values
                mat[i, j] = val[0] if len(val) > 0 else np.nan
            else:
                mask = (
                    ((sim_df[f"{fkey}_i"] == l1) & (sim_df[f"{fkey}_j"] == l2)) |
                    ((sim_df[f"{fkey}_i"] == l2) & (sim_df[f"{fkey}_j"] == l1))
                )
                sims = sim_df.loc[mask, "similarity"]
                mat[i, j] = sims.mean() if len(sims) > 0 else np.nan
    if not np.all(np.isnan(mat)):
        sns.heatmap(mat, annot=True, fmt=".3f", cmap="YlOrRd",
                    xticklabels=labels, yticklabels=labels,
                    cbar_kws={"label": "Mean Similarity"},
                    mask=np.isnan(mat),
                    linewidths=0.5, linecolor="gray", ax=ax)
    ax.set_title(f"{panel}\n(Diagonal = Within-{fkey.capitalize()})",
                 fontsize=13, fontweight="bold")

plt.suptitle(f"Similarity Matrices: Context and Genre  [{MODEL_SLUG} — individual]",
             fontsize=15, fontweight="bold")
plt.tight_layout()
plt.savefig(f"{output_dir}/similarity_matrices_{MODEL_SLUG}.png",
            dpi=300, bbox_inches="tight")
plt.show()
```

### Individual-Level t-SNE

t-SNE of the sentence embedding space coloured by genre and context. At the
individual level this also reveals whether within-cell responses (same participant
condition) cluster together.

```{python exploratory-tsne}
#| echo: false

n_svd = min(50, embeddings.shape[1] - 1)
svd   = TruncatedSVD(n_components=n_svd, random_state=42)
X_svd = svd.fit_transform(embeddings)
print(f"SVD explained variance: {svd.explained_variance_ratio_.sum():.3f}  "
      f"({n_svd} components)")

try:
    perp = min(30, len(df) // 4)   # perplexity must be < N/4 for small datasets
    tsne = TSNE(n_components=2, perplexity=perp, max_iter=1000,
                random_state=42, init="pca", learning_rate="auto")
except TypeError:
    tsne = TSNE(n_components=2, perplexity=perp, n_iter=1000,
                random_state=42, init="pca", learning_rate="auto")
                
print(perp)

X_2d = tsne.fit_transform(X_svd)

tsne_df = df[["clip_name", "context_word", "clip_genre"]].copy().reset_index(drop=True)
tsne_df["TSNE1"] = X_2d[:, 0]
tsne_df["TSNE2"] = X_2d[:, 1]
tsne_df.to_csv(f"{output_dir}/tsne_coords_{MODEL_SLUG}.csv", index=False)

fig, ax = plt.subplots(figsize=(10, 8))
sns.scatterplot(data=tsne_df, x="TSNE1", y="TSNE2",
                hue="clip_genre", style="context_word",
                palette="tab10", s=60, alpha=0.7, ax=ax)
ax.set_title(f"t-SNE: Individual MIMC Embeddings  [{MODEL_SLUG}]",
             fontsize=13, fontweight="bold")
ax.legend(bbox_to_anchor=(1.05, 1), loc="upper left", borderaxespad=0.)
plt.tight_layout()
plt.savefig(f"{output_dir}/tsne_{MODEL_SLUG}.png", dpi=300, bbox_inches="tight")
plt.show()
print("Saved: individual t-SNE plot")
```

```{r env}
install.packages("renv")
renv::init()
renv::snapshot()
```