---
title: "Framed Listening: Sentence Embedding Analyses (individual MIMC level)"
author: "Hazel A. van der Walle (PhD student, Music, Durham University)"
date: "23 April 2026"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    theme: cosmo
---

All datasets generated and used for this study are openly available on GitHub:
<https://github.com/HazelvdW/context-framed-listening>.

This document analyses **semantic** similarity between individual music-influenced
mental content (MIMC) descriptions using sentence embeddings and cosine similarity.
It is the third pipeline in the analysis chain and the only one where all five
condition categories are fully available.

**Position in the analysis chain:**

| Document | Method | Level | N texts | RQ2b available? |
|---|---|---|---|---|
| `NLP-TFIDF-analysis.qmd` | TF-IDF | combMIMC (aggregated) | 64 | No |
| `NLP-SEmb-analysis.qmd` **(this doc)** | **Sentence embeddings** | **Individual MIMC** | **N per participant** | **Yes** |

At the individual level, each row is one participant's MIMC description for one
clip × context cell. This means `Sclip_Scontext` pairs (same clip, same context,
different participants) now exist and are fully populated, enabling RQ2b
(combined alignment advantage) to be tested for the first time in the pipeline.

**Model selection note**: `all-MiniLM-L6-v2` is used as the default model. 
It was fine-tuned specifically for semantic similarity on diverse sentence-level 
text and performs strongly on short inputs (3–128 tokens), matching the short 
length of individual MIMC descriptions. The model name is set in a single config 
variable below and can be swapped without modifying any other code — see the
model comparison note in the setup section for alternatives including mpnet.

Analyses mirror the combMIMC pipeline in structure, conditions, and research
questions exactly.

---

## Setup

```{r setup-r, echo=FALSE}
library(reticulate)

# Uncomment to install Python packages on first run:
 reticulate::py_install(c(
   "pandas", "numpy", "scipy", "scikit-learn",
   "matplotlib", "seaborn", "sentence-transformers", "torch"
 ), pip = TRUE)
```

```{python setup-python, echo=FALSE}
import os
import numpy as np
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
from itertools import combinations
from matplotlib.patches import Patch

from sklearn.metrics.pairwise import cosine_similarity
from sklearn.decomposition    import TruncatedSVD
from sklearn.manifold         import TSNE
from scipy                    import stats
from scipy.stats              import kruskal, mannwhitneyu
from sentence_transformers    import SentenceTransformer, models as st_models

# ── Paths ─────────────────────────────────────────────────────────────────────
base_path  = (
    "/Users/hazelaileenvanderwalle/Library/CloudStorage/"
    "OneDrive-Personal/work/study/PhD/_PROJECT/"
    "_framedListening_NLP/context-framed-listening"
)
output_dir = f"{base_path}/NLP_outputs/SentenceEmbedding"
os.makedirs(output_dir, exist_ok=True)
print(f"Output directory: {output_dir}")
```

```{python version-check, echo=FALSE}
# ── Environment version check ──────────────────────────────────────────────────
import importlib, sys
from packaging.version import Version

REQUIREMENTS = {
    "numpy":                "1.26",
    "pandas":               "2.1",
    "scipy":                "1.11",
    "sklearn":              "1.3",    # scikit-learn
    "matplotlib":           "3.8",
    "seaborn":              "0.13",
    "sentence_transformers": "2.7",   # sentence-transformers
    "torch":                "2.1",
}

print(f"Python {sys.version}")
print("-" * 52)
all_ok = True
for pkg, min_ver in REQUIREMENTS.items():
    try:
        mod = importlib.import_module(pkg)
        ver = getattr(mod, "__version__", "unknown")
        ok  = Version(ver) >= Version(min_ver) if ver != "unknown" else True
        status = "OK" if ok else f"WARNING — expected >={min_ver}"
        if not ok:
            all_ok = False
        print(f"  {pkg:<26} {ver:<12} {status}")
    except ImportError:
        print(f"  {pkg:<26} NOT INSTALLED  ERROR")
        all_ok = False
if all_ok:
    print("\nAll package versions OK.")
else:
    print("\nOne or more issues — run: pip install -r requirements.txt")
```

```{python setup-python-MODEL, echo=FALSE}
# ── Model configuration ────────────────────────────────────────────────────────
# Change MODEL_NAME here to swap model; all downstream code adjusts automatically.
#
# Recommended options for short text:
#   "sentence-transformers/all-MiniLM-L6-v2"    <- DEFAULT: fast, strong on short text
#   "...           /paraphrase-MiniLM-L3-v2"    <- lightest/fastest
#   "sentence-transformers/all-mpnet-base-v2"   <- higher quality, slower
#   "...           /paraphrase-mpnet-base-v2"   <- tuned for paraphrase detection and semantic equivalence
#   "vinai/bertweet-base"                       <- pretrained on tweets (short, informal)
#   "princeton-nlp/sup-simcse-roberta-base"     <- contrastive learning on NLI data
#
# Models on the sentence-transformers hub (ST_NATIVE = True) have pooling config
# baked in and load directly. Raw HuggingFace models (ST_NATIVE = False) need an
# explicit mean-pooling wrapper — this is handled automatically in the embed block.

MODEL_NAME    = "sentence-transformers/all-MiniLM-L6-v2"
MODEL_SLUG    = MODEL_NAME.split("/")[-1]   # used in filenames
MAX_SEQ_LEN   = 128                         # e.g. 128 MiniLM max; 512 for mpnet

# Prefixes whose models are natively packaged for sentence-transformers
ST_NATIVE = MODEL_NAME.startswith("sentence-transformers/")

print(f"Model:            {MODEL_NAME}")
print(f"Slug:             {MODEL_SLUG}")
print(f"Max seq length:   {MAX_SEQ_LEN}")
print(f"Native ST model:  {ST_NATIVE}")
```

---

## Helper Functions

```{python helpers}
def sig_marker(p):
    """Return significance marker string for a p-value."""
    if p < 0.001: return "***"
    if p < 0.01:  return "**"
    if p < 0.05:  return "*"
    return "n.s."


def welch_t(g1, g2):
    """Welch's t-test with Welch-Satterthwaite degrees of freedom.
    Returns (t, p, df)."""
    n1, n2 = len(g1), len(g2)
    v1, v2 = g1.var(ddof=1), g2.var(ddof=1)
    se     = np.sqrt(v1/n1 + v2/n2)
    t      = (g1.mean() - g2.mean()) / se
    df     = (v1/n1 + v2/n2)**2 / ((v1/n1)**2/(n1-1) + (v2/n2)**2/(n2-1))
    p      = 2 * (1 - stats.t.cdf(abs(t), df))
    return float(t), float(p), float(df)


def cohens_d(g1, g2):
    """Compute Cohen's d effect size."""
    pooled = np.sqrt((g1.std()**2 + g2.std()**2) / 2)
    return float((g1.mean() - g2.mean()) / pooled) if pooled > 0 else np.nan
```

---

## Data Preparation

### Load Data

Load **`dataMIMC_preprocessed.csv`** — individual-level preprocessed MIMC
descriptions, one row per participant × clip × context observation.

```{python load-data, echo=FALSE}
data_path = f"{base_path}/NLP_outputs/dataMIMC_preprocessed.csv"
df        = pd.read_csv(data_path)

# Drop rows with missing text
n_before = len(df)
df = df.dropna(subset=["textMIMC_lvl1a"]).reset_index(drop=True)
n_after  = len(df)
if n_before != n_after:
    print(f"Dropped {n_before - n_after} rows with missing textMIMC_lvl1a")

print(f"Shape:   {df.shape}")
print(f"Columns: {df.columns.tolist()}")
print(f"\nUnique clips:    {sorted(df['clip_name'].unique())}")
print(f"Unique contexts: {sorted(df['context_word'].unique())}")
print(f"Unique genres:   {sorted(df['clip_genre'].unique())}")
print(f"\nTotal individual MIMC responses: {len(df)}")

# Descriptive summary of text length
df["text_len_words"] = df["textMIMC_lvl1a"].str.split().str.len()
print(f"\nText length (words):")
print(f"  Min:    {df['text_len_words'].min()}")
print(f"  Median: {df['text_len_words'].median():.0f}")
print(f"  Mean:   {df['text_len_words'].mean():.1f}")
print(f"  Max:    {df['text_len_words'].max()}")
print(f"  Texts > {MAX_SEQ_LEN} tokens (approx): "
      f"{(df['text_len_words'] > MAX_SEQ_LEN * 0.75).sum()}  "
      f"(word count is a rough proxy for token count)")

df.head(4)
```

### Sentence Embeddings

Encode each individual MIMC description using the configured model. Embeddings are
cached to disk keyed to the model slug so re-runs skip encoding entirely, and
switching models automatically triggers a fresh encode.

```{python embed, echo=FALSE}
embed_path = f"{output_dir}/embeddings_{MODEL_SLUG}.npy"

if os.path.exists(embed_path):
    embeddings = np.load(embed_path)
    print(f"Loaded cached embeddings: {embeddings.shape}  ({MODEL_SLUG})")
else:
    print(f"Encoding {len(df)} texts with {MODEL_NAME} ...")
    model = SentenceTransformer(MODEL_NAME)
    model.max_seq_length = MAX_SEQ_LEN
    embeddings = model.encode(
        df["textMIMC_lvl1a"].tolist(),
        batch_size        = 64,
        show_progress_bar = True,
        convert_to_numpy  = True,
        normalize_embeddings = True    # L2 normalise -> cosine sim = dot product
    )
    np.save(embed_path, embeddings)
    print(f"Saved embeddings: {embeddings.shape}  ->  {embed_path}")

print(f"\nEmbedding matrix: {embeddings.shape[0]} texts × {embeddings.shape[1]} dims")
print(f"L2 norms (should be ~1.0): "
      f"min={np.linalg.norm(embeddings, axis=1).min():.4f}  "
      f"max={np.linalg.norm(embeddings, axis=1).max():.4f}")
```

### Pairwise Similarity by Condition

At the individual level the full N×N pairwise matrix is too large to hold in memory
if N is large. Similarities are instead computed in batches and written directly to
the condition records, avoiding materialising the full matrix.

Each pair is annotated with the same five condition labels as the combMIMC pipeline.
Because participants contribute one response per cell, `Sclip_Scontext` pairs now
exist: two different participants who heard the same clip under the same context
label.

> **Note on non-independence**: pairs at the individual level are not independent —
> each participant's response appears in multiple pairs. This is the same structure
> as the combMIMC pairwise comparisons and is standard in semantic similarity
> research of this kind. Welch's t-tests are used as in the combMIMC pipeline;
> the pair is the unit of analysis.

| Condition | Description |
|---|---|
| `Sclip_Scontext` | Same clip, same context — **different participants** — combined alignment |
| `Sclip_Dcontext` | Same clip, different context — isolates **clip** influence |
| `Dclip_Scontext` | Different clip, same context — isolates **context** influence |
| `Dclip_Dcontext_Sgenre` | Both different, same genre |
| `Dclip_Dcontext_Dgenre` | Entirely different — dissimilarity baseline |

```{python extract-similarity, echo=FALSE}
clips    = df["clip_name"].values
contexts = df["context_word"].values
genres   = df["clip_genre"].values
n        = len(df)

records = {k: [] for k in [
    "item_i", "item_j", "similarity",
    "same_clip", "same_context", "same_genre", "condition",
    "context_i", "context_j", "genre_i", "genre_j"
]}

# Batch dot-product similarity (embeddings are L2-normalised so dot = cosine)
BATCH = 256
for i in range(n):
    # Only upper triangle (j > i) to avoid duplicate pairs
    sims_row = embeddings[i] @ embeddings[i+1:].T   # shape: (n - i - 1,)
    for k, j in enumerate(range(i + 1, n)):
        sc = clips[i]    == clips[j]
        sx = contexts[i] == contexts[j]
        sg = genres[i]   == genres[j]

        if sc and sx:
            cond = "Sclip_Scontext"
        elif sc and not sx:
            cond = "Sclip_Dcontext"
        elif not sc and sx:
            cond = "Dclip_Scontext"
        else:
            cond = "Dclip_Dcontext_Sgenre" if sg else "Dclip_Dcontext_Dgenre"

        records["item_i"].append(i)
        records["item_j"].append(j)
        records["similarity"].append(float(sims_row[k]))
        records["same_clip"].append(sc)
        records["same_context"].append(sx)
        records["same_genre"].append(sg)
        records["condition"].append(cond)
        records["context_i"].append(contexts[i])
        records["context_j"].append(contexts[j])
        records["genre_i"].append(genres[i])
        records["genre_j"].append(genres[j])

sim_df = pd.DataFrame(records)

print(f"Total unique pairs: {len(sim_df):,}")
print("\nCondition distribution:")
print(sim_df["condition"].value_counts().sort_index().to_string())

sim_df.to_csv(
    f"{output_dir}/similarity_by_condition_{MODEL_SLUG}.csv", index=False)

genre_list = sorted(df["clip_genre"].unique())
ctx_list   = sorted(df["context_word"].unique())
print("\nSaved similarity data")
```

---

## RQ1 — Does Context Shape MIMC Similarity?

**Logic**: Compare `Dclip_Scontext` (different music, same context label) against
`Dclip_Dcontext_Dgenre` (everything different — the dissimilarity floor). If context
drives convergence, pairs sharing a context label should be more similar than pairs
sharing nothing.

### Omnibus Test

```{python omnibus-kruskal, echo=FALSE}
all_conditions = [
    "Sclip_Scontext",
    "Sclip_Dcontext",
    "Dclip_Scontext",
    "Dclip_Dcontext_Sgenre",
    "Dclip_Dcontext_Dgenre",
]

cond_groups = [sim_df.loc[sim_df["condition"] == c, "similarity"].values
               for c in all_conditions if (sim_df["condition"] == c).any()]
valid_conds = [c for c in all_conditions if (sim_df["condition"] == c).any()]

H, p_kw = kruskal(*cond_groups)
print("OMNIBUS KRUSKAL–WALLIS TEST ACROSS ALL CONDITIONS")
print("=" * 60)
print(f"  H({len(valid_conds)-1}) = {H:.3f},  p = {p_kw:.4e}  {sig_marker(p_kw)}")
print(f"  Conditions tested: {valid_conds}")

print("\nPost-hoc pairwise Mann–Whitney U  (Bonferroni corrected)")
print("-" * 60)
posthoc_pairs   = list(combinations(range(len(valid_conds)), 2))
posthoc_results = []
for i, j in posthoc_pairs:
    g1, g2  = cond_groups[i], cond_groups[j]
    u, p_mw = mannwhitneyu(g1, g2, alternative="two-sided")
    d       = cohens_d(pd.Series(g1), pd.Series(g2))
    posthoc_results.append(dict(
        cond1=valid_conds[i], cond2=valid_conds[j],
        mean1=g1.mean(), mean2=g2.mean(),
        U=u, p=p_mw, d=d, n1=len(g1), n2=len(g2)
    ))

posthoc_df             = pd.DataFrame(posthoc_results)
posthoc_df["p_bonf"]   = (posthoc_df["p"] * len(posthoc_df)).clip(upper=1.0)
posthoc_df["sig_bonf"] = posthoc_df["p_bonf"].apply(sig_marker)
posthoc_df             = posthoc_df.sort_values("d", key=abs, ascending=False)

print(posthoc_df[["cond1","cond2","mean1","mean2","d","p","p_bonf","sig_bonf"]]
      .to_string(index=False))
posthoc_df.to_csv(
    f"{output_dir}/omnibus_posthoc_{MODEL_SLUG}.csv", index=False)
print(f"\nSaved omnibus post-hoc table")
```

### Context Effect: Dclip_Scontext vs Dclip_Dcontext_Dgenre

```{python rq1-context-effect, echo=FALSE}
ctx_sims      = sim_df.loc[sim_df["condition"] == "Dclip_Scontext",       "similarity"]
baseline_sims = sim_df.loc[sim_df["condition"] == "Dclip_Dcontext_Dgenre", "similarity"]

t, p, df_val = welch_t(ctx_sims, baseline_sims)
d            = cohens_d(ctx_sims, baseline_sims)

print("RQ1 — CONTEXT EFFECT")
print("=" * 60)
print(f"  Dclip_Scontext         M = {ctx_sims.mean():.4f}  (N = {len(ctx_sims):,})")
print(f"  Dclip_Dcontext_Dgenre  M = {baseline_sims.mean():.4f}  (N = {len(baseline_sims):,})")
print(f"  Delta = {ctx_sims.mean() - baseline_sims.mean():+.4f}")
print(f"  Welch's t({df_val:.1f}) = {t:.3f},  p = {p:.4f}  {sig_marker(p)}")
print(f"  Cohen's d = {d:.3f}")

rq1_context = dict(
    mean_ctx=float(ctx_sims.mean()), mean_base=float(baseline_sims.mean()),
    delta=float(ctx_sims.mean()-baseline_sims.mean()),
    t=t, df=df_val, p=p, sig=sig_marker(p), d=d,
    n_ctx=len(ctx_sims), n_base=len(baseline_sims)
)
```

### Visualisation

```{python vis-rq1, echo=FALSE}
# All four conditions including Sclip_Scontext (now available at individual level)
rq1_conds = [
    ("Dclip_Dcontext_Dgenre", "Baseline\n(All Diff)",          "#95a5a6"),
    ("Dclip_Scontext",        "Same Context\n(Diff Clip)",     "#e74c3c"),
    ("Sclip_Dcontext",        "Same Clip\n(Diff Context)",     "#3498db"),
    ("Sclip_Scontext",        "Combined\n(Same Clip+Context)", "#9b59b6"),
]
present_rq1 = [(c, lbl, col) for c, lbl, col in rq1_conds
               if (sim_df["condition"] == c).any()]

fig, axes = plt.subplots(1, 2, figsize=(15, 6))

# Panel A: mean bars with 95% CI
ax = axes[0]
means_rq1, errs_rq1, lbls_rq1, cols_rq1 = [], [], [], []
for cond, lbl, col in present_rq1:
    g  = sim_df.loc[sim_df["condition"] == cond, "similarity"]
    ci = stats.t.interval(0.95, len(g)-1, loc=g.mean(), scale=stats.sem(g))
    means_rq1.append(g.mean())
    errs_rq1.append((ci[1]-ci[0])/2)
    lbls_rq1.append(lbl)
    cols_rq1.append(col)

ax.bar(range(len(means_rq1)), means_rq1, color=cols_rq1,
       edgecolor="black", alpha=0.85)
ax.errorbar(range(len(means_rq1)), means_rq1, yerr=errs_rq1,
            fmt="none", ecolor="black", capsize=6, linewidth=2)
ax.set_xticks(range(len(lbls_rq1)))
ax.set_xticklabels(lbls_rq1, fontsize=10)
ax.set_ylabel("Mean Cosine Similarity", fontsize=11)
ax.set_title("A. Mean Similarity by Condition\n(95% CI error bars)",
             fontsize=12, fontweight="bold")
ax.grid(axis="y", alpha=0.3)
if len(means_rq1) >= 2:
    y_brack = max(means_rq1) + max(errs_rq1) + 0.01
    ax.plot([0, 1], [y_brack, y_brack], "k-", linewidth=1.5)
    ax.text(0.5, y_brack + 0.003, rq1_context["sig"],
            ha="center", fontsize=11, fontweight="bold")

# Panel B: violin distributions
ax2 = axes[1]
plot_data = pd.concat([
    sim_df.loc[sim_df["condition"] == c, ["similarity"]].assign(label=lbl)
    for c, lbl, _ in present_rq1
])
order_v   = [lbl for _, lbl, _ in present_rq1]
palette_v = {lbl: col for _, lbl, col in present_rq1}
sns.violinplot(data=plot_data, x="label", y="similarity",
               order=order_v, hue="label", palette=palette_v,
               legend=False, inner="box", linewidth=1.5, ax=ax2)
ax2.set_xlabel("")
ax2.set_ylabel("Cosine Similarity", fontsize=11)
ax2.set_title("B. Similarity Distributions by Condition",
              fontsize=12, fontweight="bold")
ax2.grid(axis="y", alpha=0.3)

plt.suptitle(f"RQ1: Does Context Shape MIMC Similarity?  [{MODEL_SLUG} — individual]",
             fontsize=14, fontweight="bold")
plt.tight_layout()
plt.savefig(f"{output_dir}/RQ1_context_effect_{MODEL_SLUG}.png",
            dpi=300, bbox_inches="tight")
plt.show()
```

---

## RQ2 — Music or Context: Which Drives Greater Convergence?

**Logic**: `Sclip_Dcontext` (same clip, different contexts) isolates the music
contribution; `Dclip_Scontext` (different clips, same context) isolates the context
contribution. RQ2b tests whether aligning both factors (`Sclip_Scontext`) produces
additional convergence beyond either alone — **this is the first pipeline in the
chain where this test is available**, as individual-level data provides within-cell
pairs across different participants.

### Clip vs Context

```{python rq2-clip-vs-context, echo=FALSE}
clip_sims = sim_df.loc[sim_df["condition"] == "Sclip_Dcontext", "similarity"]
ctx_sims  = sim_df.loc[sim_df["condition"] == "Dclip_Scontext", "similarity"]

t, p, df_val = welch_t(clip_sims, ctx_sims)
d            = cohens_d(clip_sims, ctx_sims)

rq2_primary = dict(
    mean_clip=float(clip_sims.mean()), mean_ctx=float(ctx_sims.mean()),
    diff=float(clip_sims.mean()-ctx_sims.mean()),
    t=t, df=df_val, p=p, sig=sig_marker(p), d=d,
    n_clip=len(clip_sims), n_ctx=len(ctx_sims)
)

print("RQ2a — CLIP vs CONTEXT")
print("=" * 60)
print(f"  Sclip_Dcontext (clip-driven):    M = {rq2_primary['mean_clip']:.4f}  "
      f"(N = {rq2_primary['n_clip']:,})")
print(f"  Dclip_Scontext (context-driven): M = {rq2_primary['mean_ctx']:.4f}  "
      f"(N = {rq2_primary['n_ctx']:,})")
print(f"  Delta (clip − context): {rq2_primary['diff']:+.4f}")
print(f"  Welch's t({df_val:.1f}) = {t:.3f},  p = {p:.4f}  {sig_marker(p)}")
print(f"  Cohen's d = {d:.3f}")
dominant = "CLIP" if rq2_primary["diff"] > 0 else "CONTEXT"
print(f"\n-> {dominant} drives greater MIMC similarity at the individual level")
```

### RQ2b — Combined Advantage: Sclip_Scontext vs Single-Factor Conditions

```{python rq2-combined, echo=FALSE}
sc_sc = sim_df.loc[sim_df["condition"] == "Sclip_Scontext",  "similarity"]
sc_dc = sim_df.loc[sim_df["condition"] == "Sclip_Dcontext",  "similarity"]
dc_sc = sim_df.loc[sim_df["condition"] == "Dclip_Scontext",  "similarity"]

combined_comparisons = [
    ("Sclip_Scontext vs Sclip_Dcontext",
     "Combined advantage over Clip-only",    sc_sc, sc_dc),
    ("Sclip_Scontext vs Dclip_Scontext",
     "Combined advantage over Context-only", sc_sc, dc_sc),
]

n_comb = len(combined_comparisons)
print("RQ2b — COMBINED ALIGNMENT ADVANTAGE")
print("=" * 65)
print(f"  Sclip_Scontext  M={sc_sc.mean():.4f}  SD={sc_sc.std():.4f}  N={len(sc_sc):,}")
print(f"  Sclip_Dcontext  M={sc_dc.mean():.4f}  SD={sc_dc.std():.4f}  N={len(sc_dc):,}")
print(f"  Dclip_Scontext  M={dc_sc.mean():.4f}  SD={dc_sc.std():.4f}  N={len(dc_sc):,}")
print(f"\nWelch's t-tests  (Bonferroni k={n_comb},  alpha_adj={0.05/n_comb:.4f})")
print("-" * 65)

combined_rows = []
for label, description, g1, g2 in combined_comparisons:
    t, p, df_val = welch_t(g1, g2)
    d            = cohens_d(g1, g2)
    p_bonf       = min(p * n_comb, 1.0)
    print(f"\n  {description}")
    print(f"    Delta = {g1.mean()-g2.mean():+.4f}  "
          f"Welch's t({df_val:.1f}) = {t:.3f}  "
          f"p = {p:.4f} {sig_marker(p)}  ->  "
          f"p_bonf = {p_bonf:.4f} {sig_marker(p_bonf)}  d = {d:.3f}")
    combined_rows.append(dict(
        comparison=label, description=description,
        mean_a=g1.mean(), mean_b=g2.mean(), delta=g1.mean()-g2.mean(),
        t=t, df=df_val, p=p, p_bonf=p_bonf,
        sig=sig_marker(p), sig_bonf=sig_marker(p_bonf), d=d
    ))

combined_df = pd.DataFrame(combined_rows)
combined_df.to_csv(
    f"{output_dir}/combined_advantage_{MODEL_SLUG}.csv", index=False)
print(f"\nSaved combined advantage table")
```

### Visualisation

```{python vis-rq2, echo=FALSE}
fig, axes = plt.subplots(1, 2, figsize=(15, 6))

# Panel A: clip vs context
ax = axes[0]
clip_ci = stats.t.interval(0.95, len(clip_sims)-1,
                            loc=clip_sims.mean(), scale=stats.sem(clip_sims))
ctx_ci  = stats.t.interval(0.95, len(ctx_sims)-1,
                            loc=ctx_sims.mean(),  scale=stats.sem(ctx_sims))
means_rq2 = [clip_sims.mean(), ctx_sims.mean()]
errs_rq2  = [(clip_ci[1]-clip_ci[0])/2, (ctx_ci[1]-ctx_ci[0])/2]
groups    = ["Clip-Driven\n(Same Clip, Diff Ctx)", "Context-Driven\n(Diff Clip, Same Ctx)"]
cols_rq2  = ["#3498db", "#e74c3c"]

ax.bar(range(2), means_rq2, color=cols_rq2, edgecolor="black",
       linewidth=2, alpha=0.85, width=0.55)
ax.errorbar(range(2), means_rq2, yerr=errs_rq2, fmt="none",
            ecolor="black", capsize=8, capthick=2, linewidth=2)
ax.set_xticks(range(2))
ax.set_xticklabels(groups, fontsize=10)
ax.set_ylabel("Mean Cosine Similarity", fontsize=11)
ax.set_title("A. Clip vs Context  (RQ2a)\n(95% CI error bars)",
             fontsize=12, fontweight="bold")
mid_y = (means_rq2[0] + means_rq2[1]) / 2 + 0.005
ax.annotate("", xy=(0, mid_y), xytext=(1, mid_y),
            arrowprops=dict(arrowstyle="<->", lw=2, color="black"))
effect_text = (f"d = {rq2_primary['d']:.3f}  {rq2_primary['sig']}\n"
               f"Δ = {rq2_primary['diff']:+.4f}")
ax.text(0.5, mid_y + 0.008, effect_text, ha="center", fontsize=10,
        fontweight="bold",
        bbox=dict(boxstyle="round,pad=0.4", facecolor="lightyellow",
                  edgecolor="black", alpha=0.9))
ax.set_ylim([0, max(means_rq2) * 1.35])
ax.grid(axis="y", alpha=0.3, linestyle="--")

# Panel B: three-condition combined advantage bar
ax2 = axes[1]
three_conds = [
    (sc_dc, "Clip-only\n(Sclip_Dcontext)",    "#3498db"),
    (dc_sc, "Context-only\n(Dclip_Scontext)", "#e74c3c"),
    (sc_sc, "Combined\n(Sclip_Scontext)",     "#9b59b6"),
]
m3 = [g.mean() for g, _, _ in three_conds]
e3 = [(stats.t.interval(0.95, len(g)-1, loc=g.mean(), scale=stats.sem(g))[1] -
       stats.t.interval(0.95, len(g)-1, loc=g.mean(), scale=stats.sem(g))[0]) / 2
      for g, _, _ in three_conds]

ax2.bar(range(3), m3, color=[c for _, _, c in three_conds],
        edgecolor="black", alpha=0.85)
ax2.errorbar(range(3), m3, yerr=e3, fmt="none",
             ecolor="black", capsize=6, linewidth=2)
ax2.set_xticks(range(3))
ax2.set_xticklabels([l for _, l, _ in three_conds], fontsize=10)
ax2.set_ylabel("Mean Cosine Similarity", fontsize=11)
ax2.set_title("B. Combined Alignment Advantage  (RQ2b)\n(95% CI error bars)",
              fontsize=12, fontweight="bold")
ax2.grid(axis="y", alpha=0.3, linestyle="--")

# Annotate Bonferroni-corrected sig markers from combined_df
if len(combined_df) > 0:
    y_top = max(m3) + max(e3) + 0.01
    # Combined vs clip-only: bars 2 and 0
    ax2.plot([0, 2], [y_top, y_top], "k-", linewidth=1.2)
    ax2.text(1, y_top + 0.003,
             combined_df.loc[combined_df["description"].str.contains("Clip"), "sig_bonf"].values[0],
             ha="center", fontsize=10, fontweight="bold")
    # Combined vs context-only: bars 2 and 1
    y_top2 = y_top + 0.025
    ax2.plot([1, 2], [y_top2, y_top2], "k-", linewidth=1.2)
    ax2.text(1.5, y_top2 + 0.003,
             combined_df.loc[combined_df["description"].str.contains("Context"), "sig_bonf"].values[0],
             ha="center", fontsize=10, fontweight="bold")
    ax2.set_ylim([0, y_top2 + 0.05])

plt.suptitle(f"RQ2: Does Music or Context Drive Greater Convergence?  [{MODEL_SLUG} — individual]",
             fontsize=14, fontweight="bold")
plt.tight_layout()
plt.savefig(f"{output_dir}/RQ2_clip_vs_context_{MODEL_SLUG}.png",
            dpi=300, bbox_inches="tight")
plt.show()
```

---

## RQ3 — Does Genre Moderate the Context Effect?

**Logic**: Two complementary tests. *Framing susceptibility*: per genre, how much
does sharing a context label raise similarity above the dissimilarity floor?
*Within-genre clip vs context dominance*: within each genre, does clip or context
drive more convergence?

### Framing Susceptibility by Genre

```{python rq3-susceptibility, echo=FALSE}
print("RQ3 — GENRE FRAMING SUSCEPTIBILITY")
print("=" * 70)
print("Framing gain = Dclip_Scontext M  −  Dclip_Dcontext_Dgenre M  (per genre)")
print("-" * 70)

susceptibility_rows = []
for genre in genre_list:
    ctx_sims_g = sim_df.loc[
        (sim_df["condition"] == "Dclip_Scontext") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(ctx_sims_g) == 0:
        ctx_sims_g = sim_df.loc[
            (sim_df["condition"] == "Dclip_Scontext") &
            ((sim_df["genre_i"] == genre) | (sim_df["genre_j"] == genre)), "similarity"]
    baseline_g = sim_df.loc[
        (sim_df["condition"] == "Dclip_Dcontext_Dgenre") &
        (sim_df["genre_i"] == genre), "similarity"]

    if len(ctx_sims_g) > 1 and len(baseline_g) > 1:
        framing_gain = ctx_sims_g.mean() - baseline_g.mean()
        t, p, df_val = welch_t(ctx_sims_g, baseline_g)
        d            = cohens_d(ctx_sims_g, baseline_g)
        susceptibility_rows.append(dict(
            genre=genre,
            context_driven_mean=ctx_sims_g.mean(),
            baseline_mean=baseline_g.mean(),
            framing_gain=framing_gain,
            t=t, df=df_val, p=p, d=d,
            n_ctx=len(ctx_sims_g), n_base=len(baseline_g)
        ))
        print(f"  {genre.upper():14s}  Ctx M={ctx_sims_g.mean():.4f}  "
              f"Base M={baseline_g.mean():.4f}  "
              f"Gain={framing_gain:+.4f}  d={d:.3f}  p={p:.4f}")

susceptibility_df = pd.DataFrame(susceptibility_rows)
if len(susceptibility_df) > 0:
    n_sus = len(susceptibility_df)
    susceptibility_df["p_bonf"]   = (susceptibility_df["p"] * n_sus).clip(upper=1.0)
    susceptibility_df["sig"]      = susceptibility_df["p"].apply(sig_marker)
    susceptibility_df["sig_bonf"] = susceptibility_df["p_bonf"].apply(sig_marker)
    susceptibility_df = susceptibility_df.sort_values("framing_gain", ascending=False)
    print(f"\nGenres ranked by framing susceptibility (highest to lowest):")
    for _, r in susceptibility_df.iterrows():
        print(f"  {r['genre'].upper():14s}  Gain={r['framing_gain']:+.4f}  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")
    susceptibility_df.to_csv(
        f"{output_dir}/genre_framing_susceptibility_{MODEL_SLUG}.csv", index=False)
    print(f"\nSaved genre framing susceptibility table")
```

### Within-Genre Clip vs Context Dominance

```{python rq3-genre-moderator, echo=FALSE}
print("RQ3 — WITHIN-GENRE CLIP vs CONTEXT DOMINANCE")
print("=" * 70)
print("Clip-driven:    Sclip_Dcontext  (same clip, diff context, same genre)")
print("Context-driven: Dclip_Scontext  (diff clip, same context, same genre)")
print("-" * 70)

mod_rows = []
for genre in genre_list:
    clip_sims_g = sim_df.loc[
        (sim_df["condition"] == "Sclip_Dcontext") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    ctx_sims_g = sim_df.loc[
        (sim_df["condition"] == "Dclip_Scontext") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(clip_sims_g) > 1 and len(ctx_sims_g) > 1:
        t, p, df_val = welch_t(clip_sims_g, ctx_sims_g)
        d            = cohens_d(clip_sims_g, ctx_sims_g)
        dominant     = "CLIP" if clip_sims_g.mean() > ctx_sims_g.mean() else "CONTEXT"
        mod_rows.append(dict(
            genre=genre,
            clip_mean=clip_sims_g.mean(), clip_sd=clip_sims_g.std(),
            context_mean=ctx_sims_g.mean(), context_sd=ctx_sims_g.std(),
            diff=clip_sims_g.mean()-ctx_sims_g.mean(),
            dominant=dominant,
            t=t, df=df_val, p=p, d=d,
            n_clip=len(clip_sims_g), n_context=len(ctx_sims_g)
        ))
        print(f"  {genre.upper():14s}  Clip M={clip_sims_g.mean():.4f}  "
              f"Ctx M={ctx_sims_g.mean():.4f}  "
              f"-> {dominant:7s} dominant  d={d:.3f}  p={p:.4f}")

genre_mod_df = pd.DataFrame(mod_rows)
if len(genre_mod_df) > 0:
    n_mod = len(genre_mod_df)
    genre_mod_df["p_bonf"]   = (genre_mod_df["p"] * n_mod).clip(upper=1.0)
    genre_mod_df["sig"]      = genre_mod_df["p"].apply(sig_marker)
    genre_mod_df["sig_bonf"] = genre_mod_df["p_bonf"].apply(sig_marker)
    genre_mod_df.to_csv(
        f"{output_dir}/genre_clip_vs_context_moderator_{MODEL_SLUG}.csv", index=False)
    print(f"\nSaved within-genre clip vs context moderator table")
```

### Visualisation

```{python vis-rq3, echo=FALSE}
if len(susceptibility_df) > 0 and len(genre_mod_df) > 0:
    fig, axes = plt.subplots(1, 2, figsize=(16, 6))

    ax = axes[0]
    s  = susceptibility_df.sort_values("framing_gain", ascending=True)
    colors = ["#e74c3c" if g > 0 else "#95a5a6" for g in s["framing_gain"]]
    ax.barh(range(len(s)), s["framing_gain"], color=colors,
            edgecolor="black", alpha=0.85)
    ax.axvline(0, color="black", linewidth=1.5)
    ax.set_yticks(range(len(s)))
    ax.set_yticklabels(s["genre"].str.upper(), fontsize=11)
    ax.set_xlabel("Framing Gain\n(Dclip_Scontext − Dclip_Dcontext_Dgenre)", fontsize=10)
    ax.set_title("A. Genre Framing Susceptibility\n(Higher = More Context-Sensitive)",
                 fontsize=13, fontweight="bold")
    for i, (_, row) in enumerate(s.iterrows()):
        x_off = 0.002 if row["framing_gain"] >= 0 else -0.002
        ha    = "left"  if row["framing_gain"] >= 0 else "right"
        ax.text(row["framing_gain"] + x_off, i, row["sig_bonf"],
                ha=ha, va="center", fontsize=10, fontweight="bold")
    ax.grid(axis="x", alpha=0.3)

    ax2 = axes[1]
    s2  = genre_mod_df.sort_values("diff", ascending=True)
    colors2 = ["#3498db" if d > 0 else "#e74c3c" for d in s2["diff"]]
    ax2.barh(range(len(s2)), s2["diff"], color=colors2,
             edgecolor="black", alpha=0.85)
    ax2.axvline(0,     color="black", linewidth=1.5)
    ax2.axvline( 0.05, color="gray",  linestyle="--", alpha=0.4)
    ax2.axvline(-0.05, color="gray",  linestyle="--", alpha=0.4)
    ax2.set_yticks(range(len(s2)))
    ax2.set_yticklabels(s2["genre"].str.upper(), fontsize=11)
    ax2.set_xlabel("Clip Mean − Context Mean\n(+ve = Clip dominant; −ve = Context dominant)",
                   fontsize=10)
    ax2.set_title("B. Clip vs Context Dominance by Genre\n(Sclip_Dcontext vs Dclip_Scontext)",
                  fontsize=13, fontweight="bold")
    for i, (_, row) in enumerate(s2.iterrows()):
        x_off = 0.003 if row["diff"] >= 0 else -0.003
        ha    = "left"  if row["diff"] >= 0 else "right"
        ax2.text(row["diff"] + x_off, i, row["sig_bonf"],
                 ha=ha, va="center", fontsize=10, fontweight="bold")
    fig.legend(
        handles=[Patch(facecolor="#3498db", label="Clip dominant"),
                 Patch(facecolor="#e74c3c", label="Context dominant")],
        loc="lower center", ncol=2, fontsize=10, bbox_to_anchor=(0.75, -0.06)
    )
    ax2.grid(axis="x", alpha=0.3)

    plt.suptitle(f"RQ3: Does Genre Moderate the Context Effect?  [{MODEL_SLUG} — individual]",
                 fontsize=14, fontweight="bold")
    plt.tight_layout()
    plt.savefig(f"{output_dir}/RQ3_genre_moderation_{MODEL_SLUG}.png",
                dpi=300, bbox_inches="tight")
    plt.show()
    print("Saved: RQ3 genre moderation plot")
```

---

## Summary

```{python summary, echo=FALSE}
print(f"SUMMARY OF FINDINGS  [{MODEL_SLUG} — individual level]")
print("=" * 70)

print(f"\nRQ1 — Context Effect (Dclip_Scontext vs Dclip_Dcontext_Dgenre):")
print(f"  Context-driven M={rq1_context['mean_ctx']:.4f}  |  "
      f"Baseline M={rq1_context['mean_base']:.4f}")
print(f"  Delta={rq1_context['delta']:+.4f}  "
      f"t({rq1_context['df']:.1f})={rq1_context['t']:.3f}  "
      f"p={rq1_context['p']:.4f}  {rq1_context['sig']}  "
      f"d={rq1_context['d']:.3f}")

print(f"\nRQ2a — Clip vs Context (Sclip_Dcontext vs Dclip_Scontext):")
print(f"  Clip M={rq2_primary['mean_clip']:.4f}  |  Ctx M={rq2_primary['mean_ctx']:.4f}")
dominant = "CLIP" if rq2_primary["diff"] > 0 else "CONTEXT"
print(f"  Delta={rq2_primary['diff']:+.4f}  {dominant} dominant  "
      f"d={rq2_primary['d']:.3f}  {rq2_primary['sig']}")

print(f"\nRQ2b — Combined Advantage (Sclip_Scontext vs single-factor conditions):")
for _, r in combined_df.iterrows():
    print(f"  {r['description']}")
    print(f"    Delta={r['delta']:+.4f}  d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")

if len(susceptibility_df) > 0:
    print(f"\nRQ3 — Genre Framing Susceptibility (ranked highest to lowest):")
    for _, r in susceptibility_df.iterrows():
        print(f"  {r['genre'].upper():14s}  Gain={r['framing_gain']:+.4f}  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")

if len(genre_mod_df) > 0:
    print(f"\nRQ3 — Within-Genre Clip vs Context Dominance:")
    for _, r in genre_mod_df.iterrows():
        print(f"  {r['genre'].upper():14s}  -> {r['dominant']:7s} dominant  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")
```

---

## Exploratory Analyses

> The analyses below do not map directly onto the three pre-specified research
> questions. They are retained as descriptive and methodological supplements that
> may be useful for characterising the data or for future exploratory work.

### Pairwise Context and Genre Comparisons

Tests whether specific context labels or genres differ from each other in how much
convergence they produce. Descriptive characterisation only.

```{python exploratory-pairwise, echo=FALSE}
print("PAIRWISE CONTEXT COMPARISONS  (Bonferroni corrected)")
print("-" * 70)

ctx_pairs = []
for c1, c2 in combinations(ctx_list, 2):
    g1 = sim_df.loc[
        (sim_df["condition"] == "Dclip_Scontext") &
        (sim_df["context_i"] == c1) & (sim_df["context_j"] == c1), "similarity"]
    g2 = sim_df.loc[
        (sim_df["condition"] == "Dclip_Scontext") &
        (sim_df["context_i"] == c2) & (sim_df["context_j"] == c2), "similarity"]
    if len(g1) > 1 and len(g2) > 1:
        t, p, df_val = welch_t(g1, g2)
        d = cohens_d(g1, g2)
        ctx_pairs.append(dict(context1=c1, context2=c2,
                               mean1=g1.mean(), mean2=g2.mean(),
                               diff=g1.mean()-g2.mean(),
                               t=t, df=df_val, p=p, d=d,
                               n1=len(g1), n2=len(g2)))

context_pairs_df = pd.DataFrame(ctx_pairs)
if len(context_pairs_df) > 0:
    context_pairs_df["p_bonf"]   = (context_pairs_df["p"] * len(context_pairs_df)).clip(upper=1.0)
    context_pairs_df["sig"]      = context_pairs_df["p"].apply(sig_marker)
    context_pairs_df["sig_bonf"] = context_pairs_df["p_bonf"].apply(sig_marker)
    context_pairs_df = context_pairs_df.sort_values("d", key=abs, ascending=False)
    print(context_pairs_df[["context1","context2","mean1","mean2","d",
                             "p","p_bonf","sig_bonf"]].to_string(index=False))
    context_pairs_df.to_csv(
        f"{output_dir}/context_pairwise_comparisons_{MODEL_SLUG}.csv", index=False)

print("\n\nPAIRWISE GENRE COMPARISONS  (Bonferroni corrected)")
print("-" * 70)

genre_pairs = []
for g1_lbl, g2_lbl in combinations(genre_list, 2):
    s1 = sim_df.loc[
        (sim_df["condition"] == "Dclip_Dcontext_Sgenre") &
        (sim_df["genre_i"] == g1_lbl) & (sim_df["genre_j"] == g1_lbl), "similarity"]
    s2 = sim_df.loc[
        (sim_df["condition"] == "Dclip_Dcontext_Sgenre") &
        (sim_df["genre_i"] == g2_lbl) & (sim_df["genre_j"] == g2_lbl), "similarity"]
    if len(s1) > 1 and len(s2) > 1:
        t, p, df_val = welch_t(s1, s2)
        d = cohens_d(s1, s2)
        genre_pairs.append(dict(genre1=g1_lbl, genre2=g2_lbl,
                                 mean1=s1.mean(), mean2=s2.mean(),
                                 diff=s1.mean()-s2.mean(),
                                 t=t, df=df_val, p=p, d=d,
                                 n1=len(s1), n2=len(s2)))

genre_pairs_df = pd.DataFrame(genre_pairs)
if len(genre_pairs_df) > 0:
    genre_pairs_df["p_bonf"]   = (genre_pairs_df["p"] * len(genre_pairs_df)).clip(upper=1.0)
    genre_pairs_df["sig"]      = genre_pairs_df["p"].apply(sig_marker)
    genre_pairs_df["sig_bonf"] = genre_pairs_df["p_bonf"].apply(sig_marker)
    genre_pairs_df = genre_pairs_df.sort_values("d", key=abs, ascending=False)
    print(genre_pairs_df[["genre1","genre2","mean1","mean2","d",
                           "p","p_bonf","sig_bonf"]].to_string(index=False))
    genre_pairs_df.to_csv(
        f"{output_dir}/genre_pairwise_comparisons_{MODEL_SLUG}.csv", index=False)
```

### Similarity Matrices

Full within/between similarity for context and genre.

```{python exploratory-similarity-matrices, echo=FALSE}
ctx_within_exp = []
for ctx in ctx_list:
    sims = sim_df.loc[
        (sim_df["condition"] == "Dclip_Scontext") &
        (sim_df["context_i"] == ctx) & (sim_df["context_j"] == ctx), "similarity"]
    if len(sims) > 0:
        ctx_within_exp.append(dict(context=ctx, mean=sims.mean()))
context_within_df = pd.DataFrame(ctx_within_exp)

genre_within_exp = []
for genre in genre_list:
    sims = sim_df.loc[
        (sim_df["condition"] == "Dclip_Dcontext_Sgenre") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(sims) > 0:
        genre_within_exp.append(dict(genre=genre, mean=sims.mean()))
genre_within_df = pd.DataFrame(genre_within_exp)

fig, axes = plt.subplots(1, 2, figsize=(16, 7))
for ax, within_df, fkey, meta_col, panel in [
    (axes[0], context_within_df, "context", "context_word", "A. Context Similarity Matrix"),
    (axes[1], genre_within_df,   "genre",   "clip_genre",   "B. Genre Similarity Matrix"),
]:
    labels = sorted(df[meta_col].unique())
    n_lbl  = len(labels)
    mat    = np.full((n_lbl, n_lbl), np.nan)
    for i, l1 in enumerate(labels):
        for j, l2 in enumerate(labels):
            if i == j:
                val = within_df.loc[within_df[fkey] == l1, "mean"].values
                mat[i, j] = val[0] if len(val) > 0 else np.nan
            else:
                mask = (
                    ((sim_df[f"{fkey}_i"] == l1) & (sim_df[f"{fkey}_j"] == l2)) |
                    ((sim_df[f"{fkey}_i"] == l2) & (sim_df[f"{fkey}_j"] == l1))
                )
                sims = sim_df.loc[mask, "similarity"]
                mat[i, j] = sims.mean() if len(sims) > 0 else np.nan
    if not np.all(np.isnan(mat)):
        sns.heatmap(mat, annot=True, fmt=".3f", cmap="YlOrRd",
                    xticklabels=labels, yticklabels=labels,
                    cbar_kws={"label": "Mean Similarity"},
                    mask=np.isnan(mat),
                    linewidths=0.5, linecolor="gray", ax=ax)
    ax.set_title(f"{panel}\n(Diagonal = Within-{fkey.capitalize()})",
                 fontsize=13, fontweight="bold")

plt.suptitle(f"Similarity Matrices: Context and Genre  [{MODEL_SLUG} — individual]",
             fontsize=15, fontweight="bold")
plt.tight_layout()
plt.savefig(f"{output_dir}/similarity_matrices_{MODEL_SLUG}.png",
            dpi=300, bbox_inches="tight")
plt.show()
```

### Individual-Level t-SNE

t-SNE of the sentence embedding space coloured by genre and context. At the
individual level this also reveals whether within-cell responses (same participant
condition) cluster together.

```{python exploratory-tsne, echo=FALSE}
n_svd = min(50, embeddings.shape[1] - 1)
svd   = TruncatedSVD(n_components=n_svd, random_state=42)
X_svd = svd.fit_transform(embeddings)
print(f"SVD explained variance: {svd.explained_variance_ratio_.sum():.3f}  "
      f"({n_svd} components)")

try:
    perp = min(30, len(df) // 4)   # perplexity must be < N/4 for small datasets
    tsne = TSNE(n_components=2, perplexity=perp, max_iter=1000,
                random_state=42, init="pca", learning_rate="auto")
except TypeError:
    tsne = TSNE(n_components=2, perplexity=perp, n_iter=1000,
                random_state=42, init="pca", learning_rate="auto")

X_2d = tsne.fit_transform(X_svd)

tsne_df = df[["clip_name", "context_word", "clip_genre"]].copy().reset_index(drop=True)
tsne_df["TSNE1"] = X_2d[:, 0]
tsne_df["TSNE2"] = X_2d[:, 1]
tsne_df.to_csv(f"{output_dir}/tsne_coords_{MODEL_SLUG}.csv", index=False)

fig, ax = plt.subplots(figsize=(10, 8))
sns.scatterplot(data=tsne_df, x="TSNE1", y="TSNE2",
                hue="clip_genre", style="context_word",
                palette="tab10", s=60, alpha=0.7, ax=ax)
ax.set_title(f"t-SNE: Individual MIMC Embeddings  [{MODEL_SLUG}]",
             fontsize=13, fontweight="bold")
ax.legend(bbox_to_anchor=(1.05, 1), loc="upper left", borderaxespad=0.)
plt.tight_layout()
plt.savefig(f"{output_dir}/tsne_{MODEL_SLUG}.png", dpi=300, bbox_inches="tight")
plt.show()
print("Saved: individual t-SNE plot")
```

```{r env}
install.packages("renv")
renv::init()
renv::snapshot()
```