---
title: "Framed Listening: TF-IDF Analyses"
author: "Hazel A. van der Walle (PhD student, Music, Durham University)"
date: "11 May 2026"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    theme: cosmo
---

All datasets generated and used for this study are openly available on GitHub:
<https://github.com/HazelvdW/context-framed-listening>.

This document analyses lexical semantic similarity between music-influenced mental
content (MIMC) descriptions at the aggregated document level using TF-IDF cosine
similarity. Analyses are organised around three research questions:

1. **RQ1 — Context effect**: Do contextual framing cues shape MIMC similarity?
2. **RQ2 — Genre moderation**: Does genre moderate the context effect?
3. **RQ3 — Music vs context**: Does music or framing drive greater MIMC convergence?

> **Note on method**: TF-IDF is a bag-of-words method optimised for document-level
> analysis. Individual short MIMC texts (~10–50 words) produce extremely sparse
> vectors with minimal lexical overlap; similarity values at that scale would not
> reflect semantic relationships. This analysis therefore works exclusively with
> aggregated combMIMC documents (one per clip × context cell, N = 64). Individual-
> level analysis is handled by MiniLM.
>
> The `SC_SX` (same clip, same context) condition is unavailable at the TF-IDF
> level — each cell is one document and cannot be self-paired. RQ3b (combined
> alignment advantage) is therefore deferred to the MiniLM pipeline.
>
> This document-level lexical analysis complements the MiniLM semantic similarity
> pipeline; condition categories are identical across both methods to enable direct
> cross-method comparison.

---

## Setup

```{r setup-r, echo=FALSE}
library(reticulate)

# Install Python packages on first run:
 reticulate::py_install(c(
   "pandas", "numpy", "scikit-learn", "scipy",
   "matplotlib", "seaborn", "wordcloud"
 ), pip = TRUE)
```

```{python setup-python, echo=FALSE}
import os
import numpy as np
import pandas as pd
import matplotlib.pyplot as plt
import matplotlib.colors as mcolors
import seaborn as sns
from itertools import combinations
from matplotlib.patches import Patch

from sklearn.feature_extraction.text  import TfidfVectorizer
from sklearn.metrics.pairwise         import cosine_similarity
from sklearn.decomposition            import TruncatedSVD
from sklearn.manifold                 import TSNE
from scipy                            import stats
from scipy.stats                      import levene, kruskal, mannwhitneyu
from wordcloud                        import WordCloud

# ── Paths ─────────────────────────────────────────────────────────────────────
base_path  = (
    "/Users/hazelaileenvanderwalle/Library/CloudStorage/"
    "OneDrive-Personal/work/study/PhD/_PROJECT/"
    "_framedListening_NLP/context-framed-listening"
)
output_dir = f"{base_path}/NLP_outputs/TFIDF"
os.makedirs(output_dir, exist_ok=True)
print(f"Output directory: {output_dir}")
```

```{python version-check, echo=FALSE}
# ── Environment version check ─────────────────────────────────────────────────
import importlib, sys
from packaging.version import Version

REQUIREMENTS = {
    "numpy":      "1.26",
    "pandas":     "2.1",
    "scipy":      "1.11",
    "sklearn":    "1.3",   # previously scikit-learn
    "matplotlib": "3.8",
    "seaborn":    "0.13",
    "wordcloud":  "1.9",
}

print(f"Python {sys.version}")
print("-" * 52)
all_ok = True
for pkg, min_ver in REQUIREMENTS.items():
    try:
        mod = importlib.import_module(pkg)
        ver = getattr(mod, "__version__", "unknown")
        ok  = Version(ver) >= Version(min_ver) if ver != "unknown" else True
        status = "OK" if ok else f"WARNING — expected >={min_ver}"
        if not ok:
            all_ok = False
        print(f"  {pkg:<22} {ver:<12} {status}")
    except ImportError:
        print(f"  {pkg:<22} NOT INSTALLED  ERROR")
        all_ok = False
if all_ok:
    print("\nAll package versions OK.")
else:
    print("\nOne or more issues — run: pip install -r requirements.txt")
```

---

## Helper Functions

```{python helpers}
def sig_marker(p):
    """Return significance marker string for a p-value."""
    if p < 0.001: return "***"
    if p < 0.01:  return "**"
    if p < 0.05:  return "*"
    return "n.s."


def welch_t(g1, g2):
    """Welch's t-test returning (t, p, df, mean_diff, ci_low, ci_high)."""
    n1, n2   = len(g1), len(g2)
    v1, v2   = g1.var(ddof=1), g2.var(ddof=1)
    se       = np.sqrt(v1/n1 + v2/n2)
    t        = (g1.mean() - g2.mean()) / se
    df       = (v1/n1 + v2/n2)**2 / ((v1/n1)**2/(n1-1) + (v2/n2)**2/(n2-1))
    p        = 2 * (1 - stats.t.cdf(abs(t), df))
    mean_diff = float(g1.mean() - g2.mean())
    ci_low    = mean_diff - 1.96 * se
    ci_high   = mean_diff + 1.96 * se
    return float(t), float(p), float(df), mean_diff, ci_low, ci_high


def cohens_d(g1, g2):
    """Compute Cohen's d effect size."""
    pooled = np.sqrt((g1.std()**2 + g2.std()**2) / 2)
    return float((g1.mean() - g2.mean()) / pooled) if pooled > 0 else np.nan
```

---

## Data Preparation

### Load Data

Load **`combMIMC_lvl2a/b.csv`** — Level 2 preprocessed text data of participants'
MIMC descriptions aggregated into combMIMC documents, generated using
`NLP-text-prep.qmd`.

```{python load-data, echo=TRUE}
data_path = f"{base_path}/NLP_outputs/combMIMC_lvl2b.csv" 
df        = pd.read_csv(data_path)                        
# lvl2a = aggressive preprocessing with "thought" stop words removed   
# lvl2b retains "thought" words

print(f"Shape:   {df.shape}")
print(f"Columns: {df.columns.tolist()}")
print(f"\nUnique clips:    {sorted(df['clip_name'].unique())}")
print(f"Unique contexts: {sorted(df['context_word'].unique())}")
print(f"Unique genres:   {sorted(df['genre_code'].unique())}")
print(f"\nTotal combMIMC documents: {len(df)}")
df.head(4)
```

### TF-IDF Vectorisation

```{python tfidf-vectorise, echo=FALSE}
vectorizer = TfidfVectorizer(
    min_df       = 1,
    max_df       = 1.0,
    sublinear_tf = True    # log-normalise term frequencies
)

tfidf_matrix  = vectorizer.fit_transform(df["textMIMC_lvl2b"])
feature_names = vectorizer.get_feature_names_out()
ignore_token  = "endofinput"

print(f"TF-IDF matrix shape: {tfidf_matrix.shape}")
print(f"  -> {tfidf_matrix.shape[0]} documents x {tfidf_matrix.shape[1]} terms")
print(f"Matrix density: "
      f"{tfidf_matrix.nnz / (tfidf_matrix.shape[0] * tfidf_matrix.shape[1]):.4f}")

# Dense scores DataFrame (documents x terms)
tfidf_scores_df = pd.DataFrame(
    tfidf_matrix.toarray(),
    columns = feature_names,
    index   = df.index
)
tfidf_scores_df.to_csv(f"{output_dir}/TFIDF_scores.csv", index=False)

# Top terms by mean TF-IDF
term_means = tfidf_scores_df.mean(axis=0).sort_values(ascending=False)
term_means = term_means[term_means.index.str.lower() != ignore_token]

print("\nTop 20 terms by mean TF-IDF:")
print(term_means.head(20).to_string())
```

### Cosine Similarity Matrix

```{python cosine-matrix, echo=FALSE}
cosine_matrix = cosine_similarity(tfidf_matrix)

iu = np.triu_indices_from(cosine_matrix, k=1)
print(f"Cosine similarity matrix shape: {cosine_matrix.shape}")
print(f"Value range:  [{cosine_matrix.min():.4f}, {cosine_matrix.max():.4f}]")
print(f"Mean off-diagonal similarity: {cosine_matrix[iu].mean():.4f}")
```

### Extract Similarity Values by Condition

The pairwise matrix is unpacked into a tidy long-format DataFrame. Each row is a
unique document pair annotated with condition labels.

| Condition | Description |
|---|---|
| `SC_SX` | Same clip **and** same context — combined alignment |
| `SC_dx` | Same clip, different context — isolates **clip** influence |
| `dc_SX_SG` | Different clip, same context, **same genre** — joint context + genre alignment |
| `dc_dx_SG` | Both different, same genre |
| `dc_SX_dg` | Different clip, same context, **different genre** — isolates pure **context** influence |
| `dc_dx_dg` | Entirely different — dissimilarity baseline |

```{python extract-similarity, echo=FALSE}

clips    = df["clip_name"].values
contexts = df["context_word"].values
genres   = df["genre_code"].values
n        = len(df)

records = {k: [] for k in [
    "item_i", "item_j", "similarity",
    "same_clip", "same_context", "same_genre", "condition",
    "clip_i", "clip_j", "context_i", "context_j", "genre_i", "genre_j"
]}

for i in range(n):
    for j in range(i + 1, n):
        sc = clips[i]    == clips[j]
        sx = contexts[i] == contexts[j]
        sg = genres[i]   == genres[j]

        if sc and sx:
            cond = "SC_SX"
        elif sc and not sx:
            cond = "SC_dx"
        elif not sc and sx and not sg:
            cond = "dc_SX_dg"          # pure context isolation: diff clip, same context, diff genre
        elif not sc and sx and sg:
            cond = "dc_SX_SG"          # joint context+genre alignment: diff clip, same context, same genre
        else:
            cond = ("dc_dx_SG"
                    if sg else "dc_dx_dg")

        records["item_i"].append(i)
        records["item_j"].append(j)
        records["similarity"].append(float(cosine_matrix[i, j]))
        records["same_clip"].append(sc)
        records["same_context"].append(sx)
        records["same_genre"].append(sg)
        records["condition"].append(cond)
        records["context_i"].append(contexts[i])
        records["context_j"].append(contexts[j])
        records["genre_i"].append(genres[i])
        records["genre_j"].append(genres[j])
        records["clip_i"].append(clips[i])
        records["clip_j"].append(clips[j])

sim_df = pd.DataFrame(records)

print(f"Total unique pairs: {len(sim_df)}")
print("\nCondition distribution:")
print(sim_df["condition"].value_counts().sort_index().to_string())

sim_df.to_csv(
  f"{output_dir}/TFIDF_similarity_by_condition.csv", index=False)

genre_list = sorted(df["genre_code"].unique())
ctx_list   = sorted(df["context_word"].unique())
print("\nSaved similarity data")
```

---
---

## Linear Mixed Models

Linear mixed models (LMMs) provide a complementary, model-based approach to the
pairwise t-tests above. The outcome is pairwise cosine similarity; fixed effects
are `context_comb` (the context labels from the pair) and `genre_comb` (the 
genres of items in the pair); `item_i` and `item_j` are included as a random 
intercept to account for the fact that each individual response appears in 
multiple pairs.

Three models are fitted in sequence. Model 1 tests main effects of context, genre, and clip — clip is included as both a fixed and random effect to separate clip-specific idiosyncrasies from the genre signal, since genre is fully nested within clip. Model 2 adds mean believability (from the supplementary study) as a covariate at the clip × context cell level (64 unique values, one per clip–context pairing) — this gives genuine within-context variation in believability and avoids the collinearity that would arise from collapsing to context-level means. Model 3 tests the context × genre interaction while retaining clip as a covariate. Model comparisons use likelihood ratio tests (ANOVA on nested models) to determine whether each additional term improves fit.

Following the LMMs, estimated marginal means (emmeans) unpack pairwise context
differences while controlling for genre. Finally, a Random Forest classifier and
a Linear Discriminant Analysis (LDA) are used to assess how well context condition
can be recovered from similarity scores alone.

### LMM setup & prep

```{r lmm-setup}

# ── Packages ──────────────────────────────────────────────────────────────────
required <- c("lme4", "lmerTest", "MuMIn", "emmeans", "ggdist",
              "randomForest", "MASS", "dplyr", "ggplot2",
              "car", "cowplot", "patchwork")
for (pkg in required) {
  if (!requireNamespace(pkg, quietly = TRUE))
    install.packages(pkg, repos = "https://cloud.r-project.org")
  library(pkg, character.only = TRUE)
}

# Normalise emmeans CI column names — at large N emmeans uses asymp.LCL/UCL
# instead of lower.CL/upper.CL; this ensures ggplot code works consistently
fix_emm_ci <- function(df) {
  names(df)[names(df) == "asymp.LCL"] <- "lower.CL"
  names(df)[names(df) == "asymp.UCL"] <- "upper.CL"
  df
}

# ── Paths ─────────────────────────────────────────────────────────────────────
base_path  <- paste0(
  "/Users/hazelaileenvanderwalle/Library/CloudStorage/",
  "OneDrive-Personal/work/study/PhD/_PROJECT/",
  "_framedListening_NLP/context-framed-listening"
)
output_dir <- file.path(base_path, "NLP_outputs", "TFIDF")

sim_df_path <- file.path(output_dir, "TFIDF_similarity_by_condition.csv")
sim_df      <- read.csv(sim_df_path, stringsAsFactors = FALSE)

cat("Loaded similarity data:", nrow(sim_df), "pairs\n")
cat("Columns:", paste(names(sim_df), collapse = ", "), "\n")
```

```{r lmm-prep}

# Using sum-to-zero (effects) coding so no reference level is used —
# each coefficient represents deviation from the grand mean,
# anova() gives Type III tests for each level independently
options(contrasts = c("contr.sum", "contr.poly"))

# Define similarity pair combination variables
sim_df$genre_comb   <- paste0(sim_df$genre_i,  "_",sim_df$genre_j)
sim_df$context_comb <- paste0(sim_df$context_i,"_",sim_df$context_j)
sim_df$clip_comb    <- paste0(sim_df$clip_i,   "_",sim_df$clip_j)

cat("genre_comb levels:\n");     print(table(sim_df$genre_comb))
cat("\ncontext_comb levels:\n"); print(table(sim_df$context_comb))
# clip_comb levels levels not pasted as it's quite long

# Factor predictors — comb variables as factors for the LMMs
sim_df$genre_comb   <- factor(sim_df$genre_comb)
sim_df$context_comb <- factor(sim_df$context_comb)
sim_df$clip_comb    <- factor(sim_df$clip_comb)
sim_df$item_i       <- factor(sim_df$item_i)
sim_df$item_j       <- factor(sim_df$item_j)
# Note: combMIMC has no PROLIFIC_PID — item_i/item_j (document indices) used as
# random intercepts instead. Each document appears in multiple pairs.

cat("\ncontext_comb levels:", nlevels(sim_df$context_comb), "\n")
cat("\ngenre_comb levels:  ", nlevels(sim_df$genre_comb),   "\n")
cat("\nclip_comb levels:   ", nlevels(sim_df$clip_comb),    "\n")

# ── Believability covariate ───────────────────────────────────────────────────
supp_path <- file.path(base_path, "dataSUPPstudy.csv")
supp      <- read.csv(supp_path, stringsAsFactors = FALSE)

believe_cell <- supp |>
  group_by(clip_name, context_word) |>
  summarise(believability = mean(rating_likelihood.response, na.rm = TRUE),
            .groups = "drop")

believe_cell$clip_merge <- tolower(sapply(
  strsplit(sub("\\.mp3$", "", believe_cell$clip_name), "_"),
  function(x) {
    prefix <- switch(tolower(x[1]),
      "electronic" = "ele", "jazz" = "jaz", "metal" = "met", tolower(x[1]))
    paste(c(prefix, x[2], x[3]), collapse = "_")
  }
))
believe_cell$cntx_merge <- trimws(tolower(believe_cell$context_word))

# Merge believability for item i
sim_df$clip_i_merge <- trimws(tolower(as.character(sim_df$clip_i)))
sim_df$cntx_i_merge  <- trimws(tolower(as.character(sim_df$context_i)))

sim_df <- merge(sim_df, believe_cell[, c("clip_merge", "cntx_merge", "believability")],
                by.x = c("clip_i_merge", "cntx_i_merge"),
                by.y = c("clip_merge",   "cntx_merge"),
                all.x = TRUE)
names(sim_df)[names(sim_df) == "believability"] <- "believability_i"

# Merge believability for item j
sim_df$clip_j_merge <- trimws(tolower(as.character(sim_df$clip_j)))
sim_df$cntx_j_merge  <- trimws(tolower(as.character(sim_df$context_j)))

sim_df <- merge(sim_df, 
                believe_cell[, c("clip_merge", "cntx_merge", "believability")],
                by.x = c("clip_j_merge", "cntx_j_merge"),
                by.y = c("clip_merge",   "cntx_merge"),
                all.x = TRUE)
names(sim_df)[names(sim_df) == "believability"] <- "believability_j"

# Pair-level believability = mean of both items' cell ratings
sim_df$believability_pair <- rowMeans(
  sim_df[, c("believability_i", "believability_j")], na.rm = FALSE)

cat("\nRows with full pair believability:", sum(!is.na(sim_df$believability_pair)),
    "of", nrow(sim_df), "\n")
cat("Rows with NA (unmatched):", sum(is.na(sim_df$believability_pair)), "\n")
```

### LMM Models

```{r lmm-model-checks}
#| eval: true
#| echo: false

S <- summarise(group_by(sim_df,context_comb,genre_comb),
               M=mean(similarity,na.rm=TRUE),
               SD=sd(similarity,na.rm=TRUE))
S
SC <- summarise(group_by(sim_df,context_comb),
                M=mean(similarity,na.rm=TRUE),
                SD=sd(similarity,na.rm=TRUE))
SC
SG <- summarise(group_by(sim_df,genre_comb),
                M=mean(similarity,na.rm=TRUE),
                SD=sd(similarity,na.rm=TRUE))
SG
```

#### Model 1: context + genre main effects

```{r lmm-model1}
#| eval: true
#| echo: true

cat("———MODEL 1: similarity ~ context_comb + genre_comb 
                 + (1 | clip_comb) + (1 | item_i) + (1 | item_j)———\n")

model1 <- lmer(similarity ~ context_comb + genre_comb 
               + (1 | clip_comb) + (1 | item_i) + (1 | item_j),
               data = sim_df, REML = FALSE)

print(anova(model1))
cat("\n———Omnibus fixed effects — no reference level———\n")
print(car::Anova(model1, type = 3))
cat("\n———Pseudo-R² (Nakagawa & Schielzeth), variance explained:———\n")
print(MuMIn::r.squaredGLMM(model1))

cat("\n———EMMean, context combos with 95% CI———\n")
emm1_ctx <- emmeans(model1, ~ context_comb)
print(summary(emm1_ctx, infer = c(TRUE, FALSE), level = 0.95))

cat("\n———EMMean, genre combos with 95% CI———\n")
emm1_gen <- emmeans(model1, ~ genre_comb)
print(summary(emm1_gen, infer = c(TRUE, FALSE), level = 0.95))

cat("\n———random effects variance check———\n")
print(summary(model1)$varcor)

# ── Context emmeans pointrange plot ───────────────────────────────────────────
emm1_ctx_df <- fix_emm_ci(as.data.frame(
  summary(emm1_ctx, infer = c(TRUE, FALSE), level = 0.95)))

p_emm1_ctx <- ggplot(emm1_ctx_df,
                      aes(x = reorder(context_comb, emmean), y = emmean)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.7, linewidth = 1, colour = "#2c7bb6") +
  geom_hline(yintercept = mean(emm1_ctx_df$emmean),
             linetype = "dashed", colour = "grey50", linewidth = 0.5) +
  coord_flip() +
  labs(title    = "Model 1: Estimated Marginal Means — Context Combination",
       subtitle = "Points = emmean; bars = 95% CI; dashed = grand mean",
       x = NULL, y = "Cosine similarity (emmean)") +
  scale_y_continuous(limits = c(0.10, 0.22)) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"))

# ── Genre emmeans pointrange plot ─────────────────────────────────────────────
emm1_gen_df <- fix_emm_ci(as.data.frame(
  summary(emm1_gen, infer = c(TRUE, FALSE), level = 0.95)))

p_emm1_gen <- ggplot(emm1_gen_df,
                      aes(x = reorder(genre_comb, emmean), y = emmean)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.7, linewidth = 1, colour = "#d7191c") +
  geom_hline(yintercept = mean(emm1_gen_df$emmean),
             linetype = "dashed", colour = "grey50", linewidth = 0.5) +
  coord_flip() +
  labs(title    = "Model 1: Estimated Marginal Means — Genre Combination",
       subtitle = "Points = emmean; bars = 95% CI; dashed = grand mean",
       x = NULL, y = "Cosine similarity (emmean)") +
  scale_y_continuous(limits = c(0.10, 0.22)) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"))

p_stacked <- cowplot::plot_grid(p_emm1_ctx, p_emm1_gen, ncol = 1)
print(p_stacked)
ggsave(file.path(output_dir, "TFIDF_emmeans_model1_stacked.png"),
       p_stacked, width = 10, height = 14, dpi = 300)

# ── Pairwise context contrasts forest plot ────────────────────────────────────
cat("\n———Pairwise context contrasts (Tukey), with 95% CI———\n")
emm1_ctx_pairs <- pairs(emm1_ctx, adjust = "tukey")
print(summary(emm1_ctx_pairs, infer = c(TRUE, TRUE), level = 0.95))

emm1_pairs_df <- fix_emm_ci(as.data.frame(
  summary(emm1_ctx_pairs, infer = c(TRUE, TRUE), level = 0.95)))

# Filtered: same-context vs same-context only
is_same_ctx <- function(label) {
  parts <- strsplit(label, " - ")[[1]]
  all(sapply(parts, function(p) {
    tokens <- strsplit(p, "_")[[1]]
    length(tokens) == 2 && tokens[1] == tokens[2]
  }))
}
emm1_pairs_key <- emm1_pairs_df[
  sapply(as.character(emm1_pairs_df$contrast), is_same_ctx), ]
clean_label <- function(label) {
  parts <- strsplit(label, " - ")[[1]]
  ctxs  <- sapply(parts, function(p) strsplit(p, "_")[[1]][1])
  paste0(tools::toTitleCase(ctxs[1]), " vs ", tools::toTitleCase(ctxs[2]))
}
emm1_pairs_key$label <- sapply(as.character(emm1_pairs_key$contrast), clean_label)

p_contrasts_key <- ggplot(emm1_pairs_key,
                            aes(x = reorder(label, estimate), y = estimate)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.8, linewidth = 1.1,
                  colour = ifelse(emm1_pairs_key$p.value < 0.05,
                                  "#2c7bb6", "grey60")) +
  geom_hline(yintercept = 0, linetype = "dashed",
             colour = "grey30", linewidth = 0.6) +
  coord_flip() +
  labs(title    = "Model 1: Same-Context Pairwise Contrasts",
       subtitle = "Blue = significant (Tukey); bars = 95% CI",
       x = NULL, y = "Estimated difference in cosine similarity") +
  theme_minimal(base_size = 12) +
  theme(plot.title  = element_text(face = "bold"),
        axis.text.y = element_text(size = 11))

print(p_contrasts_key)
ggsave(file.path(output_dir, "TFIDF_emmeans_model1_contrasts.png"),
       p_contrasts_key, width = 8, height = 5, dpi = 300)
```

#### Model 2: context × genre interaction

```{r lmm-model2}
#| eval: true
#| echo: true

cat("\n———MODEL 2: context_comb × genre_comb interaction———\n")
# At N=2016 pairs this is tractable without downsampling

model2 <- lmer(similarity ~ context_comb * genre_comb 
               + (1 | clip_comb) + (1 | item_i) + (1 | item_j),
               data = sim_df, REML = FALSE)

print(anova(model2))
cat("\n———Omnibus fixed effects — no reference level———\n")
print(car::Anova(model2, type = 3))
cat("\n———Pseudo-R²:———\n")
print(MuMIn::r.squaredGLMM(model2))

cat("\n———EMMean, context combos with 95% CI———\n")
emm2_ctx <- emmeans(model2, ~ context_comb)
print(summary(emm2_ctx, infer = c(TRUE, FALSE), level = 0.95))

cat("\n———EMMean, genre combos with 95% CI———\n")
emm2_gen <- emmeans(model2, ~ genre_comb)
print(summary(emm2_gen, infer = c(TRUE, FALSE), level = 0.95))

cat("\n———EMMean, context × genre cell means with 95% CI———\n")
emm2_int <- emmeans(model2, ~ context_comb | genre_comb)
print(summary(emm2_int, infer = c(TRUE, FALSE), level = 0.95))

cat("\n———random effects variance check———\n")
print(summary(model2)$varcor)

# ── Faceted interaction plot ───────────────────────────────────────────────────
emm2_int_df <- fix_emm_ci(as.data.frame(
  summary(emm2_int, infer = c(TRUE, FALSE), level = 0.95)))

emm2_int_df$genre_i   <- sub("_.*", "", emm2_int_df$genre_comb)
emm2_int_df$genre_j   <- sub(".*_", "", emm2_int_df$genre_comb)
emm2_int_df$pair_type <- ifelse(
  emm2_int_df$genre_i == emm2_int_df$genre_j, "Same genre", "Cross genre")

genre_colours <- c("80s" = "#fc8a1e", "Electronic" = "#7dcea0",
                   "Jazz" = "#8552b6", "Metal" = "#9e1100")

p_emm2_int <- ggplot(emm2_int_df,
                      aes(x = context_comb, y = emmean,
                          colour = genre_j, group = genre_comb,
                          alpha  = pair_type, linewidth = pair_type)) +
  geom_line() +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  size = 0.45, linewidth = 0.5,
                  position = position_dodge(width = 0.25)) +
  scale_colour_manual(values = genre_colours, name = "Genre (item j)") +
  scale_alpha_manual(values = c("Same genre" = 1, "Cross genre" = 0.35),
                     guide = "none") +
  scale_linewidth_manual(values = c("Same genre" = 1.2, "Cross genre" = 0.5),
                         guide = "none") +
  facet_wrap(~ genre_i, ncol = 2,
             labeller = labeller(genre_i = c(
               "80s" = "Genre i: 80s", "Electronic" = "Genre i: Electronic",
               "Jazz" = "Genre i: Jazz", "Metal" = "Genre i: Metal"))) +
  labs(title    = "Model 2: Context × Genre Estimated Marginal Means",
       subtitle = "Faceted by genre_i; coloured by genre_j; thick lines = same-genre pairs",
       x = "Context combination", y = "Cosine similarity (emmean)") +
  theme_minimal(base_size = 10) +
  theme(plot.title    = element_text(face = "bold"),
        axis.text.x   = element_text(angle = 35, hjust = 1, size = 8),
        strip.text    = element_text(face = "bold", size = 10),
        legend.position = "right",
        panel.spacing = unit(1.2, "lines"))

print(p_emm2_int)
ggsave(file.path(output_dir, "TFIDF_emmeans_model2_interaction_faceted.png"),
       p_emm2_int, width = 14, height = 10, dpi = 300)
```

```{r model-comparisons}
#| eval: true
#| echo: true

cat("\n———Model 1 vs Model 2 (genre interaction):———\n")
print(anova(model1, model2))
```

### Estimated Marginal Means

```{r emmeans}
#| eval: true
#| echo: true

cat("———ESTIMATED MARGINAL MEANS — Model 2 (interaction)———\n")
cat("(pairwise context contrasts, Tukey adjustment)\n\n")

emm2_ctx_pairs <- emmeans(model2, pairwise ~ context_comb, adjust = "tukey")
print(summary(emm2_ctx_pairs, infer = c(TRUE, TRUE), level = 0.95))

cat("\n———context × genre cell means (Model 2):———\n")
print(summary(emmeans(model2, ~ context_comb | genre_comb),
              infer = c(TRUE, FALSE), level = 0.95))
```

---
---

## RQ1 — Does Context Shape MIMC Similarity?

**Logic**: The clearest test of whether context cues do anything at all is to compare
`dc_SX_dg` (different music, same context label) against `dc_dx_dg`
(everything different — the dissimilarity floor). If context drives convergence,
pairs sharing a context label should be more similar than pairs sharing nothing.

An omnibus Kruskal–Wallis test across all five conditions is run first to establish
that condition membership explains variation before pairwise tests are interpreted.

### Omnibus Test

```{python omnibus-kruskal, echo=FALSE}
all_conditions = [
    "SC_SX",
    "SC_dx",
    "dc_SX_SG",
    "dc_SX_dg",
    "dc_dx_SG",
    "dc_dx_dg",
]

cond_groups = [sim_df.loc[sim_df["condition"] == c, "similarity"].values
               for c in all_conditions if (sim_df["condition"] == c).any()]
valid_conds = [c for c in all_conditions if (sim_df["condition"] == c).any()]

H, p_kw = kruskal(*cond_groups)
print("OMNIBUS KRUSKAL–WALLIS TEST ACROSS ALL CONDITIONS")
print("=" * 60)
print(f"  H({len(valid_conds)-1}) = {H:.3f},  p = {p_kw:.4e}  {sig_marker(p_kw)}")
print(f"  Conditions tested: {valid_conds}")

# Post-hoc: pairwise Mann–Whitney U with Bonferroni correction
print("\nPost-hoc pairwise Mann–Whitney U  (Bonferroni corrected)")
print("-" * 60)
posthoc_pairs   = list(combinations(range(len(valid_conds)), 2))
posthoc_results = []
for i, j in posthoc_pairs:
    g1, g2  = cond_groups[i], cond_groups[j]
    u, p_mw = mannwhitneyu(g1, g2, alternative="two-sided")
    d       = cohens_d(pd.Series(g1), pd.Series(g2))
    posthoc_results.append(dict(
        cond1=valid_conds[i], cond2=valid_conds[j],
        mean1=g1.mean(), mean2=g2.mean(),
        U=u, p=p_mw, d=d, n1=len(g1), n2=len(g2)
    ))

posthoc_df             = pd.DataFrame(posthoc_results)
posthoc_df["p_bonf"]   = (posthoc_df["p"] * len(posthoc_df)).clip(upper=1.0)
posthoc_df["sig_bonf"] = posthoc_df["p_bonf"].apply(sig_marker)
posthoc_df             = posthoc_df.sort_values("d", key=abs, ascending=False)

print(posthoc_df[["cond1","cond2","mean1","mean2","d","p","p_bonf","sig_bonf"]]
      .to_string(index=False))
posthoc_df.to_csv(f"{output_dir}/TFIDF_omnibus_posthoc.csv", index=False)
print(f"\nSaved omnibus post-hoc table")
```

### Context Effect: Pure isolation (`dc_SX_dg`) and joint alignment (`dc_SX_SG`)

The `dc_SX_dg` condition previously collapsed same-context pairs regardless
of whether the two items shared a genre. Splitting by genre gives two distinct tests:
`dc_SX_dg` (different clip, same context, **different** genre) isolates the pure
context effect with genre controlled out; `dc_SX_SG` (different clip, same context,
**same** genre) captures joint context + genre alignment.

```{python rq1-context-effect, echo=FALSE}
ctx_pure_sims = sim_df.loc[sim_df["condition"] == "dc_SX_dg",             "similarity"]
ctx_joint_sims= sim_df.loc[sim_df["condition"] == "dc_SX_SG",             "similarity"]
baseline_sims = sim_df.loc[sim_df["condition"] == "dc_dx_dg","similarity"]

# Pure context effect: dc_SX_dg vs baseline
t_pure, p_pure, df_pure, diff_pure, ci_diff_pure_lo, ci_diff_pure_hi = welch_t(ctx_pure_sims, baseline_sims)
d_pure                  = cohens_d(ctx_pure_sims, baseline_sims)

# Joint context+genre alignment: dc_SX_SG vs baseline
t_joint, p_joint, df_joint, diff_joint, ci_diff_joint_lo, ci_diff_joint_hi = welch_t(ctx_joint_sims, baseline_sims)
d_joint                    = cohens_d(ctx_joint_sims, baseline_sims)
diff_joint                 = ctx_joint_sims.mean() - baseline_sims.mean()
ci_diff_joint_lo           = diff_joint - 1.96*(ctx_joint_sims.std()/len(ctx_joint_sims)**0.5 +
                                                  baseline_sims.std()/len(baseline_sims)**0.5)
ci_diff_joint_hi           = diff_joint + 1.96*(ctx_joint_sims.std()/len(ctx_joint_sims)**0.5 +
                                                  baseline_sims.std()/len(baseline_sims)**0.5)

print("RQ1 — CONTEXT EFFECT (pure isolation: dc_SX_dg vs baseline)")
print("=" * 65)
print(f"  dc_SX_dg (diff clip, same ctx, diff genre)  M = {ctx_pure_sims.mean():.4f}  (N = {len(ctx_pure_sims)})")
print(f"  dc_dx_dg (baseline)            M = {baseline_sims.mean():.4f}  (N = {len(baseline_sims)})")
print(f"  Mean diff = {diff_pure:+.4f},  95% CI [{ci_diff_pure_lo:.4f}, {ci_diff_pure_hi:.4f}]")
print(f"  Welch's t({df_pure:.1f}) = {t_pure:.3f},  p = {p_pure:.4f}  {sig_marker(p_pure)}")
print(f"  Cohen's d = {d_pure:.3f}  [note: d benchmarks not appropriate for pairwise data]")

print("\nRQ1 — JOINT CONTEXT + GENRE ALIGNMENT (dc_SX_SG vs baseline)")
print("=" * 65)
print(f"  dc_SX_SG (diff clip, same ctx, same genre)  M = {ctx_joint_sims.mean():.4f}  (N = {len(ctx_joint_sims)})")
print(f"  dc_dx_dg (baseline)            M = {baseline_sims.mean():.4f}  (N = {len(baseline_sims)})")
print(f"  Mean diff = {diff_joint:+.4f},  95% CI [{ci_diff_joint_lo:.4f}, {ci_diff_joint_hi:.4f}]")
print(f"  Welch's t({df_joint:.1f}) = {t_joint:.3f},  p = {p_joint:.4f}  {sig_marker(p_joint)}")
print(f"  Cohen's d = {d_joint:.3f}  [note: d benchmarks not appropriate for pairwise data]")

rq1_context = dict(
    mean_pure=float(ctx_pure_sims.mean()),   mean_joint=float(ctx_joint_sims.mean()),
    mean_base=float(baseline_sims.mean()),
    diff_pure=diff_pure,                     diff_joint=diff_joint,
    ci_pure_lo=ci_diff_pure_lo,              ci_pure_hi=ci_diff_pure_hi,
    ci_joint_lo=ci_diff_joint_lo,            ci_joint_hi=ci_diff_joint_hi,
    t_pure=t_pure,   df_pure=df_pure,   p_pure=p_pure,
    t_joint=t_joint, df_joint=df_joint, p_joint=p_joint,
    sig=sig_marker(p_pure),
)
```

### Visualisation

```{python vis-rq1, echo=FALSE}
# Three-condition overview: baseline → context → clip
# Note: SC_SX is excluded — not available at TF-IDF level (see RQ2b)
rq1_conds = [
    ("dc_dx_dg",  "Baseline\n(All Diff)",             "#95a5a6"),
    ("dc_SX_dg",  "Same Context\n(Diff Clip+Genre)",  "#e74c3c"),
    ("dc_SX_SG",  "Same Context+Genre\n(Diff Clip)",  "#c0392b"),
    ("SC_dx", "Same Clip\n(Diff Context)",   "#3498db"),
]
present_rq1 = [(c, lbl, col) for c, lbl, col in rq1_conds
               if (sim_df["condition"] == c).any()]

fig, axes = plt.subplots(1, 2, figsize=(15, 6))

# Panel A: mean bars with 95% CI
ax = axes[0]
means_rq1, errs_rq1, lbls_rq1, cols_rq1 = [], [], [], []
for cond, lbl, col in present_rq1:
    g  = sim_df.loc[sim_df["condition"] == cond, "similarity"]
    ci = stats.t.interval(0.95, len(g)-1, loc=g.mean(), scale=stats.sem(g))
    means_rq1.append(g.mean())
    errs_rq1.append((ci[1]-ci[0])/2)
    lbls_rq1.append(lbl)
    cols_rq1.append(col)

ax.bar(range(len(means_rq1)), means_rq1, color=cols_rq1,
       edgecolor="black", alpha=0.85)
ax.errorbar(range(len(means_rq1)), means_rq1, yerr=errs_rq1,
            fmt="none", ecolor="black", capsize=6, linewidth=2)
ax.set_xticks(range(len(lbls_rq1)))
ax.set_xticklabels(lbls_rq1, fontsize=10)
ax.set_ylabel("Mean Cosine Similarity", fontsize=11)
ax.set_title("A. Mean Similarity by Condition\n(95% CI error bars)",
             fontsize=12, fontweight="bold")
ax.grid(axis="y", alpha=0.3)
# Annotate context-vs-baseline bracket
if len(means_rq1) >= 2:
    y_brack = max(means_rq1) + max(errs_rq1) + 0.02
    ax.plot([0, 1], [y_brack, y_brack], "k-", linewidth=1.5)
    ax.text(0.5, y_brack + 0.005, rq1_context["sig"],
            ha="center", fontsize=11, fontweight="bold")

# Panel B: violin of all four conditions
ax2 = axes[1]
plot_data = pd.concat([
    sim_df.loc[sim_df["condition"] == c, ["similarity"]].assign(label=lbl)
    for c, lbl, _ in present_rq1
])
order_v   = [lbl for _, lbl, _ in present_rq1]
palette_v = {lbl: col for _, lbl, col in present_rq1}
sns.violinplot(data=plot_data, x="label", y="similarity",
               order=order_v, hue="label", palette=palette_v,
               legend=False, inner="box", linewidth=1.5, ax=ax2)
ax2.set_xlabel("")
ax2.set_ylabel("Cosine Similarity", fontsize=11)
ax2.set_title("B. Similarity Distributions by Condition",
              fontsize=12, fontweight="bold")
ax2.grid(axis="y", alpha=0.3)

plt.suptitle("RQ1: Does Context Shape MIMC Similarity?",
             fontsize=14, fontweight="bold")
plt.tight_layout()
plt.savefig(f"{output_dir}/TFIDF_RQ1_context_effect.png",
            dpi=300, bbox_inches="tight")
plt.show()
```

---

## RQ2 — Does Genre Moderate the Context Effect?

**Logic**: Two complementary tests. *Framing susceptibility*: per genre, how much
does sharing a context label raise similarity above the dissimilarity floor?
*Within-genre clip vs context dominance*: within each genre, does clip or context
drive more convergence? Model 2 (context × genre interaction) is presented as the
model-based complement to these tests.

### Framing Susceptibility by Genre

```{python rq2-susceptibility, echo=FALSE}
print("RQ2 — GENRE FRAMING SUSCEPTIBILITY")
print("=" * 70)
print("Framing gain = dc_SX_SG M  −  dc_dx_SG M  (per genre)")
print("-" * 70)

susceptibility_rows = []
for genre in genre_list:
    ctx_sims_g = sim_df.loc[
        (sim_df["condition"] == "dc_SX_SG") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(ctx_sims_g) == 0:
        ctx_sims_g = sim_df.loc[
            (sim_df["condition"] == "dc_SX_SG") &
            ((sim_df["genre_i"] == genre) | (sim_df["genre_j"] == genre)), "similarity"]
    baseline_g = sim_df.loc[
        (sim_df["condition"] == "dc_dx_SG") &
        (sim_df["genre_i"] == genre), "similarity"]

    if len(ctx_sims_g) > 1 and len(baseline_g) > 1:
        framing_gain = ctx_sims_g.mean() - baseline_g.mean()
        t, p, df_val, mean_diff, ci_low, ci_high = welch_t(ctx_sims_g, baseline_g)
        d            = cohens_d(ctx_sims_g, baseline_g)
        susceptibility_rows.append(dict(
            genre=genre,
            context_driven_mean=ctx_sims_g.mean(),
            baseline_mean=baseline_g.mean(),
            framing_gain=framing_gain,
            mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
            t=t, df=df_val, p=p, d=d,
            n_ctx=len(ctx_sims_g), n_base=len(baseline_g)
        ))
        print(f"  {genre.upper():14s}  Ctx M={ctx_sims_g.mean():.4f}  "
              f"Base M={baseline_g.mean():.4f}  "
              f"Gain={framing_gain:+.4f}  95% CI [{ci_low:.4f}, {ci_high:.4f}]  "
              f"d={d:.3f}  p={p:.4f}")

susceptibility_df = pd.DataFrame(susceptibility_rows)
if len(susceptibility_df) > 0:
    n_sus = len(susceptibility_df)
    susceptibility_df["p_bonf"]   = (susceptibility_df["p"] * n_sus).clip(upper=1.0)
    susceptibility_df["sig"]      = susceptibility_df["p"].apply(sig_marker)
    susceptibility_df["sig_bonf"] = susceptibility_df["p_bonf"].apply(sig_marker)
    susceptibility_df = susceptibility_df.sort_values("framing_gain", ascending=False)
    print(f"\nGenres ranked by framing susceptibility (highest to lowest):")
    for _, r in susceptibility_df.iterrows():
        print(f"  {r['genre'].upper():14s}  Gain={r['framing_gain']:+.4f}  "
              f"95% CI [{r['ci_low']:.4f}, {r['ci_high']:.4f}]  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")
    susceptibility_df.to_csv(
        f"{output_dir}/TFIDF_genre_framing_susceptibility.csv", index=False)
    print(f"\nSaved genre framing susceptibility table")
```

### Within-Genre Clip vs Context Dominance

```{python rq2-genre-moderator, echo=FALSE}
print("RQ2 — WITHIN-GENRE CLIP vs CONTEXT DOMINANCE")
print("=" * 70)
print("Clip-driven:    SC_dx  (same clip, diff context, same genre)")
print("Context-driven: dc_SX_SG  (diff clip, same context, same genre)")
print("-" * 70)

mod_rows = []
for genre in genre_list:
    clip_sims_g = sim_df.loc[
        (sim_df["condition"] == "SC_dx") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    ctx_sims_g = sim_df.loc[
        (sim_df["condition"] == "dc_SX_SG") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(clip_sims_g) > 1 and len(ctx_sims_g) > 1:
        t, p, df_val, mean_diff, ci_low, ci_high = welch_t(clip_sims_g, ctx_sims_g)
        d            = cohens_d(clip_sims_g, ctx_sims_g)
        dominant     = "CLIP" if clip_sims_g.mean() > ctx_sims_g.mean() else "CONTEXT"
        mod_rows.append(dict(
            genre=genre,
            clip_mean=clip_sims_g.mean(), clip_sd=clip_sims_g.std(),
            context_mean=ctx_sims_g.mean(), context_sd=ctx_sims_g.std(),
            diff=clip_sims_g.mean()-ctx_sims_g.mean(),
            mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
            dominant=dominant,
            t=t, df=df_val, p=p, d=d,
            n_clip=len(clip_sims_g), n_context=len(ctx_sims_g)
        ))
        print(f"  {genre.upper():14s}  Clip M={clip_sims_g.mean():.4f}  "
              f"Ctx M={ctx_sims_g.mean():.4f}  "
              f"95% CI [{ci_low:.4f}, {ci_high:.4f}]  "
              f"-> {dominant:7s} dominant  d={d:.3f}  p={p:.4f}")

genre_mod_df = pd.DataFrame(mod_rows)
if len(genre_mod_df) > 0:
    n_mod = len(genre_mod_df)
    genre_mod_df["p_bonf"]   = (genre_mod_df["p"] * n_mod).clip(upper=1.0)
    genre_mod_df["sig"]      = genre_mod_df["p"].apply(sig_marker)
    genre_mod_df["sig_bonf"] = genre_mod_df["p_bonf"].apply(sig_marker)
    genre_mod_df.to_csv(
        f"{output_dir}/TFIDF_genre_clip_vs_context_moderator.csv", index=False)
    print(f"\nSaved within-genre clip vs context moderator table")
```

### Visualisation

```{python vis-rq2-genre, echo=FALSE}
if len(susceptibility_df) > 0 and len(genre_mod_df) > 0:
    fig, axes = plt.subplots(1, 2, figsize=(16, 6))

    # Panel A: framing gain
    ax = axes[0]
    s  = susceptibility_df.sort_values("framing_gain", ascending=True)
    colors = ["#e74c3c" if g > 0 else "#95a5a6" for g in s["framing_gain"]]
    ax.barh(range(len(s)), s["framing_gain"], color=colors,
            edgecolor="black", alpha=0.85)
    ax.axvline(0, color="black", linewidth=1.5)
    ax.set_yticks(range(len(s)))
    ax.set_yticklabels(s["genre"].str.upper(), fontsize=11)
    ax.set_xlabel("Framing Gain\n(dc_SX_SG − dc_dx_SG)", fontsize=10)
    ax.set_title("A. Genre Framing Susceptibility\n(Higher = More Context-Sensitive)",
                 fontsize=13, fontweight="bold")
    for i, (_, row) in enumerate(s.iterrows()):
        x_off = 0.002 if row["framing_gain"] >= 0 else -0.002
        ha    = "left"  if row["framing_gain"] >= 0 else "right"
        ax.text(row["framing_gain"] + x_off, i, row["sig_bonf"],
                ha=ha, va="center", fontsize=10, fontweight="bold")
    ax.grid(axis="x", alpha=0.3)

    # Panel B: within-genre clip vs context dominance
    ax2 = axes[1]
    s2  = genre_mod_df.sort_values("diff", ascending=True)
    colors2 = ["#3498db" if d > 0 else "#e74c3c" for d in s2["diff"]]
    ax2.barh(range(len(s2)), s2["diff"], color=colors2,
             edgecolor="black", alpha=0.85)
    ax2.axvline(0,     color="black", linewidth=1.5)
    ax2.axvline( 0.05, color="gray",  linestyle="--", alpha=0.4)
    ax2.axvline(-0.05, color="gray",  linestyle="--", alpha=0.4)
    ax2.set_yticks(range(len(s2)))
    ax2.set_yticklabels(s2["genre"].str.upper(), fontsize=11)
    ax2.set_xlabel("Clip Mean − Context Mean\n(+ve = Clip dominant; −ve = Context dominant)",
                   fontsize=10)
    ax2.set_title("B. Clip vs Context Dominance by Genre\n(SC_dx vs dc_SX_SG)",
                  fontsize=13, fontweight="bold")
    for i, (_, row) in enumerate(s2.iterrows()):
        x_off = 0.003 if row["diff"] >= 0 else -0.003
        ha    = "left"  if row["diff"] >= 0 else "right"
        ax2.text(row["diff"] + x_off, i, row["sig_bonf"],
                 ha=ha, va="center", fontsize=10, fontweight="bold")
    fig.legend(
        handles=[Patch(facecolor="#3498db", label="Clip dominant"),
                 Patch(facecolor="#e74c3c", label="Context dominant")],
        loc="lower center", ncol=2, fontsize=10, bbox_to_anchor=(0.75, -0.06)
    )
    ax2.grid(axis="x", alpha=0.3)

    plt.suptitle("RQ2: Does Genre Moderate the Context Effect?",
                 fontsize=14, fontweight="bold")
    plt.tight_layout()
    plt.savefig(f"{output_dir}/TFIDF_RQ2_genre_moderation.png",
                dpi=300, bbox_inches="tight")
    plt.show()
    print("Saved: RQ2 genre moderation plot")
```

---

### Supplementary Study — Does Believability Moderate the Context Effect?

```{r lmm-model3-believability}
#| eval: true
#| echo: true

cat("\n———MODEL 3: + believability_pair (supplementary covariate)———\n")

model3 <- lmer(similarity ~ context_comb + genre_comb + believability_pair 
               + (1 | clip_comb) + (1 | item_i) + (1 | item_j),
               data = sim_df, REML = FALSE)

print(anova(model3))
cat("\n———Omnibus fixed effects — no reference level———\n")
print(car::Anova(model3, type = 3))
cat("\n———Pseudo-R² (Nakagawa & Schielzeth), variance explained:———\n")
print(MuMIn::r.squaredGLMM(model3))
cat("\n———EMMean, context combos with 95% CI———\n")
print(summary(emmeans(model3, ~ context_comb), infer = c(TRUE, FALSE), level = 0.95))
cat("\n———EMMean, genre combos with 95% CI———\n")
print(summary(emmeans(model3, ~ genre_comb), infer = c(TRUE, FALSE), level = 0.95))
cat("\n———random effects variance check———\n")
print(summary(model3)$varcor)

cat("\n———Model comparison — Model 1 vs Model 3 (believability_pair):———\n")
print(anova(model1, model3))
```

---

## RQ3 — Does Music Clip or Context Drive Greater Convergence?

**Logic**: `SC_dx` (same clip, different contexts) isolates the music
contribution; `dc_SX_dg` (different clips, same context) isolates the context
contribution.

> **TF-IDF note — `SC_SX` unavailable**: each clip × context cell is a single
> aggregated document and cannot be self-paired, so `SC_SX` yields zero pairs.
> The combined-alignment hypothesis (RQ3b) is therefore a MiniLM-only analysis.

### Clip vs Context (RQ3a)

```{python rq3-clip-vs-context, echo=FALSE}
clip_sims = sim_df.loc[sim_df["condition"] == "SC_dx", "similarity"]
ctx_sims  = sim_df.loc[sim_df["condition"] == "dc_SX_dg", "similarity"]

if len(clip_sims) == 0 or len(ctx_sims) == 0:
    raise ValueError(f"Empty condition — available: {sim_df['condition'].unique().tolist()}")

t, p, df_val, mean_diff, ci_low, ci_high = welch_t(clip_sims, ctx_sims)
d = cohens_d(clip_sims, ctx_sims)

rq3_primary = dict(
    mean_clip=float(clip_sims.mean()), mean_ctx=float(ctx_sims.mean()),
    diff=float(clip_sims.mean()-ctx_sims.mean()),
    mean_diff=mean_diff, ci_low=ci_low, ci_high=ci_high,
    t=t, df=df_val, p=p, sig=sig_marker(p), d=d,
    n_clip=len(clip_sims), n_ctx=len(ctx_sims)
)

print("RQ3a — CLIP vs CONTEXT")
print("=" * 60)
print(f"  SC_dx (clip-driven):       M = {rq3_primary['mean_clip']:.4f}  "
      f"(N = {rq3_primary['n_clip']})")
print(f"  dc_SX_dg (context-driven): M = {rq3_primary['mean_ctx']:.4f}  "
      f"(N = {rq3_primary['n_ctx']})")
print(f"  Mean difference = {mean_diff:+.4f},  95% CI [{ci_low:.4f}, {ci_high:.4f}]")
print(f"  Welch's t({df_val:.1f}) = {t:.3f},  p = {p:.4f}  {sig_marker(p)}")
print(f"  Cohen's d = {d:.3f}  [note: d benchmarks not appropriate for pairwise data]")
dominant = "CLIP" if rq3_primary["diff"] > 0 else "CONTEXT"
print(f"\n-> {dominant} drives greater MIMC similarity at the document level")
```

### RQ3b — Combined Advantage: SC_SX vs Single-Factor Conditions

> **SKIPPED in TF-IDF — MiniLM only.**
> Each clip × context cell = one document; self-pairing is undefined.
> `SC_SX` yields N = 0. Deferred to the MiniLM pipeline.

```{python rq3b-combined, echo=FALSE}
combined_df = pd.DataFrame(columns=[
    "comparison", "description", "mean_a", "mean_b",
    "delta", "mean_diff", "ci_low", "ci_high",
    "t", "df", "p", "p_bonf", "sig", "sig_bonf", "d"
])
print("RQ3b — COMBINED ADVANTAGE  [SKIPPED — TF-IDF level]")
print("  SC_SX not available. Deferred to MiniLM pipeline.")
```

### Visualisation

```{python vis-rq3, echo=FALSE}
fig, axes = plt.subplots(1, 2, figsize=(15, 6))

# Panel A: clip vs context bar
ax = axes[0]
clip_ci = stats.t.interval(0.95, len(clip_sims)-1,
                            loc=clip_sims.mean(), scale=stats.sem(clip_sims))
ctx_ci  = stats.t.interval(0.95, len(ctx_sims)-1,
                            loc=ctx_sims.mean(), scale=stats.sem(ctx_sims))
groups    = ["Clip-Driven\n(Same Clip, Diff Ctx)", "Context-Driven\n(Diff Clip, Same Ctx)"]
means_rq3 = [clip_sims.mean(), ctx_sims.mean()]
errs_rq3  = [(clip_ci[1]-clip_ci[0])/2, (ctx_ci[1]-ctx_ci[0])/2]
cols_rq3  = ["#3498db", "#e74c3c"]

ax.bar(range(2), means_rq3, color=cols_rq3, edgecolor="black",
       linewidth=2, alpha=0.85, width=0.55)
ax.errorbar(range(2), means_rq3, yerr=errs_rq3, fmt="none",
            ecolor="black", capsize=8, capthick=2, linewidth=2)
ax.set_xticks(range(2))
ax.set_xticklabels(groups, fontsize=10)
ax.set_ylabel("Mean Cosine Similarity", fontsize=11)
ax.set_title("A. Clip vs Context (RQ3a)\n(95% CI error bars)",
             fontsize=12, fontweight="bold")
mid_y = (means_rq3[0] + means_rq3[1]) / 2 + 0.01
ax.annotate("", xy=(0, mid_y), xytext=(1, mid_y),
            arrowprops=dict(arrowstyle="<->", lw=2, color="black"))
effect_text = (f"d = {rq3_primary['d']:.3f}  {rq3_primary['sig']}\n"
               f"Δ = {rq3_primary['diff']:+.4f}")
ax.text(0.5, mid_y + 0.012, effect_text, ha="center", fontsize=10,
        fontweight="bold",
        bbox=dict(boxstyle="round,pad=0.4", facecolor="lightyellow",
                  edgecolor="black", alpha=0.9))
ax.set_ylim([0, max(means_rq3) * 1.35])
ax.grid(axis="y", alpha=0.3, linestyle="--")

# Panel B: placeholder for SC_SX
ax2 = axes[1]
ax2.text(0.5, 0.5,
         "Combined alignment\nadvantage (RQ3b)\n\nNot available at\nTF-IDF level\n\n"
         "→ See MiniLM pipeline",
         ha="center", va="center", fontsize=13, style="italic", color="#7f8c8d",
         transform=ax2.transAxes,
         bbox=dict(boxstyle="round,pad=0.8", facecolor="#f5f5f5",
                   edgecolor="#bdc3c7", linewidth=1.5))
ax2.set_title("B. Combined Advantage (RQ3b)\n[MiniLM-only — skipped here]",
              fontsize=12, fontweight="bold", color="#7f8c8d")
ax2.axis("off")

plt.suptitle("RQ3: Does Music or Context Drive Greater Convergence?",
             fontsize=14, fontweight="bold")
plt.tight_layout()
plt.savefig(f"{output_dir}/TFIDF_RQ3_clip_vs_context.png",
            dpi=300, bbox_inches="tight")
plt.show()
```

---

## Summary

```{python summary, echo=FALSE}
print("SUMMARY OF FINDINGS  [TF-IDF — combMIMC level]")
print("=" * 70)

print(f"\nRQ1 — Pure context effect (dc_SX_dg vs dc_dx_dg):")
print(f"  dc_SX_dg M={rq1_context['mean_pure']:.4f}  |  "
      f"Baseline M={rq1_context['mean_base']:.4f}")
print(f"  Mean diff={rq1_context['diff_pure']:+.4f}  "
      f"95% CI [{rq1_context['ci_pure_lo']:.4f}, {rq1_context['ci_pure_hi']:.4f}]  "
      f"t({rq1_context['df_pure']:.1f})={rq1_context['t_pure']:.3f}  "
      f"p={rq1_context['p_pure']:.4f}  {rq1_context['sig']}")

print(f"\nRQ1 — Joint context+genre alignment (dc_SX_SG vs dc_dx_dg):")
print(f"  dc_SX_SG M={rq1_context['mean_joint']:.4f}  |  "
      f"Baseline M={rq1_context['mean_base']:.4f}")
print(f"  Mean diff={rq1_context['diff_joint']:+.4f}  "
      f"95% CI [{rq1_context['ci_joint_lo']:.4f}, {rq1_context['ci_joint_hi']:.4f}]  "
      f"t({rq1_context['df_joint']:.1f})={rq1_context['t_joint']:.3f}  "
      f"p={rq1_context['p_joint']:.4f}  {sig_marker(rq1_context['p_joint'])}")

if len(susceptibility_df) > 0:
    print(f"\nRQ2 — Genre Framing Susceptibility (ranked highest to lowest):")
    for _, r in susceptibility_df.iterrows():
        print(f"  {r['genre'].upper():14s}  Gain={r['framing_gain']:+.4f}  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")

if len(genre_mod_df) > 0:
    print(f"\nRQ2 — Within-Genre Clip vs Context Dominance:")
    for _, r in genre_mod_df.iterrows():
        print(f"  {r['genre'].upper():14s}  -> {r['dominant']:7s} dominant  "
              f"d={r['d']:.3f}  sig_bonf={r['sig_bonf']}")

print(f"\nRQ3a — Clip vs Context (SC_dx vs dc_SX_dg):")
print(f"  Clip M={rq3_primary['mean_clip']:.4f}  |  Ctx M={rq3_primary['mean_ctx']:.4f}")
dominant = "CLIP" if rq3_primary["diff"] > 0 else "CONTEXT"
print(f"  Mean diff={rq3_primary['mean_diff']:+.4f}  "
      f"95% CI [{rq3_primary['ci_low']:.4f}, {rq3_primary['ci_high']:.4f}]  "
      f"{dominant} dominant  d={rq3_primary['d']:.3f}  {rq3_primary['sig']}")

print(f"\nRQ3b — Combined Advantage (SC_SX):  SKIPPED — not available at TF-IDF level.")
print(f"  -> Deferred to MiniLM pipeline.")
```

---

## Exploratory Analyses

> The analyses below do not map directly onto the three pre-specified research
> questions. They are retained as descriptive and methodological supplements that
> may be useful for characterising the data or for future exploratory work.

### Word Clouds by Genre × Context

Word size reflects TF-IDF score; darker shading indicates a higher score. Useful
for understanding the lexical character of each condition cell.

```{python exploratory-wordclouds, echo=FALSE}
genre_rename = {"JAZ": "JAZZ", "MET": "METAL", "ELE": "ELECTRONIC"}
meta_wc      = df.copy()
meta_wc["genre_code"] = (meta_wc["genre_code"]
                          .str.strip().str.upper()
                          .replace(genre_rename))

genres_wc   = sorted(meta_wc["genre_code"].unique())
contexts_wc = sorted(meta_wc["context_word"].unique())

fig, axes = plt.subplots(len(genres_wc), len(contexts_wc), figsize=(20, 16))
axes = np.atleast_2d(axes)

for i, genre in enumerate(genres_wc):
    for j, context in enumerate(contexts_wc):
        ax   = axes[i, j]
        mask = ((meta_wc["genre_code"]   == genre) &
                (meta_wc["context_word"] == context))
        if mask.sum() == 0:
            ax.text(0.5, 0.5, "No data", ha="center", va="center")
            ax.axis("off")
            continue

        subset     = tfidf_scores_df.iloc[mask.values]
        mean_tfidf = subset.mean(axis=0)
        mean_tfidf = mean_tfidf[mean_tfidf.index.str.lower() != ignore_token]
        top_words  = mean_tfidf.nlargest(50).to_dict()

        if not top_words:
            ax.text(0.5, 0.5, "No data", ha="center", va="center")
            ax.axis("off")
            continue

        vals = np.array(list(top_words.values()), dtype=float)
        vmin, vmax = vals.min(), vals.max()

        def color_func(word, **kwargs):
            val  = top_words.get(word, vmin)
            norm = (val - vmin) / (vmax - vmin) if vmax > vmin else 0.5
            g    = 0.5 - norm * 0.5
            return mcolors.to_hex([g, g, g])

        wc = WordCloud(
            width=400, height=300,
            background_color="white",
            relative_scaling=0.5,
            min_font_size=8
        ).generate_from_frequencies(top_words)
        wc.recolor(color_func=color_func)

        ax.imshow(wc, interpolation="bilinear")
        ax.axis("off")

        if i == 0:
            ax.set_title(context.upper(), fontsize=18, fontweight="bold", pad=10)
        if j == 0:
            ax.text(-0.1, 0.5, genre, transform=ax.transAxes,
                    fontsize=18, fontweight="bold",
                    rotation=90, va="center", ha="right")

plt.suptitle(
    "Word Clouds by Genre × Context\n"
    "(Word size = TF-IDF score; Darker = higher value)",
    fontsize=22, fontweight="bold", y=0.995
)
plt.tight_layout()
plt.savefig(f"{output_dir}/TFIDF_genre_context_wordclouds.png",
            dpi=300, bbox_inches="tight")
plt.show()
print("Saved word clouds")
```

### Pairwise Context and Genre Comparisons

Tests whether specific context labels or genres differ from each other in how much
convergence they produce. Not pre-specified in the hypotheses — retained as
descriptive characterisation only.

```{python exploratory-pairwise, echo=FALSE}
# ── Pairwise context comparisons ──────────────────────────────────────────────
print("PAIRWISE CONTEXT COMPARISONS  (Bonferroni corrected)")
print("-" * 70)

ctx_pairs = []
for c1, c2 in combinations(ctx_list, 2):
    g1 = sim_df.loc[
        (sim_df["condition"] == "dc_SX_dg") &
        (sim_df["context_i"] == c1) & (sim_df["context_j"] == c1), "similarity"]
    g2 = sim_df.loc[
        (sim_df["condition"] == "dc_SX_dg") &
        (sim_df["context_i"] == c2) & (sim_df["context_j"] == c2), "similarity"]
    if len(g1) > 1 and len(g2) > 1:
        t, p, df_val, mean_diff, ci_low, ci_high = welch_t(g1, g2)
        d = cohens_d(g1, g2)
        ctx_pairs.append(dict(context1=c1, context2=c2,
                               mean1=g1.mean(), mean2=g2.mean(),
                               diff=g1.mean()-g2.mean(),
                               t=t, df=df_val, p=p, d=d,
                               n1=len(g1), n2=len(g2)))

context_pairs_df = pd.DataFrame(ctx_pairs)
if len(context_pairs_df) > 0:
    context_pairs_df["p_bonf"]   = (context_pairs_df["p"] * len(context_pairs_df)).clip(upper=1.0)
    context_pairs_df["sig"]      = context_pairs_df["p"].apply(sig_marker)
    context_pairs_df["sig_bonf"] = context_pairs_df["p_bonf"].apply(sig_marker)
    context_pairs_df = context_pairs_df.sort_values("d", key=abs, ascending=False)
    print(context_pairs_df[["context1","context2","mean1","mean2","d",
                             "p","p_bonf","sig_bonf"]].to_string(index=False))
    context_pairs_df.to_csv(
        f"{output_dir}/TFIDF_context_pairwise_comparisons.csv", index=False)

# ── Pairwise genre comparisons ─────────────────────────────────────────────────
print("\n\nPAIRWISE GENRE COMPARISONS  (Bonferroni corrected)")
print("-" * 70)

genre_pairs = []
for g1_lbl, g2_lbl in combinations(genre_list, 2):
    s1 = sim_df.loc[
        (sim_df["condition"] == "dc_dx_SG") &
        (sim_df["genre_i"] == g1_lbl) & (sim_df["genre_j"] == g1_lbl), "similarity"]
    s2 = sim_df.loc[
        (sim_df["condition"] == "dc_dx_SG") &
        (sim_df["genre_i"] == g2_lbl) & (sim_df["genre_j"] == g2_lbl), "similarity"]
    if len(s1) > 1 and len(s2) > 1:
        t, p, df_val, mean_diff, ci_low, ci_high = welch_t(s1, s2)
        d = cohens_d(s1, s2)
        genre_pairs.append(dict(genre1=g1_lbl, genre2=g2_lbl,
                                 mean1=s1.mean(), mean2=s2.mean(),
                                 diff=s1.mean()-s2.mean(),
                                 t=t, df=df_val, p=p, d=d,
                                 n1=len(s1), n2=len(s2)))

genre_pairs_df = pd.DataFrame(genre_pairs)
if len(genre_pairs_df) > 0:
    genre_pairs_df["p_bonf"]   = (genre_pairs_df["p"] * len(genre_pairs_df)).clip(upper=1.0)
    genre_pairs_df["sig"]      = genre_pairs_df["p"].apply(sig_marker)
    genre_pairs_df["sig_bonf"] = genre_pairs_df["p_bonf"].apply(sig_marker)
    genre_pairs_df = genre_pairs_df.sort_values("d", key=abs, ascending=False)
    print(genre_pairs_df[["genre1","genre2","mean1","mean2","d",
                           "p","p_bonf","sig_bonf"]].to_string(index=False))
    genre_pairs_df.to_csv(
        f"{output_dir}/TFIDF_genre_pairwise_comparisons.csv", index=False)
```

### Similarity Matrices

Full within/between similarity for context and genre — useful as a descriptive
data quality check and for visualising overall structure.

```{python exploratory-similarity-matrices, echo=FALSE}
# Compute within-condition means needed for matrix diagonals
ctx_within_exp = []
for ctx in ctx_list:
    sims = sim_df.loc[
        (sim_df["condition"] == "dc_SX_dg") &
        (sim_df["context_i"] == ctx) & (sim_df["context_j"] == ctx), "similarity"]
    if len(sims) > 0:
        ctx_within_exp.append(dict(context=ctx, mean=sims.mean()))
context_within_df = pd.DataFrame(ctx_within_exp)

genre_within_exp = []
for genre in genre_list:
    sims = sim_df.loc[
        (sim_df["condition"] == "dc_dx_SG") &
        (sim_df["genre_i"] == genre) & (sim_df["genre_j"] == genre), "similarity"]
    if len(sims) > 0:
        genre_within_exp.append(dict(genre=genre, mean=sims.mean()))
genre_within_df = pd.DataFrame(genre_within_exp)

fig, axes = plt.subplots(1, 2, figsize=(16, 7))
for ax, within_df, fkey, meta_col, panel in [
    (axes[0], context_within_df, "context", "context_word", "A. Context Similarity Matrix"),
    (axes[1], genre_within_df,   "genre",   "genre_code",   "B. Genre Similarity Matrix"),
]:
    labels = sorted(df[meta_col].unique())
    n_lbl  = len(labels)
    mat    = np.full((n_lbl, n_lbl), np.nan)
    for i, l1 in enumerate(labels):
        for j, l2 in enumerate(labels):
            if i == j:
                val = within_df.loc[within_df[fkey] == l1, "mean"].values
                mat[i, j] = val[0] if len(val) > 0 else np.nan
            else:
                mask = (
                    ((sim_df[f"{fkey}_i"] == l1) & (sim_df[f"{fkey}_j"] == l2)) |
                    ((sim_df[f"{fkey}_i"] == l2) & (sim_df[f"{fkey}_j"] == l1))
                )
                sims = sim_df.loc[mask, "similarity"]
                mat[i, j] = sims.mean() if len(sims) > 0 else np.nan
    if not np.all(np.isnan(mat)):
        sns.heatmap(mat, annot=True, fmt=".3f", cmap="YlOrRd",
                    xticklabels=labels, yticklabels=labels,
                    cbar_kws={"label": "Mean Similarity"},
                    mask=np.isnan(mat),
                    linewidths=0.5, linecolor="gray", ax=ax)
    ax.set_title(f"{panel}\n(Diagonal = Within-{fkey.capitalize()})",
                 fontsize=13, fontweight="bold")

plt.suptitle("Similarity Matrices: Context and Genre",
             fontsize=15, fontweight="bold")
plt.tight_layout()
plt.savefig(f"{output_dir}/TFIDF_similarity_matrices.png",
            dpi=300, bbox_inches="tight")
plt.show()
```

### Document-Level t-SNE

t-SNE projects the high-dimensional TF-IDF vectors into 2D space. Provides a visual
check on whether documents with shared conditions cluster together — useful for data
quality and interpretation, but not a hypothesis test.

```{python exploratory-tsne, echo=FALSE}
X     = tfidf_matrix.toarray()
n_svd = min(50, X.shape[1] - 1)
svd   = TruncatedSVD(n_components=n_svd, random_state=42)
X_svd = svd.fit_transform(X)
print(f"SVD explained variance: {svd.explained_variance_ratio_.sum():.3f}  "
      f"({n_svd} components)")

try:
    tsne = TSNE(n_components=2, perplexity=15, max_iter=1000,
                random_state=42, init="pca", learning_rate="auto")
except TypeError:
    tsne = TSNE(n_components=2, perplexity=15, n_iter=1000,
                random_state=42, init="pca", learning_rate="auto")

X_2d = tsne.fit_transform(X_svd)

doc_tsne_df = df[["clip_name", "context_word", "genre_code"]].copy().reset_index(drop=True)
doc_tsne_df["TSNE1"] = X_2d[:, 0]
doc_tsne_df["TSNE2"] = X_2d[:, 1]
doc_tsne_df.to_csv(f"{output_dir}/TFIDF_tsne_coords.csv", index=False)

fig, ax = plt.subplots(figsize=(10, 8))
sns.scatterplot(data=doc_tsne_df, x="TSNE1", y="TSNE2",
                hue="genre_code", style="context_word",
                palette="tab10", s=120, alpha=0.9, ax=ax)
ax.set_title("t-SNE: TF-IDF Document Embeddings (2D)",
             fontsize=13, fontweight="bold")
ax.legend(bbox_to_anchor=(1.05, 1), loc="upper left", borderaxespad=0.)
plt.tight_layout()
plt.savefig(f"{output_dir}/TFIDF_tsne_plot.png", dpi=300, bbox_inches="tight")
plt.show()
print("Saved: document t-SNE plot")
```

```{r env}
install.packages("renv")
renv::init()
renv::snapshot()
```