---
title: "Supplementary Study: Believability Rating Analysis"
subtitle: "Framed Listening — Accompanying Contextual Information"
author: "Hazel A. van der Walle (PhD student, Music, Durham University)"
date: "24 April 2026"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    theme: cosmo
    self-contained: true
---

All datasets generated and used for this study are openly available on GitHub:
<https://github.com/HazelvdW/context-framed-listening>.

---

## Overview

This document reports analyses of the **Supplementary Believability Study**.
Before listening to each clip in the main study, participants were given a
contextual description that varied by condition (e.g., one group was told a
clip was heard *in a bar*; another that it was *from a videogame*). In a
separate believability study, an independent participant sample (*N* = 80) rated
how believable each of the 64 clip–context pairings (16 clips × 4 contexts) felt
on a 1–5 scale.

The primary scientific purpose of this study is to examine whether clip–context
pairings rated as more believable also produce more semantically similar
music-influenced mental content (MIMC) in the main study — that is, whether
believability predicts the cosine similarity values from the TF-IDF and
sentence-embedding (MiniLM) pipelines. This connection is tested in Section 7.

**Research questions:**

1. Do believability ratings differ across context conditions and musical genres?
2. Do some clip–context pairings stand out as particularly high or low in believability?
3. Does clip–context believability predict MIMC cosine similarity in Study 1?

**Data:** `dataSUPPstudy.csv` — 1,280 observations (80 participants × 16 clips × 4 contexts)

> **A note on statistical approach**: believability is measured on an ordinal
> 1–5 scale. The Shapiro–Wilk test will be significant by default at N = 1,280
> due to test sensitivity (see Section 5). All inferential tests therefore use
> non-parametric equivalents consistent with the main study pipeline:
> Kruskal–Wallis omnibus tests, Dunn post-hoc comparisons with Bonferroni
> correction, and Spearman correlations.

---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE, message = FALSE, warning = FALSE,
  fig.width = 8, fig.height = 5, dpi = 300, out.width = "100%"
)
```

```{r packages}
required_packages <- c("ggplot2", "dplyr", "tidyr", "scales",
                       "kableExtra", "dunn.test", "ARTool",
                       "ggrepel", "ggpubr")

for (pkg in required_packages) {
  if (!requireNamespace(pkg, quietly = TRUE))
    install.packages(pkg, repos = "https://cloud.r-project.org")
  library(pkg, character.only = TRUE)
}

output_dir <- "output/suppstudy"
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)
```

```{r paths}
# ── Edit this path to match your local setup ───────────────────────────────────
base_path <- paste0(
  "/Users/hazelaileenvanderwalle/Library/CloudStorage/",
  "OneDrive-Personal/work/study/PhD/_PROJECT/",
  "_framedListening_NLP/context-framed-listening"
)

supp_data_path <- file.path(base_path, "dataSUPPstudy.csv")

# Cosine similarity outputs from main analysis pipelines
# (run NLP-TFIDF-analysis.qmd and NLP-SEmb-analysis.qmd first)
tfidf_sim_path <- file.path(base_path,
  "NLP_outputs/TFIDF/TFIDF_similarity_by_condition.csv")
semb_sim_path  <- file.path(base_path,
  "NLP_outputs/SentenceEmbedding/similarity_by_condition_all-MiniLM-L6-v2.csv")
```

```{r colours}
# Consistent with main study visualisations
context_colours <- c(
  "bar"        = "#9e185b",
  "concert"    = "#6369d1",
  "movie"      = "#940e8c",
  "videogame"  = "#86d202"
)

genre_colours <- c(
  "80s"        = "#fc8a1e",
  "Electronic" = "#d7ec78",
  "Jazz"       = "#8552b6",
  "Metal"      = "#9e1100"
)
```

---

## Data Loading and Cleaning

```{r load-data}
raw <- read.csv(supp_data_path, stringsAsFactors = FALSE, encoding = "UTF-8")

# Clean non-breaking spaces from context_word
raw$context_word <- trimws(gsub("\u00a0", "", raw$context_word))

# Extract genre and arousal from clip_name
raw$genre   <- sub("^([A-Za-z0-9]+)_.*",         "\\1", raw$clip_name)
raw$arousal <- sub("^[A-Za-z0-9]+_(LOW|MED)_.*", "\\1", raw$clip_name)

# Readable clip label (strip prefix and file extension)
raw$clip_short <- gsub("_", " ",
                   sub("\\.mp3$", "",
                   sub("^[A-Za-z0-9]+_[A-Z]+_[0-9]+_", "", raw$clip_name)))

# Rename key measure
raw$believability <- raw$rating_likelihood.response

# Factor ordering
raw$context_word <- factor(raw$context_word,
                            levels = c("bar", "concert", "movie", "videogame"))
raw$genre        <- factor(raw$genre,
                            levels = c("80s", "Electronic", "Jazz", "Metal"))
raw$arousal      <- factor(raw$arousal, levels = c("LOW", "MED"))
raw$PROLIFIC_PID <- factor(raw$PROLIFIC_PID)

cat("Dimensions:         ", nrow(raw), "rows ×", ncol(raw), "columns\n")
cat("Unique participants:", nlevels(raw$PROLIFIC_PID), "\n")
cat("Unique clips:       ", length(unique(raw$clip_name)), "\n")
cat("Contexts:           ", paste(levels(raw$context_word), collapse = ", "), "\n")
cat("Genres:             ", paste(levels(raw$genre),        collapse = ", "), "\n")
```

---

## Descriptive Statistics

### Overall

```{r desc-overall}
overall_desc <- data.frame(
  N      = sum(!is.na(raw$believability)),
  Mean   = round(mean(raw$believability,   na.rm = TRUE), 3),
  SD     = round(sd(raw$believability,     na.rm = TRUE), 3),
  Median = median(raw$believability,       na.rm = TRUE),
  Min    = min(raw$believability,          na.rm = TRUE),
  Max    = max(raw$believability,          na.rm = TRUE)
)
kable(overall_desc, caption = "Overall believability ratings") |>
  kable_styling(full_width = FALSE)
```

### By context condition

```{r desc-context}
desc_context <- raw |>
  group_by(context_word) |>
  summarise(N      = n(),
            Mean   = round(mean(believability, na.rm = TRUE), 3),
            SD     = round(sd(believability,   na.rm = TRUE), 3),
            Median = median(believability,     na.rm = TRUE),
            SE     = round(sd(believability,   na.rm = TRUE) / sqrt(n()), 3),
            .groups = "drop")
kable(desc_context, caption = "Believability by context condition") |>
  kable_styling(full_width = FALSE)
```

### By genre

```{r desc-genre}
desc_genre <- raw |>
  group_by(genre) |>
  summarise(N      = n(),
            Mean   = round(mean(believability, na.rm = TRUE), 3),
            SD     = round(sd(believability,   na.rm = TRUE), 3),
            Median = median(believability,     na.rm = TRUE),
            SE     = round(sd(believability,   na.rm = TRUE) / sqrt(n()), 3),
            .groups = "drop")
kable(desc_genre, caption = "Believability by genre") |>
  kable_styling(full_width = FALSE)
```

### By clip × context *(exported for Study 1 merge)*

Mean believability for each of the 64 clip–context cells — the unit used for
merging with cosine similarity values in Section 7.

```{r desc-clip-context}
desc_clip_context <- raw |>
  group_by(clip_name, clip_short, context_word, genre, arousal) |>
  summarise(N    = n(),
            Mean = round(mean(believability, na.rm = TRUE), 3),
            SD   = round(sd(believability,   na.rm = TRUE), 3),
            SE   = round(sd(believability,   na.rm = TRUE) / sqrt(n()), 3),
            .groups = "drop")

write.csv(desc_clip_context,
          file.path(output_dir, "believability_means_clip_context.csv"),
          row.names = FALSE)

kable(head(desc_clip_context, 16),
      caption = "First 16 clip × context cells (full table exported to output/)") |>
  kable_styling(full_width = FALSE, font_size = 11)
```

> **Exported:** `output/suppstudy/believability_means_clip_context.csv`

---

## Visualisations

### Distribution of all believability ratings

```{r fig-hist, fig.height=4}
p_hist <- ggplot(raw, aes(x = believability)) +
  geom_histogram(binwidth = 1, fill = "#585ccc", colour = "white", alpha = 0.85) +
  scale_x_continuous(breaks = 1:5,
                     labels = c("1\n(not at all\nbelievable)",
                                "2", "3", "4",
                                "5\n(very\nbelievable)")) +
  labs(title    = "Distribution of Believability Ratings",
       subtitle = "All clips and contexts combined (N = 1,280)",
       x = "Believability (1–5)", y = "Frequency") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))
p_hist
ggsave(file.path(output_dir, "hist_believability_overall.png"),
       p_hist, width = 7, height = 4, dpi = 300)
```

### Distribution by context condition

```{r fig-violin-context}
p_violin <- ggplot(raw, aes(x = context_word, y = believability,
                              fill = context_word)) +
  geom_violin(alpha = 0.6, trim = FALSE) +
  geom_boxplot(width = 0.15, outlier.size = 0.8, alpha = 0.85) +
  geom_hline(yintercept = 3, linetype = "dashed", colour = "grey40") +
  scale_fill_manual(values = context_colours, guide = "none") +
  scale_y_continuous(limits = c(1, 5), breaks = 1:5) +
  labs(title    = "Believability by Context Condition",
       subtitle = "Violin + boxplot; dashed line = scale midpoint (3)",
       x = "Context condition", y = "Believability (1–5)") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))
p_violin
ggsave(file.path(output_dir, "violin_believability_by_context.png"),
       p_violin, width = 8, height = 5, dpi = 300)
```

### Context × genre interaction

```{r fig-interaction}
interaction_means <- raw |>
  group_by(context_word, genre) |>
  summarise(Mean = mean(believability, na.rm = TRUE),
            SE   = sd(believability,   na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

p_interaction <- ggplot(interaction_means,
                         aes(x = context_word, y = Mean,
                             colour = genre, group = genre)) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE),
                width = 0.15, linewidth = 0.5) +
  geom_hline(yintercept = 3, linetype = "dashed", colour = "grey50") +
  scale_colour_manual(values = genre_colours, name = "Genre") +
  scale_y_continuous(limits = c(1, 5), breaks = 1:5) +
  labs(title    = "Context × Genre: Mean Believability",
       subtitle = "Error bars = ±1 SE; dashed line = scale midpoint",
       x = "Context condition", y = "Mean believability (1–5)") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))
p_interaction
ggsave(file.path(output_dir, "interaction_context_genre.png"),
       p_interaction, width = 8, height = 5, dpi = 300)
```

### Mean believability per clip (collapsed across contexts)

```{r fig-clip, fig.height=7}
clip_means_plot <- raw |>
  group_by(clip_name, clip_short, genre) |>
  summarise(Mean = mean(believability, na.rm = TRUE),
            SE   = sd(believability,   na.rm = TRUE) / sqrt(n()),
            .groups = "drop") |>
  mutate(clip_short = factor(clip_short, levels = clip_short[order(Mean)]))

p_clip <- ggplot(clip_means_plot,
                  aes(x = clip_short, y = Mean, fill = genre)) +
  geom_col(alpha = 0.85) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE),
                width = 0.25, linewidth = 0.4) +
  geom_hline(yintercept = 3, linetype = "dashed", colour = "grey40") +
  scale_fill_manual(values = genre_colours, name = "Genre") +
  scale_y_continuous(limits = c(0, 5), breaks = 1:5) +
  coord_flip() +
  labs(title    = "Mean Believability by Clip",
       subtitle = "Collapsed across all four context conditions; error bars = ±1 SE",
       x = NULL, y = "Mean believability (1–5)") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"), legend.position = "right")
p_clip
ggsave(file.path(output_dir, "bar_believability_by_clip.png"),
       p_clip, width = 10, height = 7, dpi = 300)
```

### Clip × context faceted bar chart

```{r fig-clip-context, fig.height=10, fig.width=10}
clip_context_means <- raw |>
  group_by(clip_name, clip_short, context_word, genre) |>
  summarise(Mean = mean(believability, na.rm = TRUE),
            SE   = sd(believability,   na.rm = TRUE) / sqrt(n()),
            .groups = "drop") |>
  mutate(clip_short = factor(clip_short, levels = levels(clip_means_plot$clip_short)))

p_clip_context <- ggplot(clip_context_means,
                           aes(x = clip_short, y = Mean, fill = genre)) +
  geom_col(alpha = 0.85) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE),
                width = 0.3, linewidth = 0.35) +
  geom_hline(yintercept = 3, linetype = "dashed", colour = "grey40", linewidth = 0.4) +
  facet_wrap(~ context_word, ncol = 2,
             labeller = labeller(context_word = c(
               "bar"        = "Bar",
               "concert"    = "Concert",
               "movie"      = "Movie",
               "videogame" = "videogame"))) +
  scale_fill_manual(values = genre_colours, name = "Genre") +
  scale_y_continuous(limits = c(0, 5), breaks = c(1, 3, 5)) +
  coord_flip() +
  labs(title    = "Mean Believability by Clip and Context Condition",
       subtitle = "Clips ordered by overall mean; error bars = ±1 SE; dashed = midpoint",
       x = NULL, y = "Mean believability (1–5)") +
  theme_minimal(base_size = 10) +
  theme(plot.title      = element_text(face = "bold"),
        strip.text      = element_text(face = "bold", size = 10),
        legend.position = "bottom",
        panel.spacing   = unit(1, "lines"))
p_clip_context
ggsave(file.path(output_dir, "bar_believability_clip_by_context.png"),
       p_clip_context, width = 10, height = 10, dpi = 300)
```

### Heatmap: clip × context at a glance

```{r fig-heatmap, fig.height=6, fig.width=7}
p_heatmap <- ggplot(clip_context_means,
                     aes(x = context_word, y = clip_short, fill = Mean)) +
  geom_tile(colour = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%.1f", Mean)),
            size = 2.8, colour = "white", fontface = "bold") +
  scale_fill_gradient2(low      = "#940e8c",
                       mid      = "#f5f0f5",
                       high     = "#4b9c00",
                       midpoint = 3, limits = c(1, 5),
                       name     = "Mean\nbelievability") +
  scale_x_discrete(labels = c("bar"        = "Bar",
                               "concert"    = "Concert",
                               "movie"      = "Movie",
                               "videogame" = "Video\ngame")) +
  labs(title    = "Believability Heatmap: Clip × Context",
       subtitle = "Cell values = mean rating (1–5); clips ordered by overall mean",
       x = "Context condition", y = NULL) +
  theme_minimal(base_size = 10) +
  theme(plot.title      = element_text(face = "bold"),
        axis.text.y     = element_text(size = 8),
        legend.position = "right")
p_heatmap
ggsave(file.path(output_dir, "heatmap_believability_clip_context.png"),
       p_heatmap, width = 7, height = 6, dpi = 300)
```

---

## Distribution Diagnostics

Believability is measured on a 1–5 ordinal scale. Shapiro–Wilk tests are provided
for completeness, but at N = 1,280 the test is sensitive to trivial deviations from
normality. Visual inspection of the histogram above and the results below together
confirm that non-parametric testing is appropriate.

```{r normality}
sw_overall <- shapiro.test(raw$believability)
cat(sprintf("Overall  —  W = %.4f, p = %.4e\n",
            sw_overall$statistic, sw_overall$p.value))

sw_context <- raw |>
  group_by(context_word) |>
  summarise(W = round(shapiro.test(believability)$statistic, 4),
            p = round(shapiro.test(believability)$p.value,   4),
            .groups = "drop")
kable(sw_context, caption = "Shapiro–Wilk by context condition") |>
  kable_styling(full_width = FALSE)
```

---

## One-Sample Tests vs Scale Midpoint

Do believability ratings differ from the scale midpoint (µ₀ = 3)?
Wilcoxon signed-rank tests are the non-parametric equivalent of one-sample
*t*-tests and are appropriate for ordinal data. Results report the test statistic
*V*, the group median, and the two-tailed *p*-value.

> **Note**: the `conf.int = TRUE` option for Wilcoxon signed-rank tests
> requires sufficient non-tied Walsh averages to compute a confidence interval,
> which is not guaranteed on a coarse 1–5 integer scale. Confidence intervals
> are therefore omitted; medians are reported as the location summary instead.

### Overall

```{r wilcox-overall}
cat("Overall N =", sum(!is.na(raw$believability)), "\n")
cat("Unique values:", sort(unique(raw$believability)), "\n")
w_overall <- wilcox.test(raw$believability, mu = 3)
cat(sprintf("V = %.0f, p = %.4e, Median = %.1f\n",
            w_overall$statistic, w_overall$p.value,
            median(raw$believability, na.rm = TRUE)))
```

### By context condition

```{r wilcox-context}
# Diagnostic: check what levels exist in the data vs factor levels
cat("Factor levels:  ", paste(levels(raw$context_word), collapse = " | "), "\n")
cat("Values in data: ", paste(sort(unique(as.character(raw$context_word))),
                               collapse = " | "), "\n\n")

w_context <- do.call(rbind, lapply(levels(raw$context_word), function(ctx) {
  d <- raw$believability[raw$context_word == ctx]
  d <- d[!is.na(d)]
  cat(sprintf("  %s: N = %d\n", ctx, length(d)))
  if (length(d) < 2) {
    return(data.frame(context = ctx, Median = NA, V = NA, p = NA))
  }
  wt <- tryCatch(
    wilcox.test(d, mu = 3),
    error = function(e) { cat("  ERROR:", conditionMessage(e), "\n"); NULL }
  )
  if (is.null(wt))
    return(data.frame(context = ctx, Median = round(median(d), 3), V = NA, p = NA))
  data.frame(context = ctx,
             Median  = round(median(d),   3),
             V       = wt$statistic,
             p       = round(wt$p.value,  4))
}))
kable(w_context,
      caption = "Wilcoxon signed-rank vs midpoint (3), by context") |>
  kable_styling(full_width = FALSE)
```

### By genre

```{r wilcox-genre}
cat("Factor levels:  ", paste(levels(raw$genre), collapse = " | "), "\n")
cat("Values in data: ", paste(sort(unique(as.character(raw$genre))),
                               collapse = " | "), "\n\n")

w_genre <- do.call(rbind, lapply(levels(raw$genre), function(g) {
  d <- raw$believability[raw$genre == g]
  d <- d[!is.na(d)]
  cat(sprintf("  %s: N = %d\n", g, length(d)))
  if (length(d) < 2) {
    return(data.frame(genre = g, Median = NA, V = NA, p = NA))
  }
  wt <- tryCatch(
    wilcox.test(d, mu = 3),
    error = function(e) { cat("  ERROR:", conditionMessage(e), "\n"); NULL }
  )
  if (is.null(wt))
    return(data.frame(genre = g, Median = round(median(d), 3), V = NA, p = NA))
  data.frame(genre  = g,
             Median = round(median(d),   3),
             V      = wt$statistic,
             p      = round(wt$p.value,  4))
}))
kable(w_genre,
      caption = "Wilcoxon signed-rank vs midpoint (3), by genre") |>
  kable_styling(full_width = FALSE)
```

---

## Kruskal–Wallis Tests

### Believability by context condition

```{r kw-context}
kw_context <- kruskal.test(believability ~ context_word, data = raw)
n_obs      <- nrow(raw)
k_ctx      <- nlevels(raw$context_word)
eps_ctx    <- (kw_context$statistic - k_ctx + 1) / (n_obs - k_ctx)

cat(sprintf("Kruskal–Wallis: H(%d) = %.3f, p = %.4e\n",
            kw_context$parameter, kw_context$statistic, kw_context$p.value))
cat(sprintf("Epsilon-squared = %.4f\n", eps_ctx))
```

```{r dunn-context}
cat("\nDunn post-hoc (Bonferroni correction):\n")
dunn.test(raw$believability, raw$context_word,
          method = "bonferroni", kw = FALSE, label = TRUE)
```

### Believability by genre

```{r kw-genre}
kw_genre <- kruskal.test(believability ~ genre, data = raw)
k_gen    <- nlevels(raw$genre)
eps_gen  <- (kw_genre$statistic - k_gen + 1) / (n_obs - k_gen)

cat(sprintf("Kruskal–Wallis: H(%d) = %.3f, p = %.4e\n",
            kw_genre$parameter, kw_genre$statistic, kw_genre$p.value))
cat(sprintf("Epsilon-squared = %.4f\n", eps_gen))
```

```{r dunn-genre}
cat("\nDunn post-hoc (Bonferroni correction):\n")
dunn.test(raw$believability, raw$genre,
          method = "bonferroni", kw = FALSE, label = TRUE)
```

### Context × genre interaction (ART ANOVA)

A standard two-way ANOVA assumes normally distributed residuals, which is not met
here. The Aligned Rank Transformation (ART) ANOVA is a non-parametric alternative
that tests for main effects and interactions on ranked data, and is appropriate for
ordinal outcomes with a factorial design.

```{r art-anova}
raw_complete <- raw[!is.na(raw$believability) &
                    !is.na(raw$context_word)  &
                    !is.na(raw$genre), ]
cat(sprintf("Rows used for ART ANOVA: %d (dropped %d with NAs)\n",
            nrow(raw_complete), nrow(raw) - nrow(raw_complete)))

art_model  <- art(believability ~ context_word * genre, data = raw_complete)
art_result <- anova(art_model)
print(art_result)
```

---

## Believability as a Predictor of MIMC Cosine Similarity

This is the primary scientific question of the supplementary study: do clip–context
pairings rated as more believable also produce more semantically similar MIMC in
Study 1?

Believability means at the clip × context cell level (N = 64 cells) are merged
with mean cosine similarity values from both the TF-IDF and MiniLM pipelines.
The `Dclip_Scontext` condition is used for cosine similarity — pairs sharing a
context label but different clips — because this condition directly isolates
context-driven convergence, which is what believability of the context cue most
plausibly influences. Spearman correlations are used throughout, consistent with
the ordinal believability measure and non-normal cosine similarity distributions
confirmed in the main analyses.

> **A note on power**: the correlation analysis is conducted at the context level
> (N = 4) and the clip × context cell level (N = 64). At N = 4, statistical power
> is very low and p-values should not be over-interpreted — the direction and
> magnitude of the correlation are the primary interpretive focus.

### Load cosine similarity outputs

```{r load-cosine}
load_sim <- function(path, label) {
  tryCatch(
    read.csv(path, stringsAsFactors = FALSE),
    error = function(e) {
      message(label, " file not found:\n  ", path,
              "\nRun the corresponding analysis pipeline first.")
      NULL
    }
  )
}

tfidf_sim <- load_sim(tfidf_sim_path, "TF-IDF")
semb_sim  <- load_sim(semb_sim_path,  "MiniLM")

# Aggregate Dclip_Scontext pairs to context level for each pipeline
agg_ctx_sim <- function(sim_df, sim_col_name) {
  sim_df |>
    filter(condition == "Dclip_Scontext") |>
    mutate(context_word = tolower(trimws(context_i))) |>
    group_by(context_word) |>
    summarise(!!sim_col_name := mean(similarity, na.rm = TRUE),
              n_pairs = n(),
              .groups = "drop")
}

if (!is.null(tfidf_sim)) tfidf_ctx <- agg_ctx_sim(tfidf_sim, "tfidf_mean_sim")
if (!is.null(semb_sim))  semb_ctx  <- agg_ctx_sim(semb_sim,  "semb_mean_sim")
```

### Merge with believability means

```{r merge}
# Believability collapsed to context level
bel_context <- desc_clip_context |>
  mutate(context_word = tolower(trimws(as.character(context_word)))) |>
  group_by(context_word) |>
  summarise(believability_mean = mean(Mean, na.rm = TRUE), .groups = "drop")

merged <- bel_context
if (!is.null(tfidf_sim)) merged <- left_join(merged, tfidf_ctx, by = "context_word")
if (!is.null(semb_sim))  merged <- left_join(merged, semb_ctx,  by = "context_word")

kable(merged, digits = 4,
      caption = "Believability and cosine similarity by context condition") |>
  kable_styling(full_width = FALSE)
```

### Spearman correlations

```{r spearman-cors}
results <- data.frame(Pipeline = character(), rs = numeric(),
                      S = numeric(), p = numeric(), stringsAsFactors = FALSE)

if (!is.null(tfidf_sim) && "tfidf_mean_sim" %in% names(merged)) {
  ct <- cor.test(merged$believability_mean, merged$tfidf_mean_sim,
                  method = "spearman")
  results <- rbind(results, data.frame(
    Pipeline = "TF-IDF",
    rs = round(ct$estimate, 3), S = round(ct$statistic, 1),
    p  = round(ct$p.value, 4)))
}

if (!is.null(semb_sim) && "semb_mean_sim" %in% names(merged)) {
  cs <- cor.test(merged$believability_mean, merged$semb_mean_sim,
                  method = "spearman")
  results <- rbind(results, data.frame(
    Pipeline = "MiniLM",
    rs = round(cs$estimate, 3), S = round(cs$statistic, 1),
    p  = round(cs$p.value, 4)))
}

kable(results,
      caption = paste0("Spearman correlations: believability vs mean cosine ",
                       "similarity (Dclip_Scontext, N = 4 context conditions)")) |>
  kable_styling(full_width = FALSE)
```

### Scatter plots: believability vs cosine similarity

```{r fig-scatter, fig.width=11, fig.height=5}
make_scatter <- function(data, x_col, y_col, y_label, title) {
  ggplot(data, aes(x = .data[[x_col]], y = .data[[y_col]],
                   colour = context_word, label = context_word)) +
    geom_point(size = 5, alpha = 0.9) +
    geom_smooth(method = "lm", se = TRUE, colour = "grey40",
                linewidth = 0.8, linetype = "dashed") +
    geom_text_repel(size = 3.8, show.legend = FALSE,
                    box.padding = 0.4, point.padding = 0.3) +
    scale_colour_manual(values = context_colours, name = "Context") +
    labs(title    = title,
         subtitle = "Dclip_Scontext condition; Spearman correlation; N = 4 context conditions",
         x = "Mean believability (Study 2, 1–5)",
         y = y_label) +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(face = "bold"), legend.position = "none")
}

plots <- list()

if (!is.null(tfidf_sim) && "tfidf_mean_sim" %in% names(merged))
  plots[["tfidf"]] <- make_scatter(merged, "believability_mean", "tfidf_mean_sim",
                                    "Mean cosine similarity (TF-IDF)",
                                    "TF-IDF: Believability vs Cosine Similarity")

if (!is.null(semb_sim) && "semb_mean_sim" %in% names(merged))
  plots[["semb"]] <- make_scatter(merged, "believability_mean", "semb_mean_sim",
                                   "Mean cosine similarity (MiniLM)",
                                   "MiniLM: Believability vs Cosine Similarity")

if (length(plots) == 2) {
  p_scatter <- ggarrange(plotlist = plots, ncol = 2,
                          common.legend = TRUE, legend = "bottom")
  print(p_scatter)
  ggsave(file.path(output_dir, "scatter_believability_vs_cosine.png"),
         p_scatter, width = 12, height = 5, dpi = 300)
} else if (length(plots) == 1) {
  print(plots[[1]])
}
```

---

## Session Info

```{r session-info}
sessionInfo()
```
